---
title: "Self-reported sexual identity in Stockholm County in 2021"
author: Guoqiang Zhang
email: guoqiang.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages
```{r}
library(haven)
library(data.table)
library(naniar)
library(tidyverse)
library(jomo)
library(mitml)
library(mitools)
library(ggplot2)
library(ggbreak)
library(mice)
library(ggrepel)
library(ggpubr)
library(ggmosaic)
library(tidyr)
library(dplyr)
library(finalfit)
library(survey)
library(svyVGAM)
source("/Users/guoqiang.zhang/Documents/Karolinska Institutet/Research Projects/Trends and Fluidity of Sexual Identity/Sexual_identity_in_Stockholm_County/Helper_functions.R") # helper function
```

### 2. Import and Visualise Data
```{r}
load("/Volumes/LGBT Project data/d_2021.RData")

# sampling strata
n_miss( d_2021$stratum )
d_2021$sampling_strata <- as.factor( d_2021$stratum )
length( unique( d_2021$sampling_strata ) ) # 38 strata

d_2021 <- d_2021 %>%
  mutate( sampling_strata_region = recode( sampling_strata, 
                                           `114` = "Upplands-Väsby",
                                           `115` = "Vallentuna",
                                           `117` = "Österåker",
                                           `120` = "Värmdö",
                                           `123` = "Järfälla",
                                           `125` = "Ekerö",
                                           `126` = "Huddinge",
                                           `127` = "Botkyrka",
                                           `128` = "Salem",
                                           `136` = "Haninge",
                                           `138` = "Tyresö",
                                           `139` = "Upplands-Bro",
                                           `140` = "Nykvarn",
                                           `160` = "Täby",
                                           `162` = "Danderyd",
                                           `163` = "Sollentuna",
                                           `181` = "Södertälje",
                                           `182` = "Nacka",
                                           `183` = "Sundbyberg",
                                           `184` = "Solna",
                                           `186` = "Lidingö",
                                           `187` = "Vaxholm",
                                           `188` = "Norrtälje",
                                           `191` = "Sigtuna",
                                           `192` = "Nynäshamn",
                                           `180103` = "Spånga-Tensta",
                                           `180104` = "Hässelby-Vällingby",
                                           `180106` = "Bromma",
                                           `180108` = "Kungsholmen",
                                           `180109` = "Norrmalm",
                                           `180110` = "Östermalm",
                                           `180115` = "Skarpnäck",
                                           `180118` = "Farsta",
                                           `180124` = "Skärholmen",
                                           `180125` = "Rinkeby-Kista",
                                           `180127` = "Södermalm",
                                           `180128` = "Enskede-Årsta-Vantör",
                                           `180129` = "Hägersten-Älvsjö"
                                           ) )

# sexual identity
table( d_2021$F21F45_Q57, useNA = "always" )
d_2021$sexual_identity_2021 <- factor( ifelse( d_2021$F21F45_Q57 == 1, "Heterosexual", 
                                          ifelse( d_2021$F21F45_Q57 == 2, "Homosexual",
                                                  ifelse( d_2021$F21F45_Q57 == 3, "Bisexual", "None of the above" ) ) ),
                                  levels = c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" ) )
table( d_2021$sexual_identity_2021, useNA = "always" )

# sex
table( d_2021$kon, useNA = "always" )
d_2021$sex <- factor( ifelse( d_2021$kon == 1, "Male", "Female" ), 
                      levels = c( "Male", "Female" ) )
table( d_2021$sex, useNA = "always" )

# age
summary( d_2021$F21alder )
d_2021$age <- d_2021$F21alder
d_2021$age_cat <- factor( ifelse( d_2021$age <= 29, "16-29", 
                                  ifelse( d_2021$age >=30 & d_2021$age <= 44, "30-44",
                                          ifelse( d_2021$age >= 45 & d_2021$age <= 59, "45-59", ">=60" ) ) ),
                          levels = c( "16-29", "30-44", "45-59", ">=60" ) )
table( d_2021$age_cat, useNA = "always" )

# interaction term between age and sex
d_2021$age_sex <- interaction( d_2021$age_cat, d_2021$sex )

# country of birth
table( d_2021$fodelseland, useNA = "always" )
d_2021$country_of_birth <- factor( ifelse( d_2021$fodelseland == "Afrika", "Africa",
                                           ifelse( d_2021$fodelseland == "Asien", "Asia",
                                                   ifelse( d_2021$fodelseland == "Europa", "Europe",
                                                           ifelse( d_2021$fodelseland == "Sverige", "Sweden", "Americas" ) ) ) ),
                                   levels = c( "Africa", "Americas", "Asia", "Europe", "Sweden" ) )
table( d_2021$country_of_birth, useNA = "always" )

# education
table( d_2021$utbniva2021, useNA = "always" )
d_2021$education <- factor( ifelse( d_2021$utbniva2021 <= 2, "<=9 years",
                                    ifelse( d_2021$utbniva2021 <= 4, "10-12 years", ">=13 years" ) ),
                            levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
table( d_2021$education, useNA = "always" )

# disposable income
summary( d_2021$dispink2021, useNA = "always" )
d_2021$dispink2021[ d_2021$dispink2021 < 0 ] <- NA
d_2021$income <- factor( ifelse( d_2021$dispink2021 <= 2500, "<=2,500",
                                 ifelse( d_2021$dispink2021 > 2500 & d_2021$dispink2021 <= 3500, "(2,500, 3,500]",
                                         ifelse( d_2021$dispink2021 > 3500 & d_2021$dispink2021 <= 4500, "(3,500, 4,500]", ">4,500" ) ) ),
                         levels = c( "<=2,500", "(2,500, 3,500]", "(3,500, 4,500]", ">4,500" ) )
table( d_2021$income, useNA = "always" )

# marital status
table( d_2021$civil2021, useNA = "always" )
d_2021$marital_status <- factor( ifelse( d_2021$civil2021 == "G" | d_2021$civil2021 == "RP", "Currently married",
                                         ifelse( d_2021$civil2021 == "OG", "Never married", "Other" ) ), 
                                 levels = c( "Never married", "Currently married", "Other" ) )
table( d_2021$marital_status, useNA = "always" )

# occupation
table( d_2021$SSYK_kl, useNA = "always" )
d_2021$occupation <- factor(
  ifelse(
    d_2021$SSYK_kl == "Yrken inom byggverksamhet och tillverkning" |
      d_2021$SSYK_kl == "Yrken inom lantbruk, trädgård, skogsbruk och fiske" |
      d_2021$SSYK_kl == "Yrken inom maskinell tillverkning och transport m.m.",
    "Manual and field trades",
    ifelse(
      d_2021$SSYK_kl == "Service-, omsorgs- och försäljningsyrken" |
        d_2021$SSYK_kl == "Yrken inom administration och kundtjänst" |
        d_2021$SSYK_kl == "Yrken med krav på kortare utbildning eller introduktion",
      "Service and support",
      ifelse(
        d_2021$SSYK_kl == "Yrken med krav på fördjupad högskolekompetens" |
          d_2021$SSYK_kl == "Yrken med krav på högskolekompetens eller motsvarande" |
          d_2021$SSYK_kl == "Chefsyrken",
        "Expertise and leadership",
        NA
      )
    )
  ),
  levels = c(
    "Manual and field trades",
    "Service and support",
    "Expertise and leadership"
  )
)
table( d_2021$occupation, useNA = "always" )


##### demographic characteristics #####

# among respondents (n = 23,066)
# make characteristics table by sexual identity
explanatory =  c( "sex", "age_cat", "country_of_birth", "education", "occupation", "income", "marital_status" )
dependent = "sexual_identity_2021"

d_2021_table <- d_2021 %>% 
  summary_factorlist( dependent,
                      explanatory, 
                      na_include = TRUE,
                      na_include_dependent = TRUE, 
                      total_col = TRUE,
                      add_col_totals = TRUE,
                      column = FALSE )

# Fisher's test
x1 <- table( d_2021$sex, d_2021$sexual_identity_2021 )
x1
format( round( fisher.test( x1[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x2 <- table( d_2021$age_cat, d_2021$sexual_identity_2021 )
x2
format( round( fisher.test( x2[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x3 <- table( d_2021$country_of_birth, d_2021$sexual_identity_2021 )
x3
format( round( fisher.test( x3[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x4 <- table( d_2021$education, d_2021$sexual_identity_2021 )
x4
format( round( fisher.test( x4[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x5 <- table( d_2021$income, d_2021$sexual_identity_2021 )
x5
format( round( fisher.test( x5[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x6 <- table( d_2021$marital_status, d_2021$sexual_identity_2021 )
x6
format( round( fisher.test( x6[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x7 <- table( d_2021$occupation, d_2021$sexual_identity_2021 )
x7
format( round( fisher.test( x7[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )


##### design weights #####

summary( d_2021$F21dvikt )
d_2021$design_weight <- d_2021$F21dvikt


##### non-response #####

# unit non-response
d_2021$design_weight_unit_nonresponse <- d_2021$F21dbvikt # weights calculated assuming Missing Completely At Random (MCAR) within each stratum
summary( d_2021$design_weight_unit_nonresponse )
sum( d_2021$design_weight_unit_nonresponse ) # No. of source population = 1,827,424

unitresponse_prob <- d_2021 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( unitresponse_prob = unique( design_weight ) / unique( design_weight_unit_nonresponse ),
             no.of.population = sum( design_weight_unit_nonresponse ),
             sample_size = unique( no.of.population )/unique( design_weight ) ) # calculate overall unit response rate, and no. of population and sample size within each stratum

d_2021 <- d_2021 %>% 
  left_join( unitresponse_prob, by = "sampling_strata_region" )

# item non-response
itemresponse_prob <- d_2021 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( itemresponse_prob = sum( !is.na( sexual_identity_2021 ) ) / n() ) # calculate item response rate

d_2021 <- d_2021 %>% 
  left_join( itemresponse_prob, by = "sampling_strata_region" ) %>% 
  mutate( itemresponse_prob = ifelse( is.na( sexual_identity_2021 ), 0, itemresponse_prob ) )


##### summary of stratified sampling #####

sampling_frame_2021 <- as.data.frame( d_2021 %>% 
                                   group_by( sampling_strata_region ) %>% 
                                   reframe( no.of.population = unique( no.of.population ), 
                                            sample_size = unique( no.of.population/design_weight ),
                                            unitresponse = n(),
                                            itemresponse = sum( itemresponse_prob != 0 ) ) )

sampling_frame_2021$unitresponse_rate <- sampling_frame_2021$unitresponse/sampling_frame_2021$sample_size
sampling_frame_2021$itemresponse_rate <- sampling_frame_2021$itemresponse/sampling_frame_2021$unitresponse
sampling_frame_2021$overallresponse_rate <- sampling_frame_2021$itemresponse/sampling_frame_2021$sample_size

sampling_frame_2021$unitresponse_label <- paste0( sampling_frame_2021$unitresponse, " (", 
                                             sprintf( "%.1f", sampling_frame_2021$unitresponse_rate*100 ), "%)" )
sampling_frame_2021$overallresponse_label <- paste0( sampling_frame_2021$itemresponse, " (", 
                                                sprintf( "%.1f", sampling_frame_2021$overallresponse_rate*100 ), "%)" )

round( sum( sampling_frame_2021$unitresponse )/( sum( sampling_frame_2021$sample_size ) ), 3 ) # overall unit response rate
round( sum( sampling_frame_2021$itemresponse )/( sum( sampling_frame_2021$unitresponse ) ), 3 ) # overall item response rate
round( sum( sampling_frame_2021$itemresponse )/( sum( sampling_frame_2021$sample_size ) ), 3 ) # overall response rate

writexl::write_xlsx( sampling_frame_2021, "sampling_frame_2021.xlsx" )


##### calibrated weights #####

d_2021$calibrated_weight <- d_2021$F21kalvikt

# visualize calibrated weights across sampling strata
ggplot( d_2021 %>% 
          group_by( sampling_strata_region ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( sampling_strata_region, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 230 ), breaks = c( 0, 50, 100, 150, 200 ), expand = c( 0, 0 ) ) +
  labs( y = NULL, x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ) )


##### replicating non-respondent rows for sampling design #####

# because d_2021 includes data only for respondents (unit response), we need to duplicate rows for non-respondents
# so that the final dataset represents the sampling process
rows_to_add <- d_2021 %>%
  group_by( sampling_strata_region ) %>%
  summarise( to_add = unique( sample_size ) - n(),
             no.of.population = unique( no.of.population ),
             sample_size = unique( sample_size ),
             design_weight = unique( design_weight ) )

sum( rows_to_add$to_add ) # 24,819 non-respondents

rows_to_add$to_add <- round( rows_to_add$to_add ) # to resolve floating-point precision issues

replicated_rows <- rows_to_add[ rep( row.names( rows_to_add ), rows_to_add$to_add ), c( 1, 3:5 ) ]

d_2021_complete <- bind_rows( d_2021, replicated_rows ) # 47,885 individuals in the original sample
```

### 3. Estimation of Proportions of Sexual Identities
#### 3.1. Complete-case analysis
##### 3.1.1. Define survey design
```{r}
# prepare dataset
d_2021_complete_cc <- d_2021_complete

d_2021_complete_cc$country_of_birth <- factor( 
  ifelse( d_2021_complete_cc$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2021_complete_cc$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

# create survey design
survey_design_cc <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ design_weight,
                               fpc = ~ no.of.population,
                               data = d_2021_complete_cc )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

# the following analyses assume MCAR
```

##### 3.1.2. By sex
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                        by = ~ sex,
                        design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( sex ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_sex
}

prop_cc_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_sex <- left_join( prop_cc_sex,
                          d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                             !is.na( d_2021_complete_cc$sex ), ] %>% 
                            group_by( subgroup = sex ) %>% 
                            summarise( sample_size_2021 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.3. By age group
###### 3.1.3.1. Calculate proportion by pre-specified age cut-off
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                        by = ~ age_cat,
                        design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( age_cat ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_age ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_age
}

prop_cc_age <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age <- left_join( prop_cc_age,
                          d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                             !is.na( d_2021_complete_cc$age_cat ), ] %>% 
                            group_by( subgroup = age_cat ) %>% 
                            summarise( sample_size_2021 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

###### 3.1.3.2. Calculate proportion and proportion ratio by varying age cut-offs
```{r}
d_2021_iteration_age <- d_2021_complete

min_age <- min( d_2021_iteration_age$age, na.rm = TRUE )

results_df <- data.frame()

for ( cut_off in ( min_age ):100 ) {
  d_2021_iteration_age$age_iteration <- ifelse( d_2021_iteration_age$age <= cut_off, "young", "old" )
  
  survey_design_iteration_age <- svydesign( ids = ~ 1, 
                                            strata = ~ sampling_strata_region,
                                            weights = ~ design_weight,
                                            fpc = ~ no.of.population,
                                            data = d_2021_iteration_age )
  
  list_of_df <- list()
  
  for ( cat in categories ) {
    prop_cc_age_iteration <- svyby(
      formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
      by = ~ age_iteration,
      design = subset( survey_design_iteration_age, !is.na( sexual_identity_2021 ) & !is.na( age ) ),
      FUN = svyciprop,
      method = "beta" )
    
    colnames( prop_cc_age_iteration ) <- c( "subgroup", 
                                            paste0( cat, "_point_estimate_2021" ), 
                                            paste0( cat, "_se_2021" ) )
    
    list_of_df[[cat]] <- prop_cc_age_iteration
  }
  
  prop_cc_age_iteration_merged <- Reduce( function( df1, df2 ) { 
    merge( df1, df2, by = "subgroup" ) 
    }, 
    list_of_df
    )
  
  prop_cc_age_iteration_merged$cut_off <- cut_off
  
  results_df <- rbind( results_df, prop_cc_age_iteration_merged )
  }

results_wide <- results_df %>%
  select( -ends_with( "_se_2021" ) ) %>%
  pivot_wider( names_from = subgroup, 
               values_from = c( Heterosexual_point_estimate_2021, 
                                Homosexual_point_estimate_2021, 
                                Bisexual_point_estimate_2021, 
                                `None of the above_point_estimate_2021` ) 
               )

colnames( results_wide ) <- gsub( "_point_estimate_2021", "", colnames( results_wide ) )

results_wide$Heterosexual_pr_2021 <- results_wide$Heterosexual_young/results_wide$Heterosexual_old
results_wide$Homosexual_pr_2021 <- results_wide$Homosexual_young/results_wide$Homosexual_old
results_wide$Bisexual_pr_2021 <- results_wide$Bisexual_young/results_wide$Bisexual_old
results_wide$`None of the above_pr_2021` <- results_wide$`None of the above_young`/results_wide$`None of the above_old`

results_wide$Heterosexual_pr_2021[ is.infinite( results_wide$Heterosexual_pr_2021 ) ] <- NA
results_wide$Homosexual_pr_2021[ is.infinite( results_wide$Homosexual_pr_2021 ) ] <- NA
results_wide$Bisexual_pr_2021[ is.infinite( results_wide$Bisexual_pr_2021 ) ] <- NA
results_wide$`None of the above_pr_2021`[ is.infinite( results_wide$`None of the above_pr_2021` ) ] <- NA

writexl::write_xlsx( results_wide, "prop_cc_age_iteration_2021.xlsx" )
```

##### 3.1.4. By sex*age group
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                            by = ~ age_sex,
                            design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( age_sex ) ),
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_age_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_age_sex
}

prop_cc_age_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age_sex <- left_join( prop_cc_age_sex,
                              d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                 !is.na( d_2021_complete_cc$age_sex ), ] %>% 
                                group_by( subgroup = age_sex ) %>% 
                                summarise( sample_size_2021 = n() ),
                              by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.5. By education
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_education <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                              by = ~ education,
                              design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( education ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_education ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_education
}

prop_cc_education <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_education <- left_join( prop_cc_education,
                                d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                   !is.na( d_2021_complete_cc$education ), ] %>% 
                                  group_by( subgroup = education ) %>% 
                                  summarise( sample_size_2021 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.6. By occupation
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_occupation <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                               by = ~ occupation,
                               design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( occupation ) ),
                               FUN = svyciprop,
                               vartype = "ci",
                               method = "beta" )
  
  colnames( prop_cc_occupation ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_occupation
  }

prop_cc_occupation <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
  }, 
  list_of_df )

prop_cc_occupation <- left_join( prop_cc_occupation,
                                     d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                           !is.na( d_2021_complete_cc$occupation ), ] %>% 
                                       group_by( subgroup = occupation ) %>% 
                                       summarise( sample_size_2021 = n() ),
                                     by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.7. By income
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_income <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                           by = ~ income,
                           design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( income ) ),
                           FUN = svyciprop,
                           vartype = "ci",
                           method = "beta" )
  
  colnames( prop_cc_income ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_income
}

prop_cc_income <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_income <- left_join( prop_cc_income,
                             d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                   !is.na( d_2021_complete_cc$income ), ] %>% 
                               group_by( subgroup = income ) %>% 
                               summarise( sample_size_2021 = n() ),
                             by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.8. By country of birth
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_country_of_birth <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                                     by = ~ country_of_birth,
                                     design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( country_of_birth ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_country_of_birth ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_country_of_birth
}

prop_cc_country_of_birth <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_country_of_birth <- left_join( prop_cc_country_of_birth,
                                       d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                   !is.na( d_2021_complete_cc$country_of_birth ), ] %>% 
                                         group_by( subgroup = country_of_birth ) %>% 
                                         summarise( sample_size_2021 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.9. By marital status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_marital_status <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                                   by = ~ marital_status,
                                   design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) & !is.na( marital_status ) ),
                                   FUN = svyciprop,
                                   vartype = "ci",
                                   method = "beta" )
  
  colnames( prop_cc_marital_status ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_marital_status
}

prop_cc_marital_status <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_marital_status <- left_join( prop_cc_marital_status,
                                     d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ) &
                                                   !is.na( d_2021_complete_cc$marital_status ), ] %>% 
                                       group_by( subgroup = marital_status ) %>% 
                                       summarise( sample_size_2021 = n() ),
                                     by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.10. Overall proportions of sexual identities in Stockholm County
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                                design = subset( survey_design_cc, !is.na( sexual_identity_2021 ) ),
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_overall
}

prop_cc_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
}, 
list_of_df ) %>% 
  as.data.frame() %>%
  rownames_to_column( var = "subgroup" )

prop_cc_overall[ 1, 1 ] <- "Stockholm County"

prop_cc_overall <- bind_cols( prop_cc_overall,
                              d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity_2021 ), ] %>% 
                                summarise( sample_size_2021 = n() ) ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.11. Merge datasets
```{r}
prop_cc_summary_2021 <- rbind( prop_cc_sex, 
                               prop_cc_age,
                               prop_cc_age_sex,
                               prop_cc_education,
                               prop_cc_occupation,
                               prop_cc_income, 
                               prop_cc_country_of_birth, 
                               prop_cc_marital_status,
                               prop_cc_overall 
                               )

writexl::write_xlsx( prop_cc_summary_2021, "prop_cc_summary_2021.xlsx" )
```

#### 3.2. Multiple imputation and inverse probability weighting
##### 3.2.1. Multiple imputation
###### 3.2.1.1. Obtain incomplete dataset
```{r}
d_2021_ic <- as.data.frame( d_2021 %>% 
                              select( "sampling_strata", "sampling_strata_region", "no.of.population", "calibrated_weight", "sexual_identity_2021", "age", "sex", "fodelseland", "utbniva2021", "dispink2021", "marital_status" ) ) %>%
  rename(
    country_of_birth = fodelseland, 
    education = utbniva2021, 
    income = dispink2021 
    )

summary( d_2021_ic )
d_2021_ic <- within( d_2021_ic, country_of_birth <- factor( country_of_birth ) )
d_2021_ic <- within( d_2021_ic, education <- factor( education ) )

sapply( d_2021_ic, class ) # all continuous variables are numeric, and all categorical variables are factor
```

###### 3.2.1.2. Visualize missing pattern and select auxiliary variables
```{r}
# identify missing variables
vis_miss( d_2021_ic )
n_miss( d_2021_ic )
md.pattern( d_2021_ic )
miss_var_summary( d_2021_ic ) # 2.2% missing in sexual_identity_2021, 2.1% in education, and 0.2% in income

# select auxiliary variables for sexual identity
# check whether potential auxiliary variables are correlated with sexual identity
names( d_2021_ic )
plot( d_2021_ic$sampling_strata_region, d_2021_ic$sexual_identity_2021 )
plot( d_2021_ic$sexual_identity_2021, d_2021_ic$age )
plot( d_2021_ic$sex, d_2021_ic$sexual_identity_2021 )
plot( d_2021_ic$country_of_birth, d_2021_ic$sexual_identity_2021 )
plot( d_2021_ic$education, d_2021_ic$sexual_identity_2021 )
plot( d_2021_ic$sexual_identity_2021, d_2021_ic$income )
plot( d_2021_ic$marital_status, d_2021_ic$sexual_identity_2021 )

# check whether potential auxiliary variables are related to sexual identity being missing
{
  explanatory = c( "sampling_strata_region", "age", "sex", "country_of_birth", "education", "income", "marital_status" )
  dependent = "sexual_identity_2021"
  d_2021_ic %>% missing_pairs( dependent, explanatory, position = "fill", showYAxisPlotLabels = TRUE )
  }

# finally, include all the variables as auxiliary variables for sexual identity, including sampling strata, age, sex, country of birth, education, income, and marital status
```

###### 3.2.1.3. Two-level multivariate normal imputation with latent normal variable approach
```{r}
# use multiple imputation to account for item non-response
# assume Missing At Random (MAR)

# create calibrated weight strata
d_2021_ic$calibrated_weight_strata <- as.factor( cut( d_2021_ic$calibrated_weight,
                                                      breaks = quantile( d_2021_ic$calibrated_weight, probs = seq( 0, 1, length.out = 39 ) ),
                                                      labels = 1:38,
                                                      include.lowest = TRUE,
                                                      right = TRUE ) )

# visualize calibrated weight strata
ggplot( d_2021_ic %>% 
          group_by( calibrated_weight_strata ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( calibrated_weight_strata, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 280 ), 
                      breaks = c( 0, 50, 100, 150, 200, 250 ), 
                      expand = c( 0, 0 ) ) +
  labs( y = "Calibrated Weight Strata", x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.y = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 )
         )

summary( d_2021_ic )
sapply( d_2021_ic, class ) # all continuous variables are numeric, and all categorical variables are factor


# add random effects in intercepts and predictors
fml_imp <- sexual_identity_2021 + education + income ~ 1 + age + sex + age*sex + country_of_birth + marital_status + sampling_strata_region + ( 1 + age + sex + country_of_birth + marital_status + sampling_strata_region | calibrated_weight_strata )

# perform a "dry run"
ini <- jomoImpute( data = d_2021_ic,
                   formula = fml, 
                   random.L1 = "full", # random covariance matrix of residuals
                   n.burn = 500,
                   n.iter = 2,
                   m = 2,
                   seed = 12345 # set the seed so that results can be reproduced
                   )

summary( ini ) # summarize model and display convergence statistics
plot( ini ) # display convergence and autocorrelation plots

# generate imputation
imp <- jomoImpute( data = d_2021_ic,
                   formula = fml, 
                   random.L1 = "full",
                   n.burn = 2000,
                   n.iter = 1000,
                   m = 50,
                   seed = 12345
                   )

save.image( file = "working_environment_2021.RData" )
```

###### 3.2.1.4. Validate imputations
```{r}
# validate imputation
summary( imp ) # summarize model and display convergence statistics
plot( imp ) # display convergence plots and autocorrelation plot

# extract list of imputed datasets
implist <- mitmlComplete( imp, "all" )
```

##### 3.2.2. Inverse probability weighting
```{r}
# use inverse probability weighting to account for unit non-response

# transform the imputed datasets
implist <- within( implist, {
  
  # age
  age_cat <- factor( ifelse( age <= 29, "16-29", 
                             ifelse( age >=30 & age <= 44, "30-44",
                                     ifelse( age >= 45 & age <= 66, "45-66", ">=67" ) ) ),
                     levels = c( "16-29", "30-44", "45-66", ">=67" ) )

  # country of birth
  country_of_birth_cat <- factor( ifelse( country_of_birth == "Sverige", "Sweden",
                                      ifelse( country_of_birth == "Europa", "Europe", "Outside Europe" ) ),
                              levels = c( "Sweden", "Europe", "Outside Europe" ) )
  
  # education
  education_cat <- factor( ifelse( as.numeric( as.character( education ) ) <= 2, "<=9 years",
                               ifelse( as.numeric( as.character( education ) ) <= 4, "10-12 years", ">=13 years" ) ),
                       levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
  
  # disposable income
  income_cat <- factor( ifelse( income < 1500, "<1,500",
                            ifelse( income >= 1500 & income < 3000, "[1,500, 3,000)",
                                    ifelse( income >= 3000 & income < 4500, "[3,000, 4,500)", ">=4,500" ) ) ),
                    levels = c( "<=1,500", "[1,500, 3,000)", "[3,000, 4,500)", ">=4,500" ) )
  
  # marital status
  marital_status_cat <- factor( ifelse( marital_status == "G" | marital_status == "RP", "Currently married", "Other" ), 
                            levels = c( "Currently married", "Other" ) )
  
  } )

survey_design_imp <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ calibrated_weight,
                               fpc = ~ no.of.population,
                               data = imputationList( implist ) )

# calculate proportion of each sexual identity across sampling strata
categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_stratum <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                            by = ~ sampling_strata_region, # equivalent to calculating the proportion separately for each stratum 
                            design = survey_design_cc,
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_stratum ) <- c( "sampling_strata_region", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  list_of_df[[cat]] <- prop_cc_stratum
}

prop_cc_summary <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "sampling_strata_region" ) 
  }, 
  list_of_df )

# calculate overall proportions of each sexual identity
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity_2021 == '", cat, "' )" ) ),
                                design = survey_design_cc,
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  list_of_df[[cat]] <- prop_cc_overall
}

df_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
  }, 
  list_of_df )

df_overall$sampling_strata_region <- "Stockholm County"
prop_cc_summary_2021 <- rbind( prop_cc_summary, df_overall )
```

### 4. Relation between Sexual Identity and Demographic Factors
#### 4.1. Complete-case analysis
##### 4.1.1. Define survey design
```{r}
##### prepare dataset #####

d_2021_cc_model <- d_2021_complete

# exposures of interest, including age, sex, country of birth, education, income, and marital status
d_2021_cc_model$age_exp <- relevel( d_2021_cc_model$age_cat, ref = "45-59" )

d_2021_cc_model$sex_exp <- relevel( d_2021_cc_model$sex, ref = "Male" )

d_2021_cc_model$country_of_birth_exp <- factor( 
  ifelse( d_2021_cc_model$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2021_cc_model$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

d_2021_cc_model$education_exp <- relevel( d_2021_cc_model$education, ref = ">=13 years" )

d_2021_cc_model$income_exp <- relevel( d_2021_cc_model$income, ref = ">4,500" )

d_2021_cc_model$marital_status_exp <- relevel( d_2021_cc_model$marital_status, ref = "Currently married" )


# outcomes of interest, including sexual minority, homosexual, bisexual, and other
d_2021_cc_model$sexual_minority <- ifelse( d_2021_cc_model$sexual_identity_2021 == "Heterosexual", 0, 1 )

d_2021_cc_model$homosexual <- ifelse( d_2021_cc_model$sexual_identity_2021 == "Homosexual", 1, 0 )

d_2021_cc_model$bisexual <- ifelse( d_2021_cc_model$sexual_identity_2021 == "Bisexual", 1, 0 )

d_2021_cc_model$other <- ifelse( d_2021_cc_model$sexual_identity_2021 == "None of the above", 1, 0 )


# confounding variables, including age, sex, country of birth, education, income, marital status, 
# and place of residence (i.e., sampling strata)
d_2021_cc_model$age_conf <- d_2021_cc_model$age # age

d_2021_cc_model$sex_conf <- d_2021_cc_model$sex # sex

d_2021_cc_model$country_of_birth_conf <- d_2021_cc_model$country_of_birth # country of birth (grouped into five categories due to sparse data)

d_2021_cc_model$education_conf <- as.factor( d_2021_cc_model$utbniva2021 ) # education

d_2021_cc_model$income_conf <- d_2021_cc_model$dispink2021 # disposable income

d_2021_cc_model$marital_status_conf <- d_2021_cc_model$marital_status # marital status (grouped into three categories due to sparse data)

d_2021_cc_model$place_of_residence_conf <- d_2021_cc_model$sampling_strata_region # place of residence


##### create survey design #####
survey_design_cc_model <- svydesign( ids = ~ 1,
                                     strata = ~ sampling_strata_region,
                                     weights = ~ design_weight,
                                     fpc = ~ no.of.population,
                                     data = d_2021_cc_model )

# the following analyses assume MCAR
```

##### 4.1.2. Define model formula
```{r}
########## formula for crude analyses ##########

##### exposure of interest: age #####

fml_sexual_minority_age_crude <- sexual_minority ~ age_exp
fml_homosexual_age_crude <- homosexual ~ age_exp
fml_bisexual_age_crude <- bisexual ~ age_exp
fml_other_age_crude <- other ~ age_exp

# list of formulas
fml_list_age_crude <- list(
  fml_sexual_minority_age_crude = fml_sexual_minority_age_crude,
  fml_homosexual_age_crude = fml_homosexual_age_crude,
  fml_bisexual_age_crude = fml_bisexual_age_crude,
  fml_other_age_crude = fml_other_age_crude
  )


##### exposure of interest: age by sex #####

fml_sexual_minority_age_by_sex_crude <- sexual_minority ~ age_exp*sex_exp
fml_homosexual_age_by_sex_crude <- homosexual ~ age_exp*sex_exp
fml_bisexual_age_by_sex_crude <- bisexual ~ age_exp*sex_exp
fml_other_age_by_sex_crude <- other ~ age_exp*sex_exp

# list of formulas
fml_list_age_by_sex_crude <- list(
  fml_sexual_minority_age_by_sex_crude = fml_sexual_minority_age_by_sex_crude,
  fml_homosexual_age_by_sex_crude = fml_homosexual_age_by_sex_crude,
  fml_bisexual_age_by_sex_crude = fml_bisexual_age_by_sex_crude,
  fml_other_age_by_sex_crude = fml_other_age_by_sex_crude
  )


##### exposure of interest: sex #####

fml_sexual_minority_sex_crude <- sexual_minority ~ sex_exp
fml_homosexual_sex_crude <- homosexual ~ sex_exp
fml_bisexual_sex_crude <- bisexual ~ sex_exp
fml_other_sex_crude <- other ~ sex_exp

# list of formulas
fml_list_sex_crude <- list(
  fml_sexual_minority_sex_crude = fml_sexual_minority_sex_crude,
  fml_homosexual_sex_crude = fml_homosexual_sex_crude,
  fml_bisexual_sex_crude = fml_bisexual_sex_crude,
  fml_other_sex_crude = fml_other_sex_crude
  )


##### exposure of interest: country of birth #####

fml_sexual_minority_country_of_birth_crude <- sexual_minority ~ country_of_birth_exp
fml_homosexual_country_of_birth_crude <- homosexual ~ country_of_birth_exp
fml_bisexual_country_of_birth_crude <- bisexual ~ country_of_birth_exp
fml_other_country_of_birth_crude <- other ~ country_of_birth_exp

# list of formulas
fml_list_country_of_birth_crude <- list(
  fml_sexual_minority_country_of_birth_crude = fml_sexual_minority_country_of_birth_crude,
  fml_homosexual_country_of_birth_crude = fml_homosexual_country_of_birth_crude,
  fml_bisexual_country_of_birth_crude = fml_bisexual_country_of_birth_crude,
  fml_other_country_of_birth_crude = fml_other_country_of_birth_crude
)


##### exposure of interest: education #####

fml_sexual_minority_education_crude <- sexual_minority ~ education_exp
fml_homosexual_education_crude <- homosexual ~ education_exp
fml_bisexual_education_crude <- bisexual ~ education_exp
fml_other_education_crude <- other ~ education_exp

# list of formulas
fml_list_education_crude <- list(
  fml_sexual_minority_education_crude = fml_sexual_minority_education_crude,
  fml_homosexual_education_crude = fml_homosexual_education_crude,
  fml_bisexual_education_crude = fml_bisexual_education_crude,
  fml_other_education_crude = fml_other_education_crude
  )


##### exposure of interest: income #####

fml_sexual_minority_income_crude <- sexual_minority ~ income_exp
fml_homosexual_income_crude <- homosexual ~ income_exp
fml_bisexual_income_crude <- bisexual ~ income_exp
fml_other_income_crude <- other ~ income_exp

# list of formulas
fml_list_income_crude <- list(
  fml_sexual_minority_income_crude = fml_sexual_minority_income_crude,
  fml_homosexual_income_crude = fml_homosexual_income_crude,
  fml_bisexual_income_crude = fml_bisexual_income_crude,
  fml_other_income_crude = fml_other_income_crude
  )


##### exposure of interest: marital status #####

fml_sexual_minority_marital_status_crude <- sexual_minority ~ marital_status_exp
fml_homosexual_marital_status_crude <- homosexual ~ marital_status_exp
fml_bisexual_marital_status_crude <- bisexual ~ marital_status_exp
fml_other_marital_status_crude <- other ~ marital_status_exp

# list of formulas
fml_list_marital_status_crude <- list(
  fml_sexual_minority_marital_status_crude = fml_sexual_minority_marital_status_crude,
  fml_homosexual_marital_status_crude = fml_homosexual_marital_status_crude,
  fml_bisexual_marital_status_crude = fml_bisexual_marital_status_crude,
  fml_other_marital_status_crude = fml_other_marital_status_crude
  )


########## formula for adjusted analyses ########## 

##### exposure of interest: age #####

# sexual minority
fml_sexual_minority_age_model_1 <- sexual_minority ~ age_exp + sex_conf + country_of_birth_conf
fml_sexual_minority_age_model_2 <- sexual_minority ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_age_model_1 <- homosexual ~ age_exp + sex_conf + country_of_birth_conf
fml_homosexual_age_model_2 <- homosexual ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_age_model_1 <- bisexual ~ age_exp + sex_conf + country_of_birth_conf
fml_bisexual_age_model_2 <- bisexual ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_age_model_1 <- other ~ age_exp + sex_conf + country_of_birth_conf
fml_other_age_model_2 <- other ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_age <- list(
  fml_sexual_minority_age_model_1 = fml_sexual_minority_age_model_1,
  fml_sexual_minority_age_model_2 = fml_sexual_minority_age_model_2,
  fml_homosexual_age_model_1 = fml_homosexual_age_model_1,
  fml_homosexual_age_model_2 = fml_homosexual_age_model_2,
  fml_bisexual_age_model_1 = fml_bisexual_age_model_1,
  fml_bisexual_age_model_2 = fml_bisexual_age_model_2,
  fml_other_age_model_1 = fml_other_age_model_1,
  fml_other_age_model_2 = fml_other_age_model_2
  )


##### exposure of interest: age by sex #####

# sexual minority
fml_sexual_minority_age_by_sex_model_1 <- sexual_minority ~ age_exp*sex_exp + country_of_birth_conf
fml_sexual_minority_age_by_sex_model_2 <- sexual_minority ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_age_by_sex_model_1 <- homosexual ~ age_exp*sex_exp + country_of_birth_conf
fml_homosexual_age_by_sex_model_2 <- homosexual ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_age_by_sex_model_1 <- bisexual ~ age_exp*sex_exp + country_of_birth_conf
fml_bisexual_age_by_sex_model_2 <- bisexual ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_age_by_sex_model_1 <- other ~ age_exp*sex_exp + country_of_birth_conf
fml_other_age_by_sex_model_2 <- other ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_age_by_sex <- list(
  fml_sexual_minority_age_by_sex_model_1 = fml_sexual_minority_age_by_sex_model_1,
  fml_sexual_minority_age_by_sex_model_2 = fml_sexual_minority_age_by_sex_model_2,
  fml_homosexual_age_by_sex_model_1 = fml_homosexual_age_by_sex_model_1,
  fml_homosexual_age_by_sex_model_2 = fml_homosexual_age_by_sex_model_2,
  fml_bisexual_age_by_sex_model_1 = fml_bisexual_age_by_sex_model_1,
  fml_bisexual_age_by_sex_model_2 = fml_bisexual_age_by_sex_model_2,
  fml_other_age_by_sex_model_1 = fml_other_age_by_sex_model_1,
  fml_other_age_by_sex_model_2 = fml_other_age_by_sex_model_2
  )


##### exposure of interest: sex #####

# sexual minority
fml_sexual_minority_sex_model_1 <- sexual_minority ~ sex_exp + age_conf + country_of_birth_conf
fml_sexual_minority_sex_model_2 <- sexual_minority ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_sex_model_1 <- homosexual ~ sex_exp + age_conf + country_of_birth_conf
fml_homosexual_sex_model_2 <- homosexual ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_sex_model_1 <- bisexual ~ sex_exp + age_conf + country_of_birth_conf
fml_bisexual_sex_model_2 <- bisexual ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_sex_model_1 <- other ~ sex_exp + age_conf + country_of_birth_conf
fml_other_sex_model_2 <- other ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_sex <- list(
  fml_sexual_minority_sex_model_1 = fml_sexual_minority_sex_model_1,
  fml_sexual_minority_sex_model_2 = fml_sexual_minority_sex_model_2,
  fml_homosexual_sex_model_1 = fml_homosexual_sex_model_1,
  fml_homosexual_sex_model_2 = fml_homosexual_sex_model_2,
  fml_bisexual_sex_model_1 = fml_bisexual_sex_model_1,
  fml_bisexual_sex_model_2 = fml_bisexual_sex_model_2,
  fml_other_sex_model_1 = fml_other_sex_model_1,
  fml_other_sex_model_2 = fml_other_sex_model_2
  )


##### exposure of interest: country of birth #####

# sexual minority
fml_sexual_minority_country_of_birth_model_1 <- sexual_minority ~ country_of_birth_exp + age_conf + sex_conf
fml_sexual_minority_country_of_birth_model_2 <- sexual_minority ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_country_of_birth_model_1 <- homosexual ~ country_of_birth_exp + age_conf + sex_conf
fml_homosexual_country_of_birth_model_2 <- homosexual ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_country_of_birth_model_1 <- bisexual ~ country_of_birth_exp + age_conf + sex_conf
fml_bisexual_country_of_birth_model_2 <- bisexual ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_country_of_birth_model_1 <- other ~ country_of_birth_exp + age_conf + sex_conf
fml_other_country_of_birth_model_2 <- other ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_country_of_birth <- list(
  fml_sexual_minority_country_of_birth_model_1 = fml_sexual_minority_country_of_birth_model_1,
  fml_sexual_minority_country_of_birth_model_2 = fml_sexual_minority_country_of_birth_model_2,
  fml_homosexual_country_of_birth_model_1 = fml_homosexual_country_of_birth_model_1,
  fml_homosexual_country_of_birth_model_2 = fml_homosexual_country_of_birth_model_2,
  fml_bisexual_country_of_birth_model_1 = fml_bisexual_country_of_birth_model_1,
  fml_bisexual_country_of_birth_model_2 = fml_bisexual_country_of_birth_model_2,
  fml_other_country_of_birth_model_1 = fml_other_country_of_birth_model_1,
  fml_other_country_of_birth_model_2 = fml_other_country_of_birth_model_2
)


##### exposure of interest: education #####

# sexual minority
fml_sexual_minority_education_model_1 <- sexual_minority ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_education_model_2 <- sexual_minority ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_education_model_1 <- homosexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_education_model_2 <- homosexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_education_model_1 <- bisexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_education_model_2 <- bisexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_education_model_1 <- other ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_education_model_2 <- other ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_education <- list(
  fml_sexual_minority_education_model_1 = fml_sexual_minority_education_model_1,
  fml_sexual_minority_education_model_2 = fml_sexual_minority_education_model_2,
  fml_homosexual_education_model_1 = fml_homosexual_education_model_1,
  fml_homosexual_education_model_2 = fml_homosexual_education_model_2,
  fml_bisexual_education_model_1 = fml_bisexual_education_model_1,
  fml_bisexual_education_model_2 = fml_bisexual_education_model_2,
  fml_other_education_model_1 = fml_other_education_model_1,
  fml_other_education_model_2 = fml_other_education_model_2
  )


##### exposure of interest: income #####

# sexual minority
fml_sexual_minority_income_model_1 <- sexual_minority ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_income_model_2 <- sexual_minority ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_income_model_1 <- homosexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_income_model_2 <- homosexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_income_model_1 <- bisexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_income_model_2 <- bisexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_income_model_1 <- other ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_income_model_2 <- other ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_income <- list(
  fml_sexual_minority_income_model_1 = fml_sexual_minority_income_model_1,
  fml_sexual_minority_income_model_2 = fml_sexual_minority_income_model_2,
  fml_homosexual_income_model_1 = fml_homosexual_income_model_1,
  fml_homosexual_income_model_2 = fml_homosexual_income_model_2,
  fml_bisexual_income_model_1 = fml_bisexual_income_model_1,
  fml_bisexual_income_model_2 = fml_bisexual_income_model_2,
  fml_other_income_model_1 = fml_other_income_model_1,
  fml_other_income_model_2 = fml_other_income_model_2
  )


##### exposure of interest: marital status #####

# sexual minority
fml_sexual_minority_marital_status_model_1 <- sexual_minority ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_marital_status_model_2 <- sexual_minority ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# homosexual
fml_homosexual_marital_status_model_1 <- homosexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_marital_status_model_2 <- homosexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# bisexual
fml_bisexual_marital_status_model_1 <- bisexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_marital_status_model_2 <- bisexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# other
fml_other_marital_status_model_1 <- other ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_marital_status_model_2 <- other ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# list of formulas
fml_list_marital_status <- list(
  fml_sexual_minority_marital_status_model_1 = fml_sexual_minority_marital_status_model_1,
  fml_sexual_minority_marital_status_model_2 = fml_sexual_minority_marital_status_model_2,
  fml_homosexual_marital_status_model_1 = fml_homosexual_marital_status_model_1,
  fml_homosexual_marital_status_model_2 = fml_homosexual_marital_status_model_2,
  fml_bisexual_marital_status_model_1 = fml_bisexual_marital_status_model_1,
  fml_bisexual_marital_status_model_2 = fml_bisexual_marital_status_model_2,
  fml_other_marital_status_model_1 = fml_other_marital_status_model_1,
  fml_other_marital_status_model_2 = fml_other_marital_status_model_2
  )

exposures <- c( "age", "age_by_sex", "sex", "country_of_birth", "education", "income", "marital_status" )
```

##### 4.1.3. Unadjusted analyses
```{r}
# fit Poisson regression model for each exposure and each outcome
all_models_cc_crude <- list()

for ( exposure in exposures ) {
  all_models_cc_crude[[ exposure ]] <- list()
  
  fml_list_name <- paste( "fml_list", exposure, "crude", sep = "_" )
  
  for ( name in names( get( fml_list_name ) ) ) {
    all_models_cc_crude[[ exposure ]][[ name ]] <- fit_model_crude( get( fml_list_name )[[ name ]],
                                                                    survey_design_cc_model )
  }
}

# refit the model for age by sex, using female as the reference group
# to extract results for age among females
d_2021_cc_model$sex_exp <- relevel( d_2021_cc_model$sex, ref = "Female" )

survey_design_cc_model_refit <- svydesign( ids = ~ 1,
                                           strata = ~ sampling_strata_region,
                                           weights = ~ design_weight,
                                           fpc = ~ no.of.population,
                                           data = d_2021_cc_model )

refit_model_cc_age_by_sex_crude <- list()

for ( name in names( fml_list_age_by_sex_crude ) ) {
  refit_model_cc_age_by_sex_crude[[ name ]] <- fit_model_crude( fml_list_age_by_sex_crude[[ name ]],
                                                                survey_design_cc_model_refit )
}
```

##### 4.1.4. Adjusted analyses
```{r}
# fit Poisson, log-binomial, and logistic regression models for each exposure and each outcome
all_models_cc <- list()

for ( exposure in exposures ) {
  all_models_cc[[ exposure ]] <- list()
  
  fml_list_name <- paste( "fml_list", exposure, sep = "_" )
  
  for ( name in names( get( fml_list_name ) ) ) {
    all_models_cc[[ exposure ]][[ name ]] <- fit_models( get( fml_list_name )[[ name ]],
                                                         survey_design_cc_model )
  }
}

# refit the three models for age by sex, using female as the reference group
# to extract results for age among females
refit_model_cc_age_by_sex <- list()

for ( name in names( fml_list_age_by_sex ) ) {
  refit_model_cc_age_by_sex[[ name ]] <- fit_models( fml_list_age_by_sex[[ name ]],
                                                     survey_design_cc_model_refit )
}
```

##### 4.1.5. Extract results
```{r}
identities <- c( "sexual_minority", "homosexual", "bisexual", "other" )
models <- c( "poisson", "log_binomial", "logistic" )

########## Crude analyses ##########

##### exposure of interest: age #####

exposures_age <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60"  )

# extract coefficient and 95% CI
results_cc_age_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$age ) ) {
  results_cc_age_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "age", 
    outcome = outcome, 
    variables = exposures_age
  )
}

# extract proportion ratio and 95% CI
results_cc_age_pr_crude <- extract_results_pr_crude( results_cc_age_coef_crude, identities, "age" )


##### exposure of interest: age by sex #####

exposures_age_male <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expFemale", "age_exp30-44:sex_expFemale", "age_exp>=60:sex_expFemale" )
exposures_age_female <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expMale", "age_exp30-44:sex_expMale", "age_exp>=60:sex_expMale" )

# extract coefficient and 95% CI among males
results_cc_age_by_sex_coef_crude_male <- list()

for ( outcome in names( all_models_cc_crude$age_by_sex ) ) {
  results_cc_age_by_sex_coef_crude_male[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "age_by_sex", 
    outcome = outcome, 
    variables = exposures_age_male
  )
}

# extract coefficient and 95% CI among females
results_cc_age_by_sex_coef_crude_female <- list()

for ( outcome in names( refit_model_cc_age_by_sex_crude ) ) {
  model <- refit_model_cc_age_by_sex_crude[[ outcome ]]
  results_cc_age_by_sex_coef_crude_female[[ outcome ]] <- cbind( coef( model )[ exposures_age_female ], 
                                                                 confint( model, ddf = degf( model$survey.design ) )[ exposures_age_female, , drop = FALSE ] )
}

# extract proportion ratio and 95% CI
results_cc_age_by_sex_pr_crude_male <- extract_results_pr_crude( results_cc_age_by_sex_coef_crude_male, identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_by_sex_pr_crude_female <- extract_results_pr_crude( results_cc_age_by_sex_coef_crude_female, identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_crude <- rbind( results_cc_age_by_sex_pr_crude_male[ c( 1:3 ), ], 
                                         results_cc_age_by_sex_pr_crude_female[ c( 1:3 ), ] )


##### exposure of interest: sex #####

exposures_sex <- c( "sex_expFemale" )

# extract coefficient and 95% CI
results_cc_sex_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$sex ) ) {
  results_cc_sex_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "sex", 
    outcome = outcome, 
    variables = exposures_sex
  )
}

# extract proportion ratio and 95% CI
results_cc_sex_pr_crude <- extract_results_pr_crude( results_cc_sex_coef_crude, identities, "sex" )


##### exposure of interest: country of birth #####

exposures_country_of_birth <- c( "country_of_birth_expEurope", "country_of_birth_expOutside Europe" )

# extract coefficient and 95% CI
results_cc_country_of_birth_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$country_of_birth ) ) {
  results_cc_country_of_birth_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "country_of_birth", 
    outcome = outcome, 
    variables = exposures_country_of_birth
  )
}

# extract proportion ratio and 95% CI
results_cc_country_of_birth_pr_crude <- extract_results_pr_crude( results_cc_country_of_birth_coef_crude, identities, "country_of_birth" )


##### exposure of interest: education #####

exposures_education <- c( "education_exp<=9 years", "education_exp10-12 years" )

# extract coefficient and 95% CI
results_cc_education_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$education ) ) {
  results_cc_education_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "education", 
    outcome = outcome, 
    variables = exposures_education
  )
}

# extract proportion ratio and 95% CI
results_cc_education_pr_crude <- extract_results_pr_crude( results_cc_education_coef_crude, identities, "education" )


##### exposure of interest: income #####

exposures_income <- c( "income_exp<=2,500", "income_exp(2,500, 3,500]", "income_exp(3,500, 4,500]" )

# extract coefficient and 95% CI
results_cc_income_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$income ) ) {
  results_cc_income_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "income", 
    outcome = outcome, 
    variables = exposures_income
  )
}

# extract proportion ratio and 95% CI
results_cc_income_pr_crude <- extract_results_pr_crude( results_cc_income_coef_crude, identities, "income" )


##### exposure of interest: marital status #####

exposures_marital_status <- c( "marital_status_expNever married", "marital_status_expOther" )

# extract coefficient and 95% CI
results_cc_marital_status_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$marital_status ) ) {
  results_cc_marital_status_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "marital_status", 
    outcome = outcome, 
    variables = exposures_marital_status
  )
}

# extract proportion ratio and 95% CI
results_cc_marital_status_pr_crude <- extract_results_pr_crude( results_cc_marital_status_coef_crude, identities, "marital_status" )


########## Adjusted analyses ##########

##### exposure of interest: age #####

# extract coefficient and 95% CI
results_cc_age_coef <- list()

for ( outcome in names( all_models_cc$age ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_age_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "age", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_age
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_age_pr_poisson_model_1 <- extract_results_pr( results_cc_age_coef, "model_1_poisson", identities, "age" )
colnames( results_cc_age_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_age_pr_poisson_model_1 )[-1], "_model_1")

results_cc_age_pr_poisson_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_poisson", identities, "age" )
colnames( results_cc_age_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_age_pr_poisson_model_2 )[-1], "_model_2")

results_cc_age_pr_poisson <- merge( results_cc_age_pr_poisson_model_1, results_cc_age_pr_poisson_model_2, by = "Exposure" )

results_cc_age_pr_log_binomial_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_log_binomial", identities, "age" )
results_cc_age_pr_logistic_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_logistic", identities, "age" )


##### exposure of interest: age by sex #####

# extract coefficient and 95% CI among males
results_cc_age_coef_male <- list()

for ( outcome in names( all_models_cc$age_by_sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_age_coef_male[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "age_by_sex", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_age_male
    )
  }
}

# extract coefficient and 95% CI among females
results_cc_age_coef_female <- list()

for ( outcome in names( refit_model_cc_age_by_sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    model <- refit_model_cc_age_by_sex[[ outcome ]][[ mod ]]
    
    if ( !is.null( model ) ) {
      results_cc_age_coef_female[[ key ]] <- cbind( coef( model )[ exposures_age_female ], 
                                                    confint( model, ddf = degf( model$survey.design ) )[ exposures_age_female, , drop = FALSE ] )
    }
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
# results from poisson regression
results_cc_age_pr_poisson_male_model_1 <- extract_results_pr( results_cc_age_coef_male, "model_1_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_poisson_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_poisson_female_model_1 <- extract_results_pr( results_cc_age_coef_female, "model_1_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_pr_poisson_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_poisson_model_1 <- rbind( results_cc_age_pr_poisson_male_model_1[ c( 1:3 ), ], results_cc_age_pr_poisson_female_model_1[ c( 1:3 ), ] )
colnames( results_cc_age_by_sex_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_age_by_sex_pr_poisson_model_1 )[-1], "_model_1")

results_cc_age_by_sex_pr_poisson_model_2 <- rbind( results_cc_age_pr_poisson_male_model_2[ c( 1:3 ), ], results_cc_age_pr_poisson_female_model_2[ c( 1:3 ), ] )
colnames( results_cc_age_by_sex_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_age_by_sex_pr_poisson_model_2 )[-1], "_model_2" )

results_cc_age_by_sex_pr_poisson <- merge( results_cc_age_by_sex_pr_poisson_model_1, results_cc_age_by_sex_pr_poisson_model_2, by = "Exposure" )


# results from log binomial regression
results_cc_age_pr_log_binomial_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_log_binomial", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_log_binomial_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_log_binomial", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_log_binomial_model_2 <- rbind( results_cc_age_pr_log_binomial_male_model_2[ c( 1:3 ), ], 
                                                        results_cc_age_pr_log_binomial_female_model_2[ c( 1:3 ), ] )


# results from logistic regression
results_cc_age_pr_logistic_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_logistic", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_logistic_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_logistic", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_logistic_model_2 <- rbind( results_cc_age_pr_logistic_male_model_2[ c( 1:3 ), ], 
                                                    results_cc_age_pr_logistic_female_model_2[ c( 1:3 ), ] )


##### exposure of interest: sex #####

# extract coefficient and 95% CI
results_cc_sex_coef <- list()

for ( outcome in names( all_models_cc$sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_sex_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "sex", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_sex
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_sex_pr_poisson_model_1 <- extract_results_pr( results_cc_sex_coef, "model_1_poisson", identities, "sex" )
colnames( results_cc_sex_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_sex_pr_poisson_model_1 )[-1], "_model_1")

results_cc_sex_pr_poisson_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_poisson", identities, "sex" )
colnames( results_cc_sex_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_sex_pr_poisson_model_2 )[-1], "_model_2")

results_cc_sex_pr_poisson <- merge( results_cc_sex_pr_poisson_model_1, results_cc_sex_pr_poisson_model_2, by = "Exposure" )

results_cc_sex_pr_log_binomial_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_log_binomial", identities, "sex" )
results_cc_sex_pr_logistic_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_logistic", identities, "sex" )


##### exposure of interest: country of birth #####

# extract coefficient and 95% CI
results_cc_country_of_birth_coef <- list()

for ( outcome in names( all_models_cc$country_of_birth ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_country_of_birth_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "country_of_birth", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_country_of_birth
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_country_of_birth_pr_poisson_model_1 <- extract_results_pr( results_cc_country_of_birth_coef, "model_1_poisson", identities, "country_of_birth" )
colnames( results_cc_country_of_birth_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_country_of_birth_pr_poisson_model_1 )[-1], "_model_1")

results_cc_country_of_birth_pr_poisson_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_poisson", identities, "country_of_birth" )
colnames( results_cc_country_of_birth_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_country_of_birth_pr_poisson_model_2 )[-1], "_model_2")

results_cc_country_of_birth_pr_poisson <- merge( results_cc_country_of_birth_pr_poisson_model_1, results_cc_country_of_birth_pr_poisson_model_2, by = "Exposure" )

results_cc_country_of_birth_pr_log_binomial_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_log_binomial", identities, "country_of_birth" )
results_cc_country_of_birth_pr_logistic_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_logistic", identities, "country_of_birth" )


##### exposure of interest: education #####

# extract coefficient and 95% CI
results_cc_education_coef <- list()

for ( outcome in names( all_models_cc$education ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_education_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "education", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_education
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_education_pr_poisson_model_1 <- extract_results_pr( results_cc_education_coef, "model_1_poisson", identities, "education" )
colnames( results_cc_education_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_education_pr_poisson_model_1 )[-1], "_model_1")

results_cc_education_pr_poisson_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_poisson", identities, "education" )
colnames( results_cc_education_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_education_pr_poisson_model_2 )[-1], "_model_2")

results_cc_education_pr_poisson <- merge( results_cc_education_pr_poisson_model_1, results_cc_education_pr_poisson_model_2, by = "Exposure" )

results_cc_education_pr_log_binomial_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_log_binomial", identities, "education" )
results_cc_education_pr_logistic_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_logistic", identities, "education" )


##### exposure of interest: income #####

# extract coefficient and 95% CI
results_cc_income_coef <- list()

for ( outcome in names( all_models_cc$income ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_income_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "income", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_income
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_income_pr_poisson_model_1 <- extract_results_pr( results_cc_income_coef, "model_1_poisson", identities, "income" )
colnames( results_cc_income_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_income_pr_poisson_model_1 )[-1], "_model_1")

results_cc_income_pr_poisson_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_poisson", identities, "income" )
colnames( results_cc_income_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_income_pr_poisson_model_2 )[-1], "_model_2")

results_cc_income_pr_poisson <- merge( results_cc_income_pr_poisson_model_1, results_cc_income_pr_poisson_model_2, by = "Exposure" )

results_cc_income_pr_log_binomial_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_log_binomial", identities, "income" )
results_cc_income_pr_logistic_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_logistic", identities, "income" )


##### exposure of interest: marital status #####

# extract coefficient and 95% CI
results_cc_marital_status_coef <- list()

for ( outcome in names( all_models_cc$marital_status ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_marital_status_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "marital_status", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_marital_status
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_marital_status_pr_poisson_model_1 <- extract_results_pr( results_cc_marital_status_coef, "model_1_poisson", identities, "marital_status" )
colnames( results_cc_marital_status_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_marital_status_pr_poisson_model_1 )[-1], "_model_1")

results_cc_marital_status_pr_poisson_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_poisson", identities, "marital_status" )
colnames( results_cc_marital_status_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_marital_status_pr_poisson_model_2 )[-1], "_model_2")

results_cc_marital_status_pr_poisson <- merge( results_cc_marital_status_pr_poisson_model_1, results_cc_marital_status_pr_poisson_model_2, by = "Exposure" )

results_cc_marital_status_pr_log_binomial_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_log_binomial", identities, "marital_status" )
results_cc_marital_status_pr_logistic_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_logistic", identities, "marital_status" )


##### combine results #####

results_cc_pr_crude <- rbind( results_cc_age_pr_crude,
                              results_cc_age_by_sex_pr_crude,
                              results_cc_sex_pr_crude,
                              results_cc_country_of_birth_pr_crude,
                              results_cc_education_pr_crude,
                              results_cc_income_pr_crude,
                              results_cc_marital_status_pr_crude
)

results_cc_pr_poisson <- rbind( results_cc_age_pr_poisson,
                                results_cc_age_by_sex_pr_poisson,
                                results_cc_sex_pr_poisson,
                                results_cc_country_of_birth_pr_poisson,
                                results_cc_education_pr_poisson,
                                results_cc_income_pr_poisson,
                                results_cc_marital_status_pr_poisson
)

writexl::write_xlsx( merge( results_cc_pr_crude, results_cc_pr_poisson, by = "Exposure" ),
                     "results_cc_pr_poisson_2021.xlsx" )

results_cc_pr_log_binomial <- rbind( results_cc_age_pr_log_binomial_model_2,
                                     results_cc_age_by_sex_pr_log_binomial_model_2,
                                     results_cc_sex_pr_log_binomial_model_2,
                                     results_cc_country_of_birth_pr_log_binomial_model_2,
                                     results_cc_education_pr_log_binomial_model_2,
                                     results_cc_income_pr_log_binomial_model_2,
                                     results_cc_marital_status_pr_log_binomial_model_2
)

results_cc_pr_logistic <- rbind( results_cc_age_pr_logistic_model_2,
                                 results_cc_age_by_sex_pr_logistic_model_2,
                                 results_cc_sex_pr_logistic_model_2,
                                 results_cc_country_of_birth_pr_logistic_model_2,
                                 results_cc_education_pr_logistic_model_2,
                                 results_cc_income_pr_logistic_model_2,
                                 results_cc_marital_status_pr_logistic_model_2
)

colnames( results_cc_pr_poisson )[-1] <- paste0( colnames( results_cc_pr_poisson )[-1], "_poisson")
colnames( results_cc_pr_log_binomial )[-1] <- paste0( colnames( results_cc_pr_log_binomial )[-1], "_log_binomial")
colnames( results_cc_pr_logistic )[-1] <- paste0( colnames( results_cc_pr_logistic )[-1], "_logistic")

results_cc_pr_all_models_2021 <- results_cc_pr_poisson %>%
  full_join( results_cc_pr_log_binomial, by = "Exposure" ) %>%
  full_join( results_cc_pr_logistic, by = "Exposure" )

writexl::write_xlsx( results_cc_pr_all_models_2021, "results_cc_pr_all_models_2021.xlsx" )
```

```{r}
# fit the substantive model to each of the imputed data sets
fit.imp <- with( imp.list, lmer( english ~ ravens + sex + fluent + ( 1|school ) ) )

# pool results
testEstimates(fit.imp, var.comp = TRUE) # Many different pooling methods are supported by mitml
```