---
title: "Self-reported sexual identity in Stockholm County in 2014"
author: Guoqiang Zhang
email: guoqiang.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages
```{r}
library(haven)
library(data.table)
library(naniar)
library(bayesrules)
library(rstan)
library(rstanarm)
library(bayesplot)
library(tidyverse)
library(brms)
library(jomo)
library(mitml)
library(mitools)
library(epiR)
library(nnet)
library(ggplot2)
library(ggbreak)
library(mice)
library(ggrepel)
library(ggpubr)
library(ggmosaic)
library(tidyr)
library(dplyr)
library(finalfit)
library(survey)
library(svyVGAM)
```

### 2. Import and Visualise Data
```{r}
# d_2014 <- read_sas("G:/CES/SRHR/SPHC LGBTQ health data/sphc14_21.sas7bdat")

# sampling strata
n_miss( d_2014$stratum )
d_2014$sampling_strata <- as.factor( d_2014$stratum )
length( unique( d_2014$sampling_strata ) ) # 39 strata

d_2014 <- d_2014 %>%
  mutate( sampling_strata_region = recode( sampling_strata, 
                                           `3101` = "Upplands Väsby",
                                           `3102` = "Vallentuna",
                                           `3103` = "Österåker",
                                           `3104` = "Värmdö",
                                           `3105` = "Järfälla",
                                           `3106` = "Ekerö",
                                           `3107` = "Huddinge",
                                           `3108` = "Botkyrka",
                                           `3109` = "Salem",
                                           `3110` = "Haninge",
                                           `3111` = "Tyresö",
                                           `3112` = "Upplands-Bro",
                                           `3113` = "Nykvarn",
                                           `3114` = "Täby",
                                           `3115` = "Danderyd",
                                           `3116` = "Sollentuna",
                                           `3117` = "Södertälje",
                                           `3118` = "Nacka",
                                           `3119` = "Sundbyberg",
                                           `3120` = "Solna",
                                           `3121` = "Lidingö",
                                           `3122` = "Vaxholm",
                                           `3123` = "Norrtälje",
                                           `3124` = "Sigtuna",
                                           `3125` = "Nynäshamn",
                                           `3201` = "Rinkeby-Kista",
                                           `3202` = "Spånga-Tensta",
                                           `3203` = "Hässelby-Vällingby",
                                           `3204` = "Bromma",
                                           `3205` = "Kungsholmen",
                                           `3206` = "Norrmalm",
                                           `3207` = "Östermalm",
                                           `3208` = "Södermalm",
                                           `3209` = "Enskede, Årsta-Vantör",
                                           `3210` = "Skarpnäck",
                                           `3211` = "Farsta",
                                           `3212` = "Älvsjö",
                                           `3213` = "Hägersten-Liljeholmen",
                                           `3214` = "Skärholmen"
                                           ) )

# sexual identity
table( d_2014$F14U90G82, useNA = "always" )
d_2014$sexual_identity <- factor( ifelse( d_2014$F14U90G82 == 1, "Heterosexual", 
                                          ifelse( d_2014$F14U90G82 == 2, "Homosexual",
                                                  ifelse( d_2014$F14U90G82 == 3, "Bisexual", "None of the above" ) ) ),
                                  levels = c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" ) )
table( d_2014$sexual_identity, useNA = "always" )

# sex
table( d_2014$kon, useNA = "always" )
d_2014$sex <- factor( ifelse( d_2014$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2014$sex, useNA = "always" )

# age
summary( d_2014$F14alder )
d_2014$age <- d_2014$F14alder
d_2014$age_cat <- factor( ifelse( d_2014$age <= 29, "16-29", 
                                  ifelse( d_2014$age >=30 & d_2014$age <= 44, "30-44",
                                          ifelse( d_2014$age >= 45 & d_2014$age <= 59, "45-59", ">=60" ) ) ),
                          levels = c( "16-29", "30-44", "45-59", ">=60" ) )
table( d_2014$age_cat, useNA = "always" )

# interaction term between age and sex
d_2014$age_sex <- interaction( d_2014$age_cat, d_2014$sex )

# country of birth
table( d_2014$fodelseland, useNA = "always" )
d_2014$country_of_birth <- factor( ifelse( d_2014$fodelseland == "Afrika", "Africa",
                                           ifelse( d_2014$fodelseland == "Asien", "Asia",
                                                   ifelse( d_2014$fodelseland == "Europa", "Europe",
                                                           ifelse( d_2014$fodelseland == "Sverige", "Sweden", "Americas" ) ) ) ),
                                   levels = c( "Africa", "Americas", "Asia", "Europe", "Sweden" ) )
table( d_2014$country_of_birth, useNA = "always" )

# education
table( d_2014$utbniva2014, useNA = "always" )
d_2014$education <- factor( ifelse( d_2014$utbniva2014 <= 2, "<=9 years",
                                    ifelse( d_2014$utbniva2014 <= 4, "10-12 years", ">=13 years" ) ),
                            levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
table( d_2014$education, useNA = "always" )

# occupation
table( d_2014$SSYK_kl, useNA = "always" )
d_2014$occupation <- factor(
  ifelse(
    d_2014$SSYK_kl == "Yrken inom byggverksamhet och tillverkning" |
      d_2014$SSYK_kl == "Yrken inom lantbruk, trädgård, skogsbruk och fiske" |
      d_2014$SSYK_kl == "Yrken inom maskinell tillverkning och transport m.m.",
    "Manual and field trades",
    ifelse(
      d_2014$SSYK_kl == "Service-, omsorgs- och försäljningsyrken" |
        d_2014$SSYK_kl == "Yrken inom administration och kundtjänst" |
        d_2014$SSYK_kl == "Yrken med krav på kortare utbildning eller introduktion",
      "Service and support",
      ifelse(
        d_2014$SSYK_kl == "Yrken med krav på fördjupad högskolekompetens" |
          d_2014$SSYK_kl == "Yrken med krav på högskolekompetens eller motsvarande" |
          d_2014$SSYK_kl == "Chefsyrken" |
          d_2014$SSYK_kl == "Militära yrken",
        "Expertise and leadership",
        NA
      )
    )
  ),
  levels = c(
    "Manual and field trades",
    "Service and support",
    "Expertise and leadership"
  )
)
table( d_2014$occupation, useNA = "always" )

# disposable income
summary( d_2014$dispink2014, useNA = "always" )
d_2014$dispink2014[ d_2014$dispink2014 < 0 ] <- NA
d_2014$income <- factor( ifelse( d_2014$dispink2014 <= 2500, "<=2,500",
                                 ifelse( d_2014$dispink2014 > 2500 & d_2014$dispink2014 <= 3500, "(2,500, 3,500]",
                                         ifelse( d_2014$dispink2014 > 3500 & d_2014$dispink2014 <= 4500, "(3,500, 4,500]", ">4,500" ) ) ),
                         levels = c( "<=2,500", "(2,500, 3,500]", "(3,500, 4,500]", ">4,500" ) )
table( d_2014$income, useNA = "always" )

# marital status
table( d_2014$civil2014, useNA = "always" )
d_2014$marital_status <- factor( ifelse( d_2014$civil2014 == "G" | d_2014$civil2014 == "RP", "Currently married",
                                         ifelse( d_2014$civil2014 == "OG", "Never married", "Other" ) ),
                                 levels = c( "Never married", "Currently married", "Other" ) )
table( d_2014$marital_status, useNA = "always" )

# living alone
table( d_2014$F14U52aG58a, useNA = "always" )
d_2014$living_alone <- factor( ifelse( d_2014$F14U52aG58a == 1, "no", "yes" ), 
                               levels = c( "yes", "no" ) )
table( d_2014$living_alone, useNA = "always" )

# personal support
table( d_2014$F14U56G66, useNA = "always" )
d_2014$personal_support <- factor( ifelse( d_2014$F14U56G66 <= 2, "yes", "no" ), 
                                   levels = c( "yes", "no" ) )
table( d_2014$personal_support, useNA = "always" )


##### demographic characteristics #####

# among respondents (n = 22,250)
# make characteristics table by sexual identity
explanatory =  c( "sex", "age_cat", "country_of_birth", "education", "occupation", "income", "marital_status", "living_alone", "personal_support" )
dependent = "sexual_identity"
d_2014_table <- d_2014 %>% 
  summary_factorlist( dependent,
                      explanatory, 
                      na_include = TRUE,
                      na_include_dependent = TRUE, 
                      total_col = TRUE,
                      add_col_totals = TRUE )

# Fisher's test
x1 <- table( d_2014$sex, d_2014$sexual_identity )
x1
format( round( fisher.test( x1[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x2 <- table( d_2014$age_cat, d_2014$sexual_identity )
x2
format( round( fisher.test( x2[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x3 <- table( d_2014$country_of_birth, d_2014$sexual_identity )
x3
format( round( fisher.test( x3[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x4 <- table( d_2014$education, d_2014$sexual_identity )
x4
format( round( fisher.test( x4[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x5 <- table( d_2014$income, d_2014$sexual_identity )
x5
format( round( fisher.test( x5[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x6 <- table( d_2014$marital_status, d_2014$sexual_identity )
x6
format( round( fisher.test( x6[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x7 <- table( d_2014$living_alone, d_2014$sexual_identity )
x7
format( round( fisher.test( x7[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x8 <- table( d_2014$personal_support, d_2014$sexual_identity )
x8
format( round( fisher.test( x8[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x8[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x8[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x9 <- table( d_2014$occupation, d_2014$sexual_identity )
x9
format( round( fisher.test( x9[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x9[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x9[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )


##### design weights #####

summary( d_2014$F14dvikt )
d_2014$design_weight <- d_2014$F14dvikt


##### non-response #####

# unit non-response
d_2014$design_weight_unit_nonresponse <- d_2014$F14dbvikt # weights calculated assuming Missing Completely At Random (MCAR) within each stratum
summary( d_2014$design_weight_unit_nonresponse )
sum( d_2014$design_weight_unit_nonresponse ) # No. of source population = 1,764,671

unitresponse_prob <- d_2014 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( unitresponse_prob = unique( design_weight ) / unique( design_weight_unit_nonresponse ),
             no.of.population = sum( design_weight_unit_nonresponse ),
             sample_size = unique( no.of.population )/unique( design_weight ) ) # calculate overall unit response rate, and no. of population and sample size within each stratum

d_2014 <- d_2014 %>% 
  left_join( unitresponse_prob, by = "sampling_strata_region" )

# item non-response
itemresponse_prob <- d_2014 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( itemresponse_prob = sum( !is.na( sexual_identity ) ) / n() ) # calculate item response rate

d_2014 <- d_2014 %>% 
  left_join( itemresponse_prob, by = "sampling_strata_region" ) %>% 
  mutate( itemresponse_prob = ifelse( is.na( sexual_identity ), 0, itemresponse_prob ) )


##### summary of stratified sampling #####

sampling_frame_2014 <- as.data.frame( d_2014 %>% 
                                   group_by( sampling_strata_region ) %>% 
                                   reframe( no.of.population = unique( no.of.population ), 
                                            sample_size = unique( no.of.population/design_weight ),
                                            unitresponse = n(),
                                            itemresponse = sum( itemresponse_prob != 0 ) ) )

sampling_frame_2014$unitresponse_rate <- sampling_frame_2014$unitresponse/sampling_frame_2014$sample_size
sampling_frame_2014$itemresponse_rate <- sampling_frame_2014$itemresponse/sampling_frame_2014$unitresponse
sampling_frame_2014$overallresponse_rate <- sampling_frame_2014$itemresponse/sampling_frame_2014$sample_size

sampling_frame_2014$unitresponse_label <- paste0( sampling_frame_2014$unitresponse, " (", 
                                             sprintf( "%.1f", sampling_frame_2014$unitresponse_rate*100 ), "%)" )
sampling_frame_2014$overallresponse_label <- paste0( sampling_frame_2014$itemresponse, " (", 
                                                sprintf( "%.1f", sampling_frame_2014$overallresponse_rate*100 ), "%)" )

round( weighted.mean( sampling_frame_2014$unitresponse_rate, sampling_frame_2014$no.of.population ), 3 ) # overall unit response rate
round( weighted.mean( sampling_frame_2014$itemresponse_rate, sampling_frame_2014$no.of.population ), 3 ) # overall item response rate
round( weighted.mean( sampling_frame_2014$overallresponse_rate, sampling_frame_2014$no.of.population ), 3 ) # overall response rate

writexl::write_xlsx( sampling_frame_2014, "sampling_frame_2014.xlsx" )


##### calibrated weights #####

d_2014$calibrated_weight <- d_2014$F14kalvikt

# visualize calibrated weights across sampling strata
ggplot( d_2014 %>% 
          group_by( sampling_strata_region ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( sampling_strata_region, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 260 ), breaks = c( 0, 50, 100, 150, 200, 250 ), expand = c( 0, 0 ) ) +
  labs( y = NULL, x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ) )


##### replicating non-respondent rows for sampling design #####

# because d_2014 includes data only for respondents (unit response), we need to duplicate rows for non-respondents
# so that the final dataset represents the sampling process
rows_to_add <- d_2014 %>%
  group_by( sampling_strata_region ) %>%
  summarise( to_add = unique( sample_size ) - n(),
             no.of.population = unique( no.of.population ),
             sample_size = unique( sample_size ),
             design_weight = unique( design_weight ) )

sum( rows_to_add$to_add ) # 30,787 non-respondents

rows_to_add$to_add <- round( rows_to_add$to_add ) # to resolve floating-point precision issues

replicated_rows <- rows_to_add[ rep( row.names( rows_to_add ), rows_to_add$to_add ), c( 1, 3:5 ) ]

d_2014_complete <- bind_rows( d_2014, replicated_rows ) # 53,037 individuals in the original sample
```

### 3. Estimation of Proportions of Sexual Identities
#### 3.1. Complete-case analysis
##### 3.1.1. Define survey design
```{r}
# prepare dataset
d_2014_complete_cc <- d_2014_complete

d_2014_complete_cc$country_of_birth <- factor( 
  ifelse( d_2014_complete_cc$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2014_complete_cc$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

d_2014_complete_cc$living_alone <- as.factor(
  ifelse( d_2014_complete_cc$living_alone == "yes", 
          "living_alone_yes",
          "living_alone_no" )
  )

d_2014_complete_cc$personal_support <- as.factor(
  ifelse( d_2014_complete_cc$personal_support == "yes", 
          "personal_support_yes",
          "personal_support_no" ) 
  )

# create survey design
survey_design_cc <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ design_weight,
                               fpc = ~ no.of.population,
                               data = d_2014_complete_cc )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

# the following analyses assume MCAR
``` 

##### 3.1.2. By sex
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                        by = ~ sex,
                        design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( sex ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_sex
}

prop_cc_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_sex <- left_join( prop_cc_sex,
                          d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$sex ), ] %>% 
                            group_by( subgroup = sex ) %>% 
                            summarise( sample_size_2014 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.3. By age group
###### 3.1.3.1. Calculate proportion by pre-specified age cut-off
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                        by = ~ age_cat,
                        design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( age_cat ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_age ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_age
}

prop_cc_age <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age <- left_join( prop_cc_age,
                          d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$age_cat ), ] %>% 
                            group_by( subgroup = age_cat ) %>% 
                            summarise( sample_size_2014 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

###### 3.1.3.2. Calculate proportion ratio by varying age cut-offs
```{r}
d_2014_iteration_age <- d_2014_complete

min_age <- min( d_2014_iteration_age$age, na.rm = TRUE )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

results_df <- data.frame()

for ( cut_off in ( min_age ):90 ) {
  d_2014_iteration_age$age_iteration <- ifelse( d_2014_iteration_age$age <= cut_off, "young", "old" )
  
  survey_design_iteration_age <- svydesign( ids = ~ 1, 
                                            strata = ~ sampling_strata_region,
                                            weights = ~ design_weight,
                                            fpc = ~ no.of.population,
                                            data = d_2014_iteration_age )
  
  list_of_df <- list()
  
  for ( cat in categories ) {
    prop_cc_age_iteration <- svyby(
      formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
      by = ~ age_iteration,
      design = subset( survey_design_iteration_age, !is.na( sexual_identity ) & !is.na( age ) ),
      FUN = svyciprop,
      method = "beta" )
    
    colnames( prop_cc_age_iteration ) <- c( "subgroup", 
                                            paste0( cat, "_point_estimate_2014" ), 
                                            paste0( cat, "_se_2014" ) )
    
    list_of_df[[cat]] <- prop_cc_age_iteration
  }
  
  prop_cc_age_iteration_merged <- Reduce( function( df1, df2 ) { 
    merge( df1, df2, by = "subgroup" ) 
    }, 
    list_of_df
    )
  
  prop_cc_age_iteration_merged$cut_off <- cut_off
  
  results_df <- rbind( results_df, prop_cc_age_iteration_merged )
  }

results_wide <- results_df %>%
  select( -ends_with( "_se_2014" ) ) %>%
  pivot_wider( names_from = subgroup, 
               values_from = c( Heterosexual_point_estimate_2014, 
                                Homosexual_point_estimate_2014, 
                                Bisexual_point_estimate_2014, 
                                `None of the above_point_estimate_2014` ) 
               )

colnames( results_wide ) <- gsub( "_point_estimate_2014", "", colnames( results_wide ) )

results_wide$Heterosexual_pr_2014 <- results_wide$Heterosexual_young/results_wide$Heterosexual_old
results_wide$Homosexual_pr_2014 <- results_wide$Homosexual_young/results_wide$Homosexual_old
results_wide$Bisexual_pr_2014 <- results_wide$Bisexual_young/results_wide$Bisexual_old
results_wide$`None of the above_pr_2014` <- results_wide$`None of the above_young`/results_wide$`None of the above_old`

results_wide$Heterosexual_pr_2014[ is.infinite( results_wide$Heterosexual_pr_2014 ) ] <- NA
results_wide$Homosexual_pr_2014[ is.infinite( results_wide$Homosexual_pr_2014 ) ] <- NA
results_wide$Bisexual_pr_2014[ is.infinite( results_wide$Bisexual_pr_2014 ) ] <- NA
results_wide$`None of the above_pr_2014`[ is.infinite( results_wide$`None of the above_pr_2014` ) ] <- NA

writexl::write_xlsx( results_wide, "prop_cc_age_iteration_2014.xlsx" )
```

##### 3.1.4. By sex*age group
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                            by = ~ age_sex,
                            design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( age_sex ) ),
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_age_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_age_sex
}

prop_cc_age_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age_sex <- left_join( prop_cc_age_sex,
                              d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$age_sex ), ] %>% 
                                group_by( subgroup = age_sex ) %>% 
                                summarise( sample_size_2014 = n() ),
                              by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.5. By education
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_education <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                              by = ~ education,
                              design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( education ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_education ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_education
}

prop_cc_education <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_education <- left_join( prop_cc_education,
                                d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$education ), ] %>% 
                                  group_by( subgroup = education ) %>% 
                                  summarise( sample_size_2014 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.6. By occupation
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_occupation <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                              by = ~ occupation,
                              design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( occupation ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_occupation ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_occupation
}

prop_cc_occupation <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_occupation <- left_join( prop_cc_occupation,
                                d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                                      !is.na( d_2014_complete_cc$occupation ), ] %>% 
                                  group_by( subgroup = occupation ) %>% 
                                  summarise( sample_size_2014 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.7. By income
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_income <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                           by = ~ income,
                           design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( income ) ),
                           FUN = svyciprop,
                           vartype = "ci",
                           method = "beta" )
  
  colnames( prop_cc_income ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_income
}

prop_cc_income <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_income <- left_join( prop_cc_income,
                             d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$income ), ] %>% 
                               group_by( subgroup = income ) %>% 
                               summarise( sample_size_2014 = n() ),
                             by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.8. By country of birth
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_country_of_birth <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                     by = ~ country_of_birth,
                                     design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( country_of_birth ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_country_of_birth ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_country_of_birth
}

prop_cc_country_of_birth <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_country_of_birth <- left_join( prop_cc_country_of_birth,
                                       d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$country_of_birth ), ] %>% 
                                         group_by( subgroup = country_of_birth ) %>% 
                                         summarise( sample_size_2014 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.9. By marital status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_marital_status <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                   by = ~ marital_status,
                                   design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( marital_status ) ),
                                   FUN = svyciprop,
                                   vartype = "ci",
                                   method = "beta" )
  
  colnames( prop_cc_marital_status ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_marital_status
}

prop_cc_marital_status <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_marital_status <- left_join( prop_cc_marital_status,
                                     d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$marital_status ), ] %>% 
                                       group_by( subgroup = marital_status ) %>% 
                                       summarise( sample_size_2014 = n() ),
                                     by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.10. By living status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_living_alone <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                 by = ~ living_alone,
                                 design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( living_alone ) ),
                                 FUN = svyciprop,
                                 vartype = "ci",
                                 method = "beta" )
  
  colnames( prop_cc_living_alone ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_living_alone
}

prop_cc_living_alone <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_living_alone <- left_join( prop_cc_living_alone,
                                   d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$living_alone ), ] %>% 
                                     group_by( subgroup = living_alone ) %>% 
                                     summarise( sample_size_2014 = n() ),
                                   by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.11. By personal support
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_personal_support <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                     by = ~ personal_support,
                                     design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( personal_support ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_personal_support ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_personal_support
}

prop_cc_personal_support <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_personal_support <- left_join( prop_cc_personal_support,
                                       d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ) &
                                             !is.na( d_2014_complete_cc$personal_support ), ] %>% 
                                         group_by( subgroup = personal_support ) %>% 
                                         summarise( sample_size_2014 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )

```

##### 3.1.12. Overall proportions of sexual identities in Stockholm County
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                design = subset( survey_design_cc, !is.na( sexual_identity ) ),
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_overall
}

prop_cc_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
}, 
list_of_df ) %>% 
  as.data.frame() %>%
  rownames_to_column( var = "subgroup" )

prop_cc_overall[ 1, 1 ] <- "Stockholm County"

prop_cc_overall <- bind_cols( prop_cc_overall,
                              d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity ), ] %>% 
                                summarise( sample_size_2014 = n() ) ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.13. Merge datasets
```{r}
prop_cc_summary_2014 <- rbind( prop_cc_sex, 
                               prop_cc_age,
                               prop_cc_age_sex,
                               prop_cc_education,
                               prop_cc_occupation,
                               prop_cc_income, 
                               prop_cc_country_of_birth, 
                               prop_cc_marital_status,
                               prop_cc_living_alone,
                               prop_cc_personal_support,
                               prop_cc_overall 
)

writexl::write_xlsx( prop_cc_summary_2014, "prop_cc_summary_2014.xlsx" )
```

#### 3.2. Multiple impuation and inverse probability weighting
```{r}

```

### 4. Relation between Sexual Identity and Demographic Factors
#### 4.1. Complete-case analysis
```{r}
##### prepare dataset #####

# calculate item response rate among those who had complete data on all variables included in the model
itemresponse_prob_mlr <- d_2014 %>%
  group_by( sampling_strata_region ) %>%
  summarise( itemresponse_prob_mlr = 
               sum( !is.na( sexual_identity ) & # only sexual identity, education and income have missing values
                      !is.na( income ) &
                      !is.na( education ) ) / n()
             )

d_2014 <- d_2014 %>% 
  left_join( itemresponse_prob_mlr, by = "sampling_strata_region" ) %>% 
  mutate( itemresponse_prob_mlr = ifelse( is.na( sexual_identity ) | is.na( education ) | is.na( income ), 0,
                                          itemresponse_prob_mlr ) )

# adjust design weights to take into account both unit and item non-response
# assume MCAR within each sampling stratum
d_2014$design_weight_unit_item_nonresponse_mlr <- ifelse( d_2014$itemresponse_prob_mlr == 0, 0,
                                                          d_2014$design_weight_unit_nonresponse*( 1/d_2014$itemresponse_prob_mlr ) )

# extract variables
d_2014_cc_mlr <- as.data.frame( d_2014[ !is.na( d_2014$sexual_identity ) &
                                          !is.na( d_2014$income ) &
                                          !is.na( d_2014$education ), ] %>% 
                                  select( "sampling_strata_region", "no.of.population", "design_weight_unit_item_nonresponse_mlr", "sexual_identity", "age_cat", "age", "sex", "country_of_birth", "education", "income", "marital_status" ) )

d_2014_cc_mlr$country_of_birth <- factor( ifelse( d_2014_cc_mlr$country_of_birth == "Sweden", "Sweden",
                                                  ifelse( d_2014_cc_mlr$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
                                          levels = c( "Sweden", "Europe", "Outside Europe" ) )

d_2014_cc_mlr$marital_status <- relevel( d_2014_cc_mlr$marital_status, ref = "Currently married" )

n_miss( d_2014_cc_mlr ) # 0 missing
summary( d_2014_cc_mlr )


##### Define design objects #####

# define design object 1
survey_design_cc_mlr_1 <- svydesign( ids = ~ 1, 
                                     strata = ~ sampling_strata_region,
                                     weights = ~ design_weight_unit_item_nonresponse_mlr,
                                     fpc = ~ no.of.population,
                                     data = d_2014_cc_mlr )

# define design object 2
# change reference category of predictors
d_2014_cc_mlr$age_cat <- relevel( d_2014_cc_mlr$age_cat, ref = ">=60" )
d_2014_cc_mlr$sex <- relevel( d_2014_cc_mlr$sex, ref = "Female" )
d_2014_cc_mlr$education <- relevel( d_2014_cc_mlr$education, ref = ">=13 years" )
d_2014_cc_mlr$income <- relevel( d_2014_cc_mlr$income, ref = ">4,500" )
d_2014_cc_mlr$marital_status <- relevel( d_2014_cc_mlr$marital_status, ref = "Never married" )

summary( d_2014_cc_mlr )

survey_design_cc_mlr_2 <- svydesign( ids = ~ 1, 
                                     strata = ~ sampling_strata_region,
                                     weights = ~ design_weight_unit_item_nonresponse_mlr,
                                     fpc = ~ no.of.population,
                                     data = d_2014_cc_mlr )


##### Fit weighted MLR models #####

fml_mlr <- sexual_identity ~ age_cat + sex + age_cat*sex + education + country_of_birth + income + marital_status + sampling_strata_region

# fit MLR model 1
model_mlr_cc_1 <- svy_vglm( fml_mlr, 
                            design = survey_design_cc_mlr_1, 
                            family = multinomial( refLevel = "Heterosexual" )
                            )

model_mlr_cc_output_1 <- merge( summary( model_mlr_cc_1 )[[ "coeftable" ]] %>% 
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ),
                                confint( model_mlr_cc_1 ) %>%
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ), 
                                by = "category" ) %>%
  select( "category", "Coef", "2.5 %", "97.5 %", "p" ) %>%
  mutate(
    OR_2014 = exp( Coef ),
    lower_ci_2014 = exp( `2.5 %` ),
    upper_ci_2014 = exp( `97.5 %` ) ) %>%
  rename(
    category_2014 = category,
    p_2014 = p
    )

levels( survey_design_cc_mlr_1$variables$sexual_identity )
new_cats <- c( "Homosexual", "Bisexual", "None of the above" )

for ( i in 1:3 ) {
  model_mlr_cc_output_1$category_2014 <- gsub(
    pattern = paste0( ":", i ), 
    replacement = paste0( "_", new_cats[i] ), 
    x = model_mlr_cc_output_1$category_2014 )
  }

model_mlr_cc_output_1_wide <- model_mlr_cc_output_1 %>%
  separate( category_2014, into = c( "category_2014", "sexual_identity" ), 
            sep = "_(?=[^_]+$)",
            extra = "merge" ) %>%
  pivot_wider(
    names_from = sexual_identity, 
    values_from = c( Coef, `2.5 %`, `97.5 %`, p_2014, OR_2014, lower_ci_2014, upper_ci_2014 )
    )

model_mlr_cc_output_1_wide <- model_mlr_cc_output_1_wide %>% select( "category_2014", "Coef_Homosexual", "2.5 %_Homosexual", "97.5 %_Homosexual", "p_2014_Homosexual", "OR_2014_Homosexual", "lower_ci_2014_Homosexual", "upper_ci_2014_Homosexual", "Coef_Bisexual", "2.5 %_Bisexual", "97.5 %_Bisexual", "p_2014_Bisexual", "OR_2014_Bisexual", "lower_ci_2014_Bisexual", "upper_ci_2014_Bisexual", "Coef_None of the above", "2.5 %_None of the above", "97.5 %_None of the above", "p_2014_None of the above", "OR_2014_None of the above", "lower_ci_2014_None of the above", "upper_ci_2014_None of the above" )

# writexl::write_xlsx( model_mlr_cc_output_1_wide, "model_mlr_cc_output_1_wide_2014.xlsx" )


# fit MLR model 2
model_mlr_cc_2 <- svy_vglm( fml_mlr, 
                            design = survey_design_cc_mlr_2, 
                            family = multinomial( refLevel = "Heterosexual" )
                            )

model_mlr_cc_output_2 <- merge( summary( model_mlr_cc_2 )[[ "coeftable" ]] %>% 
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ),
                                confint( model_mlr_cc_2 ) %>%
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ), 
                                by = "category" ) %>%
  select( "category", "Coef", "2.5 %", "97.5 %", "p" ) %>%
  mutate(
    OR_2014 = exp( Coef ),
    lower_ci_2014 = exp( `2.5 %` ),
    upper_ci_2014 = exp( `97.5 %` ) ) %>%
  rename(
    category_2014 = category,
    p_2014 = p
    )

for ( i in 1:3 ) {
  model_mlr_cc_output_2$category_2014 <- gsub(
    pattern = paste0( ":", i ), 
    replacement = paste0( "_", new_cats[i] ), 
    x = model_mlr_cc_output_2$category_2014 )
  }

model_mlr_cc_output_2_wide <- model_mlr_cc_output_2 %>%
  separate( category_2014, into = c( "category_2014", "sexual_identity" ), 
            sep = "_(?=[^_]+$)",
            extra = "merge" ) %>%
  pivot_wider(
    names_from = sexual_identity, 
    values_from = c( Coef, `2.5 %`, `97.5 %`, p_2014, OR_2014, lower_ci_2014, upper_ci_2014 )
    )

model_mlr_cc_output_2_wide <- model_mlr_cc_output_2_wide %>% select( "category_2014", "Coef_Homosexual", "2.5 %_Homosexual", "97.5 %_Homosexual", "p_2014_Homosexual", "OR_2014_Homosexual", "lower_ci_2014_Homosexual", "upper_ci_2014_Homosexual", "Coef_Bisexual", "2.5 %_Bisexual", "97.5 %_Bisexual", "p_2014_Bisexual", "OR_2014_Bisexual", "lower_ci_2014_Bisexual", "upper_ci_2014_Bisexual", "Coef_None of the above", "2.5 %_None of the above", "97.5 %_None of the above", "p_2014_None of the above", "OR_2014_None of the above", "lower_ci_2014_None of the above", "upper_ci_2014_None of the above" )

save.image(file = "Preliminary_working_environment_2014.RData")
```