---
title: "Self-reported sexual identity in Stockholm County in 2014"
author: Guoqiang Zhang
email: guoqiang.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages
```{r}
library(haven)
library(data.table)
library(naniar)
library(bayesrules)
library(rstan)
library(rstanarm)
library(bayesplot)
library(tidyverse)
library(brms)
library(jomo)
library(mitml)
library(mitools)
library(epiR)
library(nnet)
library(ggplot2)
library(ggbreak)
library(mice)
library(ggrepel)
library(ggpubr)
library(ggmosaic)
library(tidyr)
library(dplyr)
library(finalfit)
library(survey)
library(svyVGAM)
source("/Users/guoqiang.zhang/Documents/Karolinska Institutet/Research Projects/Trends and Fluidity of Sexual Identity/Sexual_identity_in_Stockholm_County/Helper_functions.R") # helper function
```

### 2. Import and Visualise Data
```{r}
load("/Volumes/LGBT Project data/d_2014.RData")

# sampling strata
n_miss( d_2014$stratum )
d_2014$sampling_strata <- as.factor( d_2014$stratum )
length( unique( d_2014$sampling_strata ) ) # 39 strata

d_2014 <- d_2014 %>%
  mutate( sampling_strata_region = recode( sampling_strata, 
                                           `3101` = "Upplands-Väsby",
                                           `3102` = "Vallentuna",
                                           `3103` = "Österåker",
                                           `3104` = "Värmdö",
                                           `3105` = "Järfälla",
                                           `3106` = "Ekerö",
                                           `3107` = "Huddinge",
                                           `3108` = "Botkyrka",
                                           `3109` = "Salem",
                                           `3110` = "Haninge",
                                           `3111` = "Tyresö",
                                           `3112` = "Upplands-Bro",
                                           `3113` = "Nykvarn",
                                           `3114` = "Täby",
                                           `3115` = "Danderyd",
                                           `3116` = "Sollentuna",
                                           `3117` = "Södertälje",
                                           `3118` = "Nacka",
                                           `3119` = "Sundbyberg",
                                           `3120` = "Solna",
                                           `3121` = "Lidingö",
                                           `3122` = "Vaxholm",
                                           `3123` = "Norrtälje",
                                           `3124` = "Sigtuna",
                                           `3125` = "Nynäshamn",
                                           `3201` = "Rinkeby-Kista",
                                           `3202` = "Spånga-Tensta",
                                           `3203` = "Hässelby-Vällingby",
                                           `3204` = "Bromma",
                                           `3205` = "Kungsholmen",
                                           `3206` = "Norrmalm",
                                           `3207` = "Östermalm",
                                           `3208` = "Södermalm",
                                           `3209` = "Enskede-Årsta-Vantör",
                                           `3210` = "Skarpnäck",
                                           `3211` = "Farsta",
                                           `3212` = "Älvsjö",
                                           `3213` = "Hägersten-Liljeholmen",
                                           `3214` = "Skärholmen"
                                           ) )

# sexual identity in 2014
table( d_2014$F14U90G82, useNA = "always" )
d_2014$sexual_identity_2014 <- factor( ifelse( d_2014$F14U90G82 == 1, "Heterosexual",
                                                  ifelse( d_2014$F14U90G82 == 2, "Homosexual",
                                                          ifelse( d_2014$F14U90G82 == 3, "Bisexual", "None of the above" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" ) )
table( d_2014$sexual_identity_2014, useNA = "always" )

# sexual identity in 2021
table( d_2014$F21F91, useNA = "always" )
d_2014$sexual_identity_2021 <- factor( ifelse( d_2014$F21F91 == 1, "Heterosexual",
                                                  ifelse( d_2014$F21F91 == 2, "Homosexual",
                                                          ifelse( d_2014$F21F91 == 3, "Bisexual", "None of the above" ) ) ),
                                          levels = c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" ) )
table( d_2014$sexual_identity_2021, useNA = "always" )

# any change in sexual identity in 2014-2021
d_2014$sexual_identity_fluidity <- ifelse( d_2014$sexual_identity_2014 != d_2014$sexual_identity_2021, 1, 0 )

# sex
table( d_2014$kon, useNA = "always" )
d_2014$sex <- factor( ifelse( d_2014$kon == 1, "Male", "Female" ),
                      levels = c( "Male", "Female" ) )
table( d_2014$sex, useNA = "always" )

# age
summary( d_2014$F14alder )
d_2014$age <- d_2014$F14alder
d_2014$age_cat <- factor( ifelse( d_2014$age <= 29, "16-29", 
                                  ifelse( d_2014$age >=30 & d_2014$age <= 44, "30-44",
                                          ifelse( d_2014$age >= 45 & d_2014$age <= 59, "45-59", ">=60" ) ) ),
                          levels = c( "16-29", "30-44", "45-59", ">=60" ) )
table( d_2014$age_cat, useNA = "always" )

# interaction term between age and sex
d_2014$age_sex <- interaction( d_2014$age_cat, d_2014$sex )

# generation
d_2014$birth_year <- 2014 - d_2014$age
d_2014 <- d_2014 %>%
  mutate( generation = case_when(
    birth_year >= 1997 & birth_year <= 2012 ~ "Generation Z (1997–2012)",
    birth_year >= 1981 & birth_year <= 1996 ~ "Millennials (1981–1996)",
    birth_year >= 1965 & birth_year <= 1980 ~ "Generation X (1965–1980)",
    birth_year >= 1946 & birth_year <= 1964 ~ "Baby Boomers (1946–1964)",
    birth_year >= 1928 & birth_year <= 1945 ~ "Silent Generation (1928–1945)",
    birth_year >= 1901 & birth_year <= 1927 ~ "Greatest Generation (1901–1927)"
  ) )

d_2014$generation <- factor( 
  d_2014$generation, 
  levels = c( "Generation Z (1997–2012)", "Millennials (1981–1996)", "Generation X (1965–1980)", "Baby Boomers (1946–1964)", "Silent Generation (1928–1945)", "Greatest Generation (1901–1927)" ) )
summary( d_2014$generation )

# country of birth
table( d_2014$fodelseland, useNA = "always" )
d_2014$country_of_birth <- factor( ifelse( d_2014$fodelseland == "Afrika", "Africa",
                                           ifelse( d_2014$fodelseland == "Asien", "Asia",
                                                   ifelse( d_2014$fodelseland == "Europa", "Europe",
                                                           ifelse( d_2014$fodelseland == "Sverige", "Sweden", "Americas" ) ) ) ),
                                   levels = c( "Africa", "Americas", "Asia", "Europe", "Sweden" ) )
table( d_2014$country_of_birth, useNA = "always" )

# education
table( d_2014$utbniva2014, useNA = "always" )
d_2014$education <- factor( ifelse( d_2014$utbniva2014 <= 2, "<=9 years",
                                    ifelse( d_2014$utbniva2014 <= 4, "10-12 years", ">=13 years" ) ),
                            levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
table( d_2014$education, useNA = "always" )

# occupation
table( d_2014$SSYK_kl, useNA = "always" )
d_2014$occupation <- factor(
  ifelse(
    d_2014$SSYK_kl == "Yrken inom byggverksamhet och tillverkning" |
      d_2014$SSYK_kl == "Yrken inom lantbruk, trädgård, skogsbruk och fiske" |
      d_2014$SSYK_kl == "Yrken inom maskinell tillverkning och transport m.m.",
    "Manual and field trades",
    ifelse(
      d_2014$SSYK_kl == "Service-, omsorgs- och försäljningsyrken" |
        d_2014$SSYK_kl == "Yrken inom administration och kundtjänst" |
        d_2014$SSYK_kl == "Yrken med krav på kortare utbildning eller introduktion",
      "Service and support",
      ifelse(
        d_2014$SSYK_kl == "Yrken med krav på fördjupad högskolekompetens" |
          d_2014$SSYK_kl == "Yrken med krav på högskolekompetens eller motsvarande" |
          d_2014$SSYK_kl == "Chefsyrken" |
          d_2014$SSYK_kl == "Militära yrken",
        "Expertise and leadership",
        NA
      )
    )
  ),
  levels = c(
    "Manual and field trades",
    "Service and support",
    "Expertise and leadership"
  )
)
table( d_2014$occupation, useNA = "always" )

# disposable income
summary( d_2014$dispink2014, useNA = "always" )
d_2014$dispink2014[ d_2014$dispink2014 < 0 ] <- NA
d_2014$dispink2014 <- d_2014$dispink2014*( 1960/1790 ) # Consumer Price Index (CPI)-adjusted income
d_2014$income <- factor( ifelse( d_2014$dispink2014 <= 2500, "<=2,500",
                                 ifelse( d_2014$dispink2014 > 2500 & d_2014$dispink2014 <= 3500, "(2,500, 3,500]",
                                         ifelse( d_2014$dispink2014 > 3500 & d_2014$dispink2014 <= 4500, "(3,500, 4,500]", ">4,500" ) ) ),
                         levels = c( "<=2,500", "(2,500, 3,500]", "(3,500, 4,500]", ">4,500" ) )
table( d_2014$income, useNA = "always" )

# marital status
table( d_2014$civil2014, useNA = "always" )
d_2014$marital_status <- factor( ifelse( d_2014$civil2014 == "G" | d_2014$civil2014 == "RP", "Currently married",
                                         ifelse( d_2014$civil2014 == "OG", "Never married", "Other" ) ),
                                 levels = c( "Never married", "Currently married", "Other" ) )
table( d_2014$marital_status, useNA = "always" )

# living alone
table( d_2014$F14U52aG58a, useNA = "always" )
d_2014$living_alone <- factor( ifelse( d_2014$F14U52aG58a == 1, "no", "yes" ), 
                               levels = c( "yes", "no" ) )
table( d_2014$living_alone, useNA = "always" )

# personal support
table( d_2014$F14U56G66, useNA = "always" )
d_2014$personal_support <- factor( ifelse( d_2014$F14U56G66 <= 2, "yes", "no" ), 
                                   levels = c( "yes", "no" ) )
table( d_2014$personal_support, useNA = "always" )


##### demographic characteristics #####

# among respondents (n = 22,250)
# make characteristics table by sexual identity
explanatory =  c( "sex", "age_cat", "country_of_birth", "education", "occupation", "income", "marital_status", "living_alone", "personal_support" )
dependent = "sexual_identity_2014"

d_2014_table_1 <- d_2014 %>% 
  summary_factorlist( dependent,
                      explanatory, 
                      na_include = TRUE,
                      na_include_dependent = TRUE, 
                      total_col = TRUE,
                      add_col_totals = TRUE,
                      column = FALSE )

# Fisher's test
x1 <- table( d_2014$sex, d_2014$sexual_identity_2014 )
x1
format( round( fisher.test( x1[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x2 <- table( d_2014$age_cat, d_2014$sexual_identity_2014 )
x2
format( round( fisher.test( x2[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x3 <- table( d_2014$country_of_birth, d_2014$sexual_identity_2014 )
x3
format( round( fisher.test( x3[, c( 1, 2 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x4 <- table( d_2014$education, d_2014$sexual_identity_2014 )
x4
format( round( fisher.test( x4[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x5 <- table( d_2014$income, d_2014$sexual_identity_2014 )
x5
format( round( fisher.test( x5[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x6 <- table( d_2014$marital_status, d_2014$sexual_identity_2014 )
x6
format( round( fisher.test( x6[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x7 <- table( d_2014$living_alone, d_2014$sexual_identity_2014 )
x7
format( round( fisher.test( x7[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x7[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x8 <- table( d_2014$personal_support, d_2014$sexual_identity_2014 )
x8
format( round( fisher.test( x8[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x8[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x8[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x9 <- table( d_2014$occupation, d_2014$sexual_identity_2014 )
x9
format( round( fisher.test( x9[, c( 1, 2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x9[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x9[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

# make characteristics table by changes of sexual identity
explanatory =  c( "sex", "age_cat", "country_of_birth", "education", "occupation", "income", "marital_status", "living_alone", "personal_support", "sexual_identity_2014" )
dependent = "sexual_identity_fluidity"

d_2014_table_2 <- d_2014 %>% 
  mutate( sexual_identity_fluidity = factor( sexual_identity_fluidity, levels = c( 0, 1 ), labels = c( "no change", "change" ) ) ) %>%
  summary_factorlist( dependent,
                      explanatory, 
                      na_include = TRUE,
                      na_include_dependent = TRUE, 
                      total_col = TRUE,
                      add_col_totals = TRUE,
                      column = FALSE )

# Fisher's test
x1 <- table( d_2014$sex, d_2014$sexual_identity_fluidity )
x1
format( round( fisher.test( x1 )$p.value, 3 ), nsmall = 3 )

x2 <- table( d_2014$age_cat, d_2014$sexual_identity_fluidity )
x2
format( round( fisher.test( x2, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x3 <- table( d_2014$country_of_birth, d_2014$sexual_identity_fluidity )
x3
format( round( fisher.test( x3, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x4 <- table( d_2014$education, d_2014$sexual_identity_fluidity )
x4
format( round( fisher.test( x4, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x5 <- table( d_2014$occupation, d_2014$sexual_identity_fluidity )
x5
format( round( fisher.test( x5, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x6 <- table( d_2014$income, d_2014$sexual_identity_fluidity )
x6
format( round( fisher.test( x6, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x7 <- table( d_2014$marital_status, d_2014$sexual_identity_fluidity )
x7
format( round( fisher.test( x7, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x8 <- table( d_2014$living_alone, d_2014$sexual_identity_fluidity )
x8
format( round( fisher.test( x8, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x9 <- table( d_2014$personal_support, d_2014$sexual_identity_fluidity )
x9
format( round( fisher.test( x9, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x10 <- table( d_2014$sexual_identity_2014, d_2014$sexual_identity_fluidity )
x10
format( round( fisher.test( x10, simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )


##### design weights #####

summary( d_2014$F14dvikt )
d_2014$design_weight <- d_2014$F14dvikt


##### non-response #####

# unit non-response
d_2014$design_weight_unit_nonresponse <- d_2014$F14dbvikt # weights calculated assuming Missing Completely At Random (MCAR) within each stratum
summary( d_2014$design_weight_unit_nonresponse )
sum( d_2014$design_weight_unit_nonresponse ) # No. of source population = 1,764,671

unitresponse_prob <- d_2014 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( unitresponse_prob = unique( design_weight ) / unique( design_weight_unit_nonresponse ),
             no.of.population = sum( design_weight_unit_nonresponse ),
             sample_size = unique( no.of.population )/unique( design_weight ) ) # calculate overall unit response rate, and no. of population and sample size within each stratum

d_2014 <- d_2014 %>% 
  left_join( unitresponse_prob, by = "sampling_strata_region" )

# item non-response
itemresponse_prob <- d_2014 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( itemresponse_prob = sum( !is.na( sexual_identity_2014 ) ) / n() ) # calculate item response rate

d_2014 <- d_2014 %>% 
  left_join( itemresponse_prob, by = "sampling_strata_region" ) %>% 
  mutate( itemresponse_prob = ifelse( is.na( sexual_identity_2014 ), 0, itemresponse_prob ) )


##### summary of stratified sampling #####

sampling_frame_2014 <- as.data.frame( d_2014 %>% 
                                   group_by( sampling_strata_region ) %>% 
                                   reframe( no.of.population = unique( no.of.population ), 
                                            sample_size = unique( no.of.population/design_weight ),
                                            unitresponse = n(),
                                            itemresponse = sum( itemresponse_prob != 0 ) ) )

sampling_frame_2014$unitresponse_rate <- sampling_frame_2014$unitresponse/sampling_frame_2014$sample_size
sampling_frame_2014$itemresponse_rate <- sampling_frame_2014$itemresponse/sampling_frame_2014$unitresponse
sampling_frame_2014$overallresponse_rate <- sampling_frame_2014$itemresponse/sampling_frame_2014$sample_size

sampling_frame_2014$unitresponse_label <- paste0( sampling_frame_2014$unitresponse, " (", 
                                             sprintf( "%.1f", sampling_frame_2014$unitresponse_rate*100 ), "%)" )
sampling_frame_2014$overallresponse_label <- paste0( sampling_frame_2014$itemresponse, " (", 
                                                sprintf( "%.1f", sampling_frame_2014$overallresponse_rate*100 ), "%)" )

round( sum( sampling_frame_2014$unitresponse )/( sum( sampling_frame_2014$sample_size ) ), 3 ) # overall unit response rate
round( sum( sampling_frame_2014$itemresponse )/( sum( sampling_frame_2014$unitresponse ) ), 3 ) # overall item response rate
round( sum( sampling_frame_2014$itemresponse )/( sum( sampling_frame_2014$sample_size ) ), 3 ) # overall response rate

writexl::write_xlsx( sampling_frame_2014, "sampling_frame_2014.xlsx" )


##### calibrated weights #####

d_2014$calibrated_weight <- d_2014$F14kalvikt

# visualize calibrated weights across sampling strata
ggplot( d_2014 %>% 
          group_by( sampling_strata_region ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( sampling_strata_region, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 260 ), breaks = c( 0, 50, 100, 150, 200, 250 ), expand = c( 0, 0 ) ) +
  labs( y = NULL, x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ) )


##### replicating non-respondent rows for sampling design #####

# because d_2014 includes data only for respondents (unit response), we need to duplicate rows for non-respondents
# so that the final dataset represents the sampling process
rows_to_add <- d_2014 %>%
  group_by( sampling_strata_region ) %>%
  summarise( to_add = unique( sample_size ) - n(),
             no.of.population = unique( no.of.population ),
             sample_size = unique( sample_size ),
             design_weight = unique( design_weight ) )

sum( rows_to_add$to_add ) # 30,787 non-respondents

rows_to_add$to_add <- round( rows_to_add$to_add ) # to resolve floating-point precision issues

replicated_rows <- rows_to_add[ rep( row.names( rows_to_add ), rows_to_add$to_add ), c( 1, 3:5 ) ]

d_2014_complete <- bind_rows( d_2014, replicated_rows ) # 53,037 individuals in the original sample
```

### 3. Estimation of Proportions of Sexual Identities
#### 3.1. Complete-case analysis
##### 3.1.1. Define survey design
```{r}
# prepare dataset
d_2014_complete_cc <- d_2014_complete

d_2014_complete_cc$country_of_birth <- factor( 
  ifelse( d_2014_complete_cc$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2014_complete_cc$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

d_2014_complete_cc$living_alone <- as.factor(
  ifelse( d_2014_complete_cc$living_alone == "yes", 
          "living_alone_yes",
          "living_alone_no" )
  )

d_2014_complete_cc$personal_support <- as.factor(
  ifelse( d_2014_complete_cc$personal_support == "yes", 
          "personal_support_yes",
          "personal_support_no" ) 
  )

# create survey design
survey_design_cc <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ design_weight,
                               fpc = ~ no.of.population,
                               data = d_2014_complete_cc )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

# the following analyses assume MCAR
``` 

##### 3.1.2. By sex
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                        by = ~ sex,
                        design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( sex ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_sex
}

prop_cc_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_sex <- left_join( prop_cc_sex,
                          d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$sex ), ] %>% 
                            group_by( subgroup = sex ) %>% 
                            summarise( sample_size_2014 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.3. By age group
###### 3.1.3.1. Calculate proportion by pre-specified age cut-off
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                        by = ~ age_cat,
                        design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( age_cat ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_age ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_age
}

prop_cc_age <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age <- left_join( prop_cc_age,
                          d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$age_cat ), ] %>% 
                            group_by( subgroup = age_cat ) %>% 
                            summarise( sample_size_2014 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

###### 3.1.3.2. Calculate proportion and proportion ratio by varying age cut-offs
```{r}
d_2014_iteration_age <- d_2014_complete

min_age <- min( d_2014_iteration_age$age, na.rm = TRUE )

results_df <- data.frame()

for ( cut_off in ( min_age ):100 ) {
  d_2014_iteration_age$age_iteration <- ifelse( d_2014_iteration_age$age <= cut_off, "young", "old" )
  
  survey_design_iteration_age <- svydesign( ids = ~ 1, 
                                            strata = ~ sampling_strata_region,
                                            weights = ~ design_weight,
                                            fpc = ~ no.of.population,
                                            data = d_2014_iteration_age )
  
  list_of_df <- list()
  
  for ( cat in categories ) {
    prop_cc_age_iteration <- svyby(
      formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
      by = ~ age_iteration,
      design = subset( survey_design_iteration_age, !is.na( sexual_identity_2014 ) & !is.na( age ) ),
      FUN = svyciprop,
      method = "beta" )
    
    colnames( prop_cc_age_iteration ) <- c( "subgroup", 
                                            paste0( cat, "_point_estimate_2014" ), 
                                            paste0( cat, "_se_2014" ) )
    
    list_of_df[[cat]] <- prop_cc_age_iteration
  }
  
  prop_cc_age_iteration_merged <- Reduce( function( df1, df2 ) { 
    merge( df1, df2, by = "subgroup" ) 
    }, 
    list_of_df
    )
  
  prop_cc_age_iteration_merged$cut_off <- cut_off
  
  results_df <- rbind( results_df, prop_cc_age_iteration_merged )
  }

results_wide <- results_df %>%
  select( -ends_with( "_se_2014" ) ) %>%
  pivot_wider( names_from = subgroup, 
               values_from = c( Heterosexual_point_estimate_2014, 
                                Homosexual_point_estimate_2014, 
                                Bisexual_point_estimate_2014, 
                                `None of the above_point_estimate_2014` ) 
               )

colnames( results_wide ) <- gsub( "_point_estimate_2014", "", colnames( results_wide ) )

results_wide$Heterosexual_pr_2014 <- results_wide$Heterosexual_young/results_wide$Heterosexual_old
results_wide$Homosexual_pr_2014 <- results_wide$Homosexual_young/results_wide$Homosexual_old
results_wide$Bisexual_pr_2014 <- results_wide$Bisexual_young/results_wide$Bisexual_old
results_wide$`None of the above_pr_2014` <- results_wide$`None of the above_young`/results_wide$`None of the above_old`

results_wide$Heterosexual_pr_2014[ is.infinite( results_wide$Heterosexual_pr_2014 ) ] <- NA
results_wide$Homosexual_pr_2014[ is.infinite( results_wide$Homosexual_pr_2014 ) ] <- NA
results_wide$Bisexual_pr_2014[ is.infinite( results_wide$Bisexual_pr_2014 ) ] <- NA
results_wide$`None of the above_pr_2014`[ is.infinite( results_wide$`None of the above_pr_2014` ) ] <- NA

writexl::write_xlsx( results_wide, "prop_cc_age_iteration_2014.xlsx" )
```

###### 3.1.3.3. Calculate proportion by generation
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_generation <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                        by = ~ generation,
                        design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( generation ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_generation ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_generation
}

prop_cc_generation <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_generation <- left_join( prop_cc_generation,
                          d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                                !is.na( d_2014_complete_cc$generation ), ] %>% 
                            group_by( subgroup = generation ) %>% 
                            summarise( sample_size_2014 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.4. By sex*age group
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                            by = ~ age_sex,
                            design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( age_sex ) ),
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_age_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_age_sex
}

prop_cc_age_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age_sex <- left_join( prop_cc_age_sex,
                              d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$age_sex ), ] %>% 
                                group_by( subgroup = age_sex ) %>% 
                                summarise( sample_size_2014 = n() ),
                              by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.5. By education
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_education <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                              by = ~ education,
                              design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( education ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_education ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_education
}

prop_cc_education <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_education <- left_join( prop_cc_education,
                                d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$education ), ] %>% 
                                  group_by( subgroup = education ) %>% 
                                  summarise( sample_size_2014 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.6. By occupation
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_occupation <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                              by = ~ occupation,
                              design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( occupation ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_occupation ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_occupation
}

prop_cc_occupation <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_occupation <- left_join( prop_cc_occupation,
                                d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                                      !is.na( d_2014_complete_cc$occupation ), ] %>% 
                                  group_by( subgroup = occupation ) %>% 
                                  summarise( sample_size_2014 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.7. By income
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_income <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                           by = ~ income,
                           design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( income ) ),
                           FUN = svyciprop,
                           vartype = "ci",
                           method = "beta" )
  
  colnames( prop_cc_income ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_income
}

prop_cc_income <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_income <- left_join( prop_cc_income,
                             d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$income ), ] %>% 
                               group_by( subgroup = income ) %>% 
                               summarise( sample_size_2014 = n() ),
                             by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.8. By country of birth
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_country_of_birth <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                                     by = ~ country_of_birth,
                                     design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( country_of_birth ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_country_of_birth ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_country_of_birth
}

prop_cc_country_of_birth <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_country_of_birth <- left_join( prop_cc_country_of_birth,
                                       d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$country_of_birth ), ] %>% 
                                         group_by( subgroup = country_of_birth ) %>% 
                                         summarise( sample_size_2014 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.9. By marital status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_marital_status <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                                   by = ~ marital_status,
                                   design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( marital_status ) ),
                                   FUN = svyciprop,
                                   vartype = "ci",
                                   method = "beta" )
  
  colnames( prop_cc_marital_status ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_marital_status
}

prop_cc_marital_status <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_marital_status <- left_join( prop_cc_marital_status,
                                     d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$marital_status ), ] %>% 
                                       group_by( subgroup = marital_status ) %>% 
                                       summarise( sample_size_2014 = n() ),
                                     by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.10. By living status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_living_alone <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                                 by = ~ living_alone,
                                 design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( living_alone ) ),
                                 FUN = svyciprop,
                                 vartype = "ci",
                                 method = "beta" )
  
  colnames( prop_cc_living_alone ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_living_alone
}

prop_cc_living_alone <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_living_alone <- left_join( prop_cc_living_alone,
                                   d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$living_alone ), ] %>% 
                                     group_by( subgroup = living_alone ) %>% 
                                     summarise( sample_size_2014 = n() ),
                                   by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.11. By personal support
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_personal_support <- svyby( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                                     by = ~ personal_support,
                                     design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) & !is.na( personal_support ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_personal_support ) <- c( "subgroup", paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_personal_support
}

prop_cc_personal_support <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_personal_support <- left_join( prop_cc_personal_support,
                                       d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ) &
                                             !is.na( d_2014_complete_cc$personal_support ), ] %>% 
                                         group_by( subgroup = personal_support ) %>% 
                                         summarise( sample_size_2014 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )

```

##### 3.1.12. Overall proportions of sexual identities in Stockholm County
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity_2014 == '", cat, "' )" ) ),
                                design = subset( survey_design_cc, !is.na( sexual_identity_2014 ) ),
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2014" ), paste0( cat, "_lower_ci_2014" ), paste0( cat, "_upper_ci_2014" ) )
  
  list_of_df[[cat]] <- prop_cc_overall
}

prop_cc_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
}, 
list_of_df ) %>% 
  as.data.frame() %>%
  rownames_to_column( var = "subgroup" )

prop_cc_overall[ 1, 1 ] <- "Stockholm County"

prop_cc_overall <- bind_cols( prop_cc_overall,
                              d_2014_complete_cc[ !is.na( d_2014_complete_cc$sexual_identity_2014 ), ] %>% 
                                summarise( sample_size_2014 = n() ) ) %>%
  mutate( sample_size_2014 = prettyNum( sample_size_2014, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.13. Merge datasets
```{r}
prop_cc_summary_2014 <- rbind( prop_cc_sex, 
                               prop_cc_age,
                               prop_cc_generation,
                               prop_cc_age_sex,
                               prop_cc_education,
                               prop_cc_occupation,
                               prop_cc_income, 
                               prop_cc_country_of_birth, 
                               prop_cc_marital_status,
                               prop_cc_living_alone,
                               prop_cc_personal_support,
                               prop_cc_overall 
)

writexl::write_xlsx( prop_cc_summary_2014, "prop_cc_summary_2014.xlsx" )
```

#### 3.2. Multiple imputation and survey weights
##### 3.2.1. Multiple imputation
###### 3.2.1.1. Obtain incomplete dataset
```{r}
summary( d_2014 )
selected_variables <- c( "sampling_strata_region", "no.of.population", "sample_size", "calibrated_weight", "sexual_identity_2014", "sexual_identity_2021", "age", "sex", "country_of_birth", "utbniva2014", "occupation", "dispink2014", "marital_status", "living_alone", "F14U56G66" )

d_2014_incomplete <- d_2014 %>% 
  select( all_of( selected_variables ) ) %>%
  mutate( utbniva2014 = as.factor( utbniva2014 ),
          F14U56G66 = as.factor( F14U56G66 ) ) %>%
  rename( education = utbniva2014,
          income = dispink2014,
          personal_support = F14U56G66
  )

# visualize the distribution of income (semi-continuous)
ggplot( d_2014_incomplete, aes( x = income ) ) +
  geom_histogram( binwidth = 10, fill = "steelblue", color = "steelblue" ) +
  xlim( c( 0, 20000 ) )

ggplot( d_2014_incomplete, aes( x = log( income ) ) ) +
  geom_histogram( binwidth = 0.01, fill = "steelblue", color = "steelblue" ) +
  xlim( c( log( 1 ), log( 20000 ) ) )

# generate two variables for income
d_2014_incomplete$income_cat <- as.factor( ifelse( d_2014_incomplete$income == 0, 0, 1 ) )
d_2014_incomplete$income_log_con <- ifelse( d_2014_incomplete$income == 0, NA, log( d_2014_incomplete$income ) )
d_2014_incomplete <- d_2014_incomplete %>% select( -c( income ) )

summary( d_2014_incomplete )
sapply( d_2014_incomplete, class ) # all continuous variables are numeric, and all categorical variables are factor
```

###### 3.2.1.2. Visualize missing pattern
```{r}
# identify missing variables
vis_miss( d_2014_incomplete )
n_miss( d_2014_incomplete )
miss_var_summary( d_2014_incomplete ) # 37.6% missing in sexual_identity_2021, 9.0% in sexual_identity_2014,
# 8.2% in personal_support, 7.5% in living_alone, 0.7% in education, 0.2% in income
```

###### 3.2.1.3. Two-level multivariate normal imputation
```{r}
# use multiple imputation to account for item non-response
# assume Missing At Random (MAR)

# create weight strata
d_2014_incomplete$weight_strata <- as.factor( cut( d_2014_incomplete$calibrated_weight,
                                                   breaks = quantile( d_2014_incomplete$calibrated_weight, 
                                                                      probs = seq( 0, 1, length.out = 26 ) ),
                                                   labels = 1:25,
                                                   include.lowest = TRUE,
                                                   right = TRUE ) )

ggplot( d_2014_incomplete %>% 
          group_by( weight_strata ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( weight_strata, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 320 ), 
                      breaks = c( 0, 50, 100, 150, 200, 250, 300 ), 
                      expand = c( 0, 0 ) ) +
  labs( y = "Calibrated Weight Strata", x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.y = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 )
  )
```

### 4. Relation between Sexual Identity and Demographic Factors
#### 4.1. Complete-case analysis
##### 4.1.1. Define survey design
```{r}
##### prepare dataset #####

d_2014_cc_model <- d_2014_complete

# exposures of interest, including age, sex, country of birth, education, income, marital status, living status, and personal support
d_2014_cc_model$age_exp <- relevel( d_2014_cc_model$age_cat, ref = "45-59" )

d_2014_cc_model$sex_exp <- relevel( d_2014_cc_model$sex, ref = "Male" )

d_2014_cc_model$country_of_birth_exp <- factor( 
  ifelse( d_2014_cc_model$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2014_cc_model$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

d_2014_cc_model$education_exp <- relevel( d_2014_cc_model$education, ref = ">=13 years" )

d_2014_cc_model$income_exp <- relevel( d_2014_cc_model$income, ref = ">4,500" )

d_2014_cc_model$marital_status_exp <- relevel( d_2014_cc_model$marital_status, ref = "Currently married" )

d_2014_cc_model$living_status_exp <- relevel( d_2014_cc_model$living_alone, ref = "no" )

d_2014_cc_model$personal_support_exp <- relevel( d_2014_cc_model$personal_support, ref = "yes" )


# outcomes of interest, including sexual minority, homosexual, bisexual, and other
d_2014_cc_model$sexual_minority <- ifelse( d_2014_cc_model$sexual_identity_2014 == "Heterosexual", 0, 1 )

d_2014_cc_model$homosexual <- ifelse( d_2014_cc_model$sexual_identity_2014 == "Homosexual", 1, 0 )

d_2014_cc_model$bisexual <- ifelse( d_2014_cc_model$sexual_identity_2014 == "Bisexual", 1, 0 )

d_2014_cc_model$other <- ifelse( d_2014_cc_model$sexual_identity_2014 == "None of the above", 1, 0 )


# confounding variables, including age, sex, country of birth, education, income, marital status, 
# and place of residence (i.e., sampling strata)
d_2014_cc_model$age_conf <- d_2014_cc_model$age # age

d_2014_cc_model$sex_conf <- d_2014_cc_model$sex # sex

d_2014_cc_model$country_of_birth_conf <- d_2014_cc_model$country_of_birth # country of birth (grouped into five categories due to sparse data)

d_2014_cc_model$education_conf <- as.factor( d_2014_cc_model$utbniva2014 ) # education

d_2014_cc_model$income_conf <- d_2014_cc_model$dispink2014 # disposable income

d_2014_cc_model$marital_status_conf <- d_2014_cc_model$marital_status # marital status (grouped into three categories due to sparse data)

d_2014_cc_model$place_of_residence_conf <- d_2014_cc_model$sampling_strata_region # place of residence


##### create survey design #####
survey_design_cc_model <- svydesign( ids = ~ 1,
                                     strata = ~ sampling_strata_region,
                                     weights = ~ design_weight,
                                     fpc = ~ no.of.population,
                                     data = d_2014_cc_model )

# the following analyses assume MCAR
```

##### 4.1.2. Define model formula
```{r}
########## formula for crude analyses ##########

##### exposure of interest: age #####

fml_sexual_minority_age_crude <- sexual_minority ~ age_exp
fml_homosexual_age_crude <- homosexual ~ age_exp
fml_bisexual_age_crude <- bisexual ~ age_exp
fml_other_age_crude <- other ~ age_exp

# list of formulas
fml_list_age_crude <- list(
  fml_sexual_minority_age_crude = fml_sexual_minority_age_crude,
  fml_homosexual_age_crude = fml_homosexual_age_crude,
  fml_bisexual_age_crude = fml_bisexual_age_crude,
  fml_other_age_crude = fml_other_age_crude
  )


##### exposure of interest: age by sex #####

fml_sexual_minority_age_by_sex_crude <- sexual_minority ~ age_exp*sex_exp
fml_homosexual_age_by_sex_crude <- homosexual ~ age_exp*sex_exp
fml_bisexual_age_by_sex_crude <- bisexual ~ age_exp*sex_exp
fml_other_age_by_sex_crude <- other ~ age_exp*sex_exp

# list of formulas
fml_list_age_by_sex_crude <- list(
  fml_sexual_minority_age_by_sex_crude = fml_sexual_minority_age_by_sex_crude,
  fml_homosexual_age_by_sex_crude = fml_homosexual_age_by_sex_crude,
  fml_bisexual_age_by_sex_crude = fml_bisexual_age_by_sex_crude,
  fml_other_age_by_sex_crude = fml_other_age_by_sex_crude
  )


##### exposure of interest: sex #####

fml_sexual_minority_sex_crude <- sexual_minority ~ sex_exp
fml_homosexual_sex_crude <- homosexual ~ sex_exp
fml_bisexual_sex_crude <- bisexual ~ sex_exp
fml_other_sex_crude <- other ~ sex_exp

# list of formulas
fml_list_sex_crude <- list(
  fml_sexual_minority_sex_crude = fml_sexual_minority_sex_crude,
  fml_homosexual_sex_crude = fml_homosexual_sex_crude,
  fml_bisexual_sex_crude = fml_bisexual_sex_crude,
  fml_other_sex_crude = fml_other_sex_crude
  )


##### exposure of interest: country of birth #####

fml_sexual_minority_country_of_birth_crude <- sexual_minority ~ country_of_birth_exp
fml_homosexual_country_of_birth_crude <- homosexual ~ country_of_birth_exp
fml_bisexual_country_of_birth_crude <- bisexual ~ country_of_birth_exp
fml_other_country_of_birth_crude <- other ~ country_of_birth_exp

# list of formulas
fml_list_country_of_birth_crude <- list(
  fml_sexual_minority_country_of_birth_crude = fml_sexual_minority_country_of_birth_crude,
  fml_homosexual_country_of_birth_crude = fml_homosexual_country_of_birth_crude,
  fml_bisexual_country_of_birth_crude = fml_bisexual_country_of_birth_crude,
  fml_other_country_of_birth_crude = fml_other_country_of_birth_crude
)


##### exposure of interest: education #####

fml_sexual_minority_education_crude <- sexual_minority ~ education_exp
fml_homosexual_education_crude <- homosexual ~ education_exp
fml_bisexual_education_crude <- bisexual ~ education_exp
fml_other_education_crude <- other ~ education_exp

# list of formulas
fml_list_education_crude <- list(
  fml_sexual_minority_education_crude = fml_sexual_minority_education_crude,
  fml_homosexual_education_crude = fml_homosexual_education_crude,
  fml_bisexual_education_crude = fml_bisexual_education_crude,
  fml_other_education_crude = fml_other_education_crude
  )


##### exposure of interest: income #####

fml_sexual_minority_income_crude <- sexual_minority ~ income_exp
fml_homosexual_income_crude <- homosexual ~ income_exp
fml_bisexual_income_crude <- bisexual ~ income_exp
fml_other_income_crude <- other ~ income_exp

# list of formulas
fml_list_income_crude <- list(
  fml_sexual_minority_income_crude = fml_sexual_minority_income_crude,
  fml_homosexual_income_crude = fml_homosexual_income_crude,
  fml_bisexual_income_crude = fml_bisexual_income_crude,
  fml_other_income_crude = fml_other_income_crude
  )


##### exposure of interest: marital status #####

fml_sexual_minority_marital_status_crude <- sexual_minority ~ marital_status_exp
fml_homosexual_marital_status_crude <- homosexual ~ marital_status_exp
fml_bisexual_marital_status_crude <- bisexual ~ marital_status_exp
fml_other_marital_status_crude <- other ~ marital_status_exp

# list of formulas
fml_list_marital_status_crude <- list(
  fml_sexual_minority_marital_status_crude = fml_sexual_minority_marital_status_crude,
  fml_homosexual_marital_status_crude = fml_homosexual_marital_status_crude,
  fml_bisexual_marital_status_crude = fml_bisexual_marital_status_crude,
  fml_other_marital_status_crude = fml_other_marital_status_crude
  )


##### exposure of interest: living status #####

fml_sexual_minority_living_status_crude <- sexual_minority ~ living_status_exp
fml_homosexual_living_status_crude <- homosexual ~ living_status_exp
fml_bisexual_living_status_crude <- bisexual ~ living_status_exp
fml_other_living_status_crude <- other ~ living_status_exp

# list of formulas
fml_list_living_status_crude <- list(
  fml_sexual_minority_living_status_crude = fml_sexual_minority_living_status_crude,
  fml_homosexual_living_status_crude = fml_homosexual_living_status_crude,
  fml_bisexual_living_status_crude = fml_bisexual_living_status_crude,
  fml_other_living_status_crude = fml_other_living_status_crude
)


##### exposure of interest: personal support #####

fml_sexual_minority_personal_support_crude <- sexual_minority ~ personal_support_exp
fml_homosexual_personal_support_crude <- homosexual ~ personal_support_exp
fml_bisexual_personal_support_crude <- bisexual ~ personal_support_exp
fml_other_personal_support_crude <- other ~ personal_support_exp

# list of formulas
fml_list_personal_support_crude <- list(
  fml_sexual_minority_personal_support_crude = fml_sexual_minority_personal_support_crude,
  fml_homosexual_personal_support_crude = fml_homosexual_personal_support_crude,
  fml_bisexual_personal_support_crude = fml_bisexual_personal_support_crude,
  fml_other_personal_support_crude = fml_other_personal_support_crude
)


########## formula for adjusted analyses ########## 

##### exposure of interest: age #####

# sexual minority
fml_sexual_minority_age_model_1 <- sexual_minority ~ age_exp + sex_conf + country_of_birth_conf
fml_sexual_minority_age_model_2 <- sexual_minority ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_age_model_1 <- homosexual ~ age_exp + sex_conf + country_of_birth_conf
fml_homosexual_age_model_2 <- homosexual ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_age_model_1 <- bisexual ~ age_exp + sex_conf + country_of_birth_conf
fml_bisexual_age_model_2 <- bisexual ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_age_model_1 <- other ~ age_exp + sex_conf + country_of_birth_conf
fml_other_age_model_2 <- other ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_age <- list(
  fml_sexual_minority_age_model_1 = fml_sexual_minority_age_model_1,
  fml_sexual_minority_age_model_2 = fml_sexual_minority_age_model_2,
  fml_homosexual_age_model_1 = fml_homosexual_age_model_1,
  fml_homosexual_age_model_2 = fml_homosexual_age_model_2,
  fml_bisexual_age_model_1 = fml_bisexual_age_model_1,
  fml_bisexual_age_model_2 = fml_bisexual_age_model_2,
  fml_other_age_model_1 = fml_other_age_model_1,
  fml_other_age_model_2 = fml_other_age_model_2
  )


##### exposure of interest: age by sex #####

# sexual minority
fml_sexual_minority_age_by_sex_model_1 <- sexual_minority ~ age_exp*sex_exp + country_of_birth_conf
fml_sexual_minority_age_by_sex_model_2 <- sexual_minority ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_age_by_sex_model_1 <- homosexual ~ age_exp*sex_exp + country_of_birth_conf
fml_homosexual_age_by_sex_model_2 <- homosexual ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_age_by_sex_model_1 <- bisexual ~ age_exp*sex_exp + country_of_birth_conf
fml_bisexual_age_by_sex_model_2 <- bisexual ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_age_by_sex_model_1 <- other ~ age_exp*sex_exp + country_of_birth_conf
fml_other_age_by_sex_model_2 <- other ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_age_by_sex <- list(
  fml_sexual_minority_age_by_sex_model_1 = fml_sexual_minority_age_by_sex_model_1,
  fml_sexual_minority_age_by_sex_model_2 = fml_sexual_minority_age_by_sex_model_2,
  fml_homosexual_age_by_sex_model_1 = fml_homosexual_age_by_sex_model_1,
  fml_homosexual_age_by_sex_model_2 = fml_homosexual_age_by_sex_model_2,
  fml_bisexual_age_by_sex_model_1 = fml_bisexual_age_by_sex_model_1,
  fml_bisexual_age_by_sex_model_2 = fml_bisexual_age_by_sex_model_2,
  fml_other_age_by_sex_model_1 = fml_other_age_by_sex_model_1,
  fml_other_age_by_sex_model_2 = fml_other_age_by_sex_model_2
  )


##### exposure of interest: sex #####

# sexual minority
fml_sexual_minority_sex_model_1 <- sexual_minority ~ sex_exp + age_conf + country_of_birth_conf
fml_sexual_minority_sex_model_2 <- sexual_minority ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_sex_model_1 <- homosexual ~ sex_exp + age_conf + country_of_birth_conf
fml_homosexual_sex_model_2 <- homosexual ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_sex_model_1 <- bisexual ~ sex_exp + age_conf + country_of_birth_conf
fml_bisexual_sex_model_2 <- bisexual ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_sex_model_1 <- other ~ sex_exp + age_conf + country_of_birth_conf
fml_other_sex_model_2 <- other ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_sex <- list(
  fml_sexual_minority_sex_model_1 = fml_sexual_minority_sex_model_1,
  fml_sexual_minority_sex_model_2 = fml_sexual_minority_sex_model_2,
  fml_homosexual_sex_model_1 = fml_homosexual_sex_model_1,
  fml_homosexual_sex_model_2 = fml_homosexual_sex_model_2,
  fml_bisexual_sex_model_1 = fml_bisexual_sex_model_1,
  fml_bisexual_sex_model_2 = fml_bisexual_sex_model_2,
  fml_other_sex_model_1 = fml_other_sex_model_1,
  fml_other_sex_model_2 = fml_other_sex_model_2
  )


##### exposure of interest: country of birth #####

# sexual minority
fml_sexual_minority_country_of_birth_model_1 <- sexual_minority ~ country_of_birth_exp + age_conf + sex_conf
fml_sexual_minority_country_of_birth_model_2 <- sexual_minority ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_country_of_birth_model_1 <- homosexual ~ country_of_birth_exp + age_conf + sex_conf
fml_homosexual_country_of_birth_model_2 <- homosexual ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_country_of_birth_model_1 <- bisexual ~ country_of_birth_exp + age_conf + sex_conf
fml_bisexual_country_of_birth_model_2 <- bisexual ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_country_of_birth_model_1 <- other ~ country_of_birth_exp + age_conf + sex_conf
fml_other_country_of_birth_model_2 <- other ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_country_of_birth <- list(
  fml_sexual_minority_country_of_birth_model_1 = fml_sexual_minority_country_of_birth_model_1,
  fml_sexual_minority_country_of_birth_model_2 = fml_sexual_minority_country_of_birth_model_2,
  fml_homosexual_country_of_birth_model_1 = fml_homosexual_country_of_birth_model_1,
  fml_homosexual_country_of_birth_model_2 = fml_homosexual_country_of_birth_model_2,
  fml_bisexual_country_of_birth_model_1 = fml_bisexual_country_of_birth_model_1,
  fml_bisexual_country_of_birth_model_2 = fml_bisexual_country_of_birth_model_2,
  fml_other_country_of_birth_model_1 = fml_other_country_of_birth_model_1,
  fml_other_country_of_birth_model_2 = fml_other_country_of_birth_model_2
)


##### exposure of interest: education #####

# sexual minority
fml_sexual_minority_education_model_1 <- sexual_minority ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_education_model_2 <- sexual_minority ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_education_model_1 <- homosexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_education_model_2 <- homosexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_education_model_1 <- bisexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_education_model_2 <- bisexual ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_education_model_1 <- other ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_education_model_2 <- other ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_education <- list(
  fml_sexual_minority_education_model_1 = fml_sexual_minority_education_model_1,
  fml_sexual_minority_education_model_2 = fml_sexual_minority_education_model_2,
  fml_homosexual_education_model_1 = fml_homosexual_education_model_1,
  fml_homosexual_education_model_2 = fml_homosexual_education_model_2,
  fml_bisexual_education_model_1 = fml_bisexual_education_model_1,
  fml_bisexual_education_model_2 = fml_bisexual_education_model_2,
  fml_other_education_model_1 = fml_other_education_model_1,
  fml_other_education_model_2 = fml_other_education_model_2
  )


##### exposure of interest: income #####

# sexual minority
fml_sexual_minority_income_model_1 <- sexual_minority ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_income_model_2 <- sexual_minority ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_income_model_1 <- homosexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_income_model_2 <- homosexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_income_model_1 <- bisexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_income_model_2 <- bisexual ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_income_model_1 <- other ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_income_model_2 <- other ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_income <- list(
  fml_sexual_minority_income_model_1 = fml_sexual_minority_income_model_1,
  fml_sexual_minority_income_model_2 = fml_sexual_minority_income_model_2,
  fml_homosexual_income_model_1 = fml_homosexual_income_model_1,
  fml_homosexual_income_model_2 = fml_homosexual_income_model_2,
  fml_bisexual_income_model_1 = fml_bisexual_income_model_1,
  fml_bisexual_income_model_2 = fml_bisexual_income_model_2,
  fml_other_income_model_1 = fml_other_income_model_1,
  fml_other_income_model_2 = fml_other_income_model_2
  )


##### exposure of interest: marital status #####

# sexual minority
fml_sexual_minority_marital_status_model_1 <- sexual_minority ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_marital_status_model_2 <- sexual_minority ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# homosexual
fml_homosexual_marital_status_model_1 <- homosexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_marital_status_model_2 <- homosexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# bisexual
fml_bisexual_marital_status_model_1 <- bisexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_marital_status_model_2 <- bisexual ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# other
fml_other_marital_status_model_1 <- other ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_marital_status_model_2 <- other ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + place_of_residence_conf

# list of formulas
fml_list_marital_status <- list(
  fml_sexual_minority_marital_status_model_1 = fml_sexual_minority_marital_status_model_1,
  fml_sexual_minority_marital_status_model_2 = fml_sexual_minority_marital_status_model_2,
  fml_homosexual_marital_status_model_1 = fml_homosexual_marital_status_model_1,
  fml_homosexual_marital_status_model_2 = fml_homosexual_marital_status_model_2,
  fml_bisexual_marital_status_model_1 = fml_bisexual_marital_status_model_1,
  fml_bisexual_marital_status_model_2 = fml_bisexual_marital_status_model_2,
  fml_other_marital_status_model_1 = fml_other_marital_status_model_1,
  fml_other_marital_status_model_2 = fml_other_marital_status_model_2
  )


##### exposure of interest: living status #####

# sexual minority
fml_sexual_minority_living_status_model_1 <- sexual_minority ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_living_status_model_2 <- sexual_minority ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_living_status_model_1 <- homosexual ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_living_status_model_2 <- homosexual ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_living_status_model_1 <- bisexual ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_living_status_model_2 <- bisexual ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_living_status_model_1 <- other ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_living_status_model_2 <- other ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_living_status <- list(
  fml_sexual_minority_living_status_model_1 = fml_sexual_minority_living_status_model_1,
  fml_sexual_minority_living_status_model_2 = fml_sexual_minority_living_status_model_2,
  fml_homosexual_living_status_model_1 = fml_homosexual_living_status_model_1,
  fml_homosexual_living_status_model_2 = fml_homosexual_living_status_model_2,
  fml_bisexual_living_status_model_1 = fml_bisexual_living_status_model_1,
  fml_bisexual_living_status_model_2 = fml_bisexual_living_status_model_2,
  fml_other_living_status_model_1 = fml_other_living_status_model_1,
  fml_other_living_status_model_2 = fml_other_living_status_model_2
)


##### exposure of interest: personal support #####

# sexual minority
fml_sexual_minority_personal_support_model_1 <- sexual_minority ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_minority_personal_support_model_2 <- sexual_minority ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# homosexual
fml_homosexual_personal_support_model_1 <- homosexual ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf
fml_homosexual_personal_support_model_2 <- homosexual ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# bisexual
fml_bisexual_personal_support_model_1 <- bisexual ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf
fml_bisexual_personal_support_model_2 <- bisexual ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# other
fml_other_personal_support_model_1 <- other ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf
fml_other_personal_support_model_2 <- other ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + place_of_residence_conf

# list of formulas
fml_list_personal_support <- list(
  fml_sexual_minority_personal_support_model_1 = fml_sexual_minority_personal_support_model_1,
  fml_sexual_minority_personal_support_model_2 = fml_sexual_minority_personal_support_model_2,
  fml_homosexual_personal_support_model_1 = fml_homosexual_personal_support_model_1,
  fml_homosexual_personal_support_model_2 = fml_homosexual_personal_support_model_2,
  fml_bisexual_personal_support_model_1 = fml_bisexual_personal_support_model_1,
  fml_bisexual_personal_support_model_2 = fml_bisexual_personal_support_model_2,
  fml_other_personal_support_model_1 = fml_other_personal_support_model_1,
  fml_other_personal_support_model_2 = fml_other_personal_support_model_2
)

exposures <- c( "age", "age_by_sex", "sex", "country_of_birth", "education", "income", "marital_status", "living_status", "personal_support" )
```

##### 4.1.3. Unadjusted analyses
```{r}
# fit Poisson regression model for each exposure and each outcome
all_models_cc_crude <- list()

for ( exposure in exposures ) {
  all_models_cc_crude[[ exposure ]] <- list()
  
  fml_list_name <- paste( "fml_list", exposure, "crude", sep = "_" )
  
  for ( name in names( get( fml_list_name ) ) ) {
    all_models_cc_crude[[ exposure ]][[ name ]] <- fit_model_crude( get( fml_list_name )[[ name ]],
                                                                    survey_design_cc_model )
  }
}

# refit the model for age by sex, using female as the reference group
# to extract results for age among females
d_2014_cc_model$sex_exp <- relevel( d_2014_cc_model$sex, ref = "Female" )

survey_design_cc_model_refit <- svydesign( ids = ~ 1,
                                           strata = ~ sampling_strata_region,
                                           weights = ~ design_weight,
                                           fpc = ~ no.of.population,
                                           data = d_2014_cc_model )

refit_model_cc_age_by_sex_crude <- list()

for ( name in names( fml_list_age_by_sex_crude ) ) {
  refit_model_cc_age_by_sex_crude[[ name ]] <- fit_model_crude( fml_list_age_by_sex_crude[[ name ]],
                                                                survey_design_cc_model_refit )
}
```

##### 4.1.4. Adjusted analyses
```{r}
# fit Poisson, log-binomial, and logistic regression models for each exposure and each outcome
all_models_cc <- list()

for ( exposure in exposures ) {
  all_models_cc[[ exposure ]] <- list()
  
  fml_list_name <- paste( "fml_list", exposure, sep = "_" )
  
  for ( name in names( get( fml_list_name ) ) ) {
    all_models_cc[[ exposure ]][[ name ]] <- fit_models( get( fml_list_name )[[ name ]],
                                                         survey_design_cc_model )
  }
}

# refit the three models for age by sex, using female as the reference group
# to extract results for age among females
refit_model_cc_age_by_sex <- list()

for ( name in names( fml_list_age_by_sex ) ) {
  refit_model_cc_age_by_sex[[ name ]] <- fit_models( fml_list_age_by_sex[[ name ]],
                                                     survey_design_cc_model_refit )
}
```

##### 4.1.5. Extract results
```{r}
identities <- c( "sexual_minority", "homosexual", "bisexual", "other" )
models <- c( "poisson", "log_binomial", "logistic" )

########## Crude analyses ##########

##### exposure of interest: age #####

exposures_age <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60"  )

# extract coefficient and 95% CI
results_cc_age_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$age ) ) {
  results_cc_age_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "age", 
    outcome = outcome, 
    variables = exposures_age
  )
}

# extract proportion ratio and 95% CI
results_cc_age_pr_crude <- extract_results_pr_crude( results_cc_age_coef_crude, identities, "age" )


##### exposure of interest: age by sex #####

exposures_age_male <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expFemale", "age_exp30-44:sex_expFemale", "age_exp>=60:sex_expFemale" )
exposures_age_female <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expMale", "age_exp30-44:sex_expMale", "age_exp>=60:sex_expMale" )

# extract coefficient and 95% CI among males
results_cc_age_by_sex_coef_crude_male <- list()

for ( outcome in names( all_models_cc_crude$age_by_sex ) ) {
  results_cc_age_by_sex_coef_crude_male[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "age_by_sex", 
    outcome = outcome, 
    variables = exposures_age_male
  )
}

# extract coefficient and 95% CI among females
results_cc_age_by_sex_coef_crude_female <- list()

for ( outcome in names( refit_model_cc_age_by_sex_crude ) ) {
  model <- refit_model_cc_age_by_sex_crude[[ outcome ]]
  results_cc_age_by_sex_coef_crude_female[[ outcome ]] <- cbind( coef( model )[ exposures_age_female ], 
                                                                 confint( model, ddf = degf( model$survey.design ) )[ exposures_age_female, , drop = FALSE ] )
}

# extract proportion ratio and 95% CI
results_cc_age_by_sex_pr_crude_male <- extract_results_pr_crude( results_cc_age_by_sex_coef_crude_male, identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_by_sex_pr_crude_female <- extract_results_pr_crude( results_cc_age_by_sex_coef_crude_female, identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_crude <- rbind( results_cc_age_by_sex_pr_crude_male[ c( 1:3 ), ], 
                                         results_cc_age_by_sex_pr_crude_female[ c( 1:3 ), ] )


##### exposure of interest: sex #####

exposures_sex <- c( "sex_expFemale" )

# extract coefficient and 95% CI
results_cc_sex_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$sex ) ) {
  results_cc_sex_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "sex", 
    outcome = outcome, 
    variables = exposures_sex
  )
}

# extract proportion ratio and 95% CI
results_cc_sex_pr_crude <- extract_results_pr_crude( results_cc_sex_coef_crude, identities, "sex" )


##### exposure of interest: country of birth #####

exposures_country_of_birth <- c( "country_of_birth_expEurope", "country_of_birth_expOutside Europe" )

# extract coefficient and 95% CI
results_cc_country_of_birth_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$country_of_birth ) ) {
  results_cc_country_of_birth_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "country_of_birth", 
    outcome = outcome, 
    variables = exposures_country_of_birth
  )
}

# extract proportion ratio and 95% CI
results_cc_country_of_birth_pr_crude <- extract_results_pr_crude( results_cc_country_of_birth_coef_crude, identities, "country_of_birth" )


##### exposure of interest: education #####

exposures_education <- c( "education_exp<=9 years", "education_exp10-12 years" )

# extract coefficient and 95% CI
results_cc_education_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$education ) ) {
  results_cc_education_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "education", 
    outcome = outcome, 
    variables = exposures_education
  )
}

# extract proportion ratio and 95% CI
results_cc_education_pr_crude <- extract_results_pr_crude( results_cc_education_coef_crude, identities, "education" )


##### exposure of interest: income #####

exposures_income <- c( "income_exp<=2,500", "income_exp(2,500, 3,500]", "income_exp(3,500, 4,500]" )

# extract coefficient and 95% CI
results_cc_income_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$income ) ) {
  results_cc_income_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "income", 
    outcome = outcome, 
    variables = exposures_income
  )
}

# extract proportion ratio and 95% CI
results_cc_income_pr_crude <- extract_results_pr_crude( results_cc_income_coef_crude, identities, "income" )


##### exposure of interest: marital status #####

exposures_marital_status <- c( "marital_status_expNever married", "marital_status_expOther" )

# extract coefficient and 95% CI
results_cc_marital_status_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$marital_status ) ) {
  results_cc_marital_status_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "marital_status", 
    outcome = outcome, 
    variables = exposures_marital_status
  )
}

# extract proportion ratio and 95% CI
results_cc_marital_status_pr_crude <- extract_results_pr_crude( results_cc_marital_status_coef_crude, identities, "marital_status" )


##### exposure of interest: living status #####

exposures_living_status <- c( "living_status_expyes" )

# extract coefficient and 95% CI
results_cc_living_status_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$living_status ) ) {
  results_cc_living_status_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "living_status", 
    outcome = outcome, 
    variables = exposures_living_status
  )
}

# extract proportion ratio and 95% CI
results_cc_living_status_pr_crude <- extract_results_pr_crude( results_cc_living_status_coef_crude, identities, "living_status" )


##### exposure of interest: personal support #####

exposures_personal_support <- c( "personal_support_expno" )

# extract coefficient and 95% CI
results_cc_personal_support_coef_crude <- list()

for ( outcome in names( all_models_cc_crude$personal_support ) ) {
  results_cc_personal_support_coef_crude[[ outcome ]] <- extract_results_coef_crude(
    all_models_list = all_models_cc_crude, 
    exposure = "personal_support", 
    outcome = outcome, 
    variables = exposures_personal_support
  )
}

# extract proportion ratio and 95% CI
results_cc_personal_support_pr_crude <- extract_results_pr_crude( results_cc_personal_support_coef_crude, identities, "personal_support" )


########## Adjusted analyses ##########

##### exposure of interest: age #####

# extract coefficient and 95% CI
results_cc_age_coef <- list()

for ( outcome in names( all_models_cc$age ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_age_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "age", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_age
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_age_pr_poisson_model_1 <- extract_results_pr( results_cc_age_coef, "model_1_poisson", identities, "age" )
colnames( results_cc_age_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_age_pr_poisson_model_1 )[-1], "_model_1")

results_cc_age_pr_poisson_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_poisson", identities, "age" )
colnames( results_cc_age_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_age_pr_poisson_model_2 )[-1], "_model_2")

results_cc_age_pr_poisson <- merge( results_cc_age_pr_poisson_model_1, results_cc_age_pr_poisson_model_2, by = "Exposure" )

results_cc_age_pr_log_binomial_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_log_binomial", identities, "age" )
results_cc_age_pr_logistic_model_2 <- extract_results_pr( results_cc_age_coef, "model_2_logistic", identities, "age" )


##### exposure of interest: age by sex #####

# extract coefficient and 95% CI among males
results_cc_age_coef_male <- list()

for ( outcome in names( all_models_cc$age_by_sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_age_coef_male[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "age_by_sex", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_age_male
    )
  }
}

# extract coefficient and 95% CI among females
results_cc_age_coef_female <- list()

for ( outcome in names( refit_model_cc_age_by_sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    model <- refit_model_cc_age_by_sex[[ outcome ]][[ mod ]]
    
    if ( !is.null( model ) ) {
      results_cc_age_coef_female[[ key ]] <- cbind( coef( model )[ exposures_age_female ], 
                                                    confint( model, ddf = degf( model$survey.design ) )[ exposures_age_female, , drop = FALSE ] )
    }
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
# results from poisson regression
results_cc_age_pr_poisson_male_model_1 <- extract_results_pr( results_cc_age_coef_male, "model_1_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_poisson_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_poisson_female_model_1 <- extract_results_pr( results_cc_age_coef_female, "model_1_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_pr_poisson_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_poisson", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_poisson_model_1 <- rbind( results_cc_age_pr_poisson_male_model_1[ c( 1:3 ), ], results_cc_age_pr_poisson_female_model_1[ c( 1:3 ), ] )
colnames( results_cc_age_by_sex_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_age_by_sex_pr_poisson_model_1 )[-1], "_model_1")

results_cc_age_by_sex_pr_poisson_model_2 <- rbind( results_cc_age_pr_poisson_male_model_2[ c( 1:3 ), ], results_cc_age_pr_poisson_female_model_2[ c( 1:3 ), ] )
colnames( results_cc_age_by_sex_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_age_by_sex_pr_poisson_model_2 )[-1], "_model_2" )

results_cc_age_by_sex_pr_poisson <- merge( results_cc_age_by_sex_pr_poisson_model_1, results_cc_age_by_sex_pr_poisson_model_2, by = "Exposure" )


# results from log binomial regression
results_cc_age_pr_log_binomial_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_log_binomial", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_log_binomial_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_log_binomial", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_log_binomial_model_2 <- rbind( results_cc_age_pr_log_binomial_male_model_2[ c( 1:3 ), ], 
                                                        results_cc_age_pr_log_binomial_female_model_2[ c( 1:3 ), ] )


# results from logistic regression
results_cc_age_pr_logistic_male_model_2 <- extract_results_pr( results_cc_age_coef_male, "model_2_logistic", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )

results_cc_age_pr_logistic_female_model_2 <- extract_results_pr( results_cc_age_coef_female, "model_2_logistic", identities, "age_by_sex" ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

results_cc_age_by_sex_pr_logistic_model_2 <- rbind( results_cc_age_pr_logistic_male_model_2[ c( 1:3 ), ], 
                                                    results_cc_age_pr_logistic_female_model_2[ c( 1:3 ), ] )


##### exposure of interest: sex #####

# extract coefficient and 95% CI
results_cc_sex_coef <- list()

for ( outcome in names( all_models_cc$sex ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_sex_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "sex", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_sex
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_sex_pr_poisson_model_1 <- extract_results_pr( results_cc_sex_coef, "model_1_poisson", identities, "sex" )
colnames( results_cc_sex_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_sex_pr_poisson_model_1 )[-1], "_model_1")

results_cc_sex_pr_poisson_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_poisson", identities, "sex" )
colnames( results_cc_sex_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_sex_pr_poisson_model_2 )[-1], "_model_2")

results_cc_sex_pr_poisson <- merge( results_cc_sex_pr_poisson_model_1, results_cc_sex_pr_poisson_model_2, by = "Exposure" )

results_cc_sex_pr_log_binomial_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_log_binomial", identities, "sex" )
results_cc_sex_pr_logistic_model_2 <- extract_results_pr( results_cc_sex_coef, "model_2_logistic", identities, "sex" )


##### exposure of interest: country of birth #####

# extract coefficient and 95% CI
results_cc_country_of_birth_coef <- list()

for ( outcome in names( all_models_cc$country_of_birth ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_country_of_birth_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "country_of_birth", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_country_of_birth
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_country_of_birth_pr_poisson_model_1 <- extract_results_pr( results_cc_country_of_birth_coef, "model_1_poisson", identities, "country_of_birth" )
colnames( results_cc_country_of_birth_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_country_of_birth_pr_poisson_model_1 )[-1], "_model_1")

results_cc_country_of_birth_pr_poisson_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_poisson", identities, "country_of_birth" )
colnames( results_cc_country_of_birth_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_country_of_birth_pr_poisson_model_2 )[-1], "_model_2")

results_cc_country_of_birth_pr_poisson <- merge( results_cc_country_of_birth_pr_poisson_model_1, results_cc_country_of_birth_pr_poisson_model_2, by = "Exposure" )

results_cc_country_of_birth_pr_log_binomial_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_log_binomial", identities, "country_of_birth" )
results_cc_country_of_birth_pr_logistic_model_2 <- extract_results_pr( results_cc_country_of_birth_coef, "model_2_logistic", identities, "country_of_birth" )


##### exposure of interest: education #####

# extract coefficient and 95% CI
results_cc_education_coef <- list()

for ( outcome in names( all_models_cc$education ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_education_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "education", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_education
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_education_pr_poisson_model_1 <- extract_results_pr( results_cc_education_coef, "model_1_poisson", identities, "education" )
colnames( results_cc_education_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_education_pr_poisson_model_1 )[-1], "_model_1")

results_cc_education_pr_poisson_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_poisson", identities, "education" )
colnames( results_cc_education_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_education_pr_poisson_model_2 )[-1], "_model_2")

results_cc_education_pr_poisson <- merge( results_cc_education_pr_poisson_model_1, results_cc_education_pr_poisson_model_2, by = "Exposure" )

results_cc_education_pr_log_binomial_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_log_binomial", identities, "education" )
results_cc_education_pr_logistic_model_2 <- extract_results_pr( results_cc_education_coef, "model_2_logistic", identities, "education" )


##### exposure of interest: income #####

# extract coefficient and 95% CI
results_cc_income_coef <- list()

for ( outcome in names( all_models_cc$income ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_income_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "income", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_income
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_income_pr_poisson_model_1 <- extract_results_pr( results_cc_income_coef, "model_1_poisson", identities, "income" )
colnames( results_cc_income_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_income_pr_poisson_model_1 )[-1], "_model_1")

results_cc_income_pr_poisson_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_poisson", identities, "income" )
colnames( results_cc_income_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_income_pr_poisson_model_2 )[-1], "_model_2")

results_cc_income_pr_poisson <- merge( results_cc_income_pr_poisson_model_1, results_cc_income_pr_poisson_model_2, by = "Exposure" )

results_cc_income_pr_log_binomial_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_log_binomial", identities, "income" )
results_cc_income_pr_logistic_model_2 <- extract_results_pr( results_cc_income_coef, "model_2_logistic", identities, "income" )


##### exposure of interest: marital status #####

# extract coefficient and 95% CI
results_cc_marital_status_coef <- list()

for ( outcome in names( all_models_cc$marital_status ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_marital_status_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "marital_status", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_marital_status
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_marital_status_pr_poisson_model_1 <- extract_results_pr( results_cc_marital_status_coef, "model_1_poisson", identities, "marital_status" )
colnames( results_cc_marital_status_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_marital_status_pr_poisson_model_1 )[-1], "_model_1")

results_cc_marital_status_pr_poisson_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_poisson", identities, "marital_status" )
colnames( results_cc_marital_status_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_marital_status_pr_poisson_model_2 )[-1], "_model_2")

results_cc_marital_status_pr_poisson <- merge( results_cc_marital_status_pr_poisson_model_1, results_cc_marital_status_pr_poisson_model_2, by = "Exposure" )

results_cc_marital_status_pr_log_binomial_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_log_binomial", identities, "marital_status" )
results_cc_marital_status_pr_logistic_model_2 <- extract_results_pr( results_cc_marital_status_coef, "model_2_logistic", identities, "marital_status" )


##### exposure of interest: living status #####

# extract coefficient and 95% CI
results_cc_living_status_coef <- list()

for ( outcome in names( all_models_cc$living_status ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_living_status_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "living_status", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_living_status
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_living_status_pr_poisson_model_1 <- extract_results_pr( results_cc_living_status_coef, "model_1_poisson", identities, "living_status" )
colnames( results_cc_living_status_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_living_status_pr_poisson_model_1 )[-1], "_model_1")

results_cc_living_status_pr_poisson_model_2 <- extract_results_pr( results_cc_living_status_coef, "model_2_poisson", identities, "living_status" )
colnames( results_cc_living_status_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_living_status_pr_poisson_model_2 )[-1], "_model_2")

results_cc_living_status_pr_poisson <- merge( results_cc_living_status_pr_poisson_model_1, results_cc_living_status_pr_poisson_model_2, by = "Exposure" )

results_cc_living_status_pr_log_binomial_model_2 <- extract_results_pr( results_cc_living_status_coef, "model_2_log_binomial", identities, "living_status" )
results_cc_living_status_pr_logistic_model_2 <- extract_results_pr( results_cc_living_status_coef, "model_2_logistic", identities, "living_status" )


##### exposure of interest: personal support #####

# extract coefficient and 95% CI
results_cc_personal_support_coef <- list()

for ( outcome in names( all_models_cc$personal_support ) ) {
  for ( mod in models ) {
    key <- paste( outcome, mod, sep = "_" )
    results_cc_personal_support_coef[[ key ]] <- extract_results_coef(
      all_models_list = all_models_cc, 
      exposure = "personal_support", 
      outcome = outcome, 
      model_type = mod,
      variables = exposures_personal_support
    )
  }
}

# extract proportion ratio and 95% CI from each model across outcomes
results_cc_personal_support_pr_poisson_model_1 <- extract_results_pr( results_cc_personal_support_coef, "model_1_poisson", identities, "personal_support" )
colnames( results_cc_personal_support_pr_poisson_model_1 )[-1] <- paste0( colnames( results_cc_personal_support_pr_poisson_model_1 )[-1], "_model_1")

results_cc_personal_support_pr_poisson_model_2 <- extract_results_pr( results_cc_personal_support_coef, "model_2_poisson", identities, "personal_support" )
colnames( results_cc_personal_support_pr_poisson_model_2 )[-1] <- paste0( colnames( results_cc_personal_support_pr_poisson_model_2 )[-1], "_model_2")

results_cc_personal_support_pr_poisson <- merge( results_cc_personal_support_pr_poisson_model_1, results_cc_personal_support_pr_poisson_model_2, by = "Exposure" )

results_cc_personal_support_pr_log_binomial_model_2 <- extract_results_pr( results_cc_personal_support_coef, "model_2_log_binomial", identities, "personal_support" )
results_cc_personal_support_pr_logistic_model_2 <- extract_results_pr( results_cc_personal_support_coef, "model_2_logistic", identities, "personal_support" )


##### combine results #####

results_cc_pr_crude <- rbind( results_cc_age_pr_crude,
                              results_cc_age_by_sex_pr_crude,
                              results_cc_sex_pr_crude,
                              results_cc_country_of_birth_pr_crude,
                              results_cc_education_pr_crude,
                              results_cc_income_pr_crude,
                              results_cc_marital_status_pr_crude,
                              results_cc_living_status_pr_crude,
                              results_cc_personal_support_pr_crude
)

results_cc_pr_poisson <- rbind( results_cc_age_pr_poisson,
                                results_cc_age_by_sex_pr_poisson,
                                results_cc_sex_pr_poisson,
                                results_cc_country_of_birth_pr_poisson,
                                results_cc_education_pr_poisson,
                                results_cc_income_pr_poisson,
                                results_cc_marital_status_pr_poisson,
                                results_cc_living_status_pr_poisson,
                                results_cc_personal_support_pr_poisson
)

writexl::write_xlsx( merge( results_cc_pr_crude, results_cc_pr_poisson, by = "Exposure" ),
                     "results_cc_pr_poisson_2014.xlsx" )

results_cc_pr_log_binomial <- rbind( results_cc_age_pr_log_binomial_model_2,
                                     results_cc_age_by_sex_pr_log_binomial_model_2,
                                     results_cc_sex_pr_log_binomial_model_2,
                                     results_cc_country_of_birth_pr_log_binomial_model_2,
                                     results_cc_education_pr_log_binomial_model_2,
                                     results_cc_income_pr_log_binomial_model_2,
                                     results_cc_marital_status_pr_log_binomial_model_2,
                                     results_cc_living_status_pr_log_binomial_model_2,
                                     results_cc_personal_support_pr_log_binomial_model_2
)

results_cc_pr_logistic <- rbind( results_cc_age_pr_logistic_model_2,
                                 results_cc_age_by_sex_pr_logistic_model_2,
                                 results_cc_sex_pr_logistic_model_2,
                                 results_cc_country_of_birth_pr_logistic_model_2,
                                 results_cc_education_pr_logistic_model_2,
                                 results_cc_income_pr_logistic_model_2,
                                 results_cc_marital_status_pr_logistic_model_2,
                                 results_cc_living_status_pr_logistic_model_2,
                                 results_cc_personal_support_pr_logistic_model_2
)

colnames( results_cc_pr_poisson )[-1] <- paste0( colnames( results_cc_pr_poisson )[-1], "_poisson")
colnames( results_cc_pr_log_binomial )[-1] <- paste0( colnames( results_cc_pr_log_binomial )[-1], "_log_binomial")
colnames( results_cc_pr_logistic )[-1] <- paste0( colnames( results_cc_pr_logistic )[-1], "_logistic")

results_cc_pr_all_models_2014 <- results_cc_pr_poisson %>%
  full_join( results_cc_pr_log_binomial, by = "Exposure" ) %>%
  full_join( results_cc_pr_logistic, by = "Exposure" )

writexl::write_xlsx( results_cc_pr_all_models_2014, "results_cc_pr_all_models_2014.xlsx" )
```

### 5. Estimation of Proportion of Changes in Sexual Identity
#### 5.1. Complete-case analysis
##### 5.1.1. Define survey design
```{r}
# prepare dataset
d_2014_complete_cc_fluidity <- d_2014_complete

d_2014_complete_cc_fluidity$sexual_identity_fluidity <- factor(
  ifelse( d_2014_complete_cc_fluidity$sexual_identity_fluidity == 1, "changed", "unchanged" ),
  levels = c( "changed", "unchanged" )
)

d_2014_complete_cc_fluidity$country_of_birth <- factor( 
  ifelse( d_2014_complete_cc_fluidity$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2014_complete_cc_fluidity$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
)

d_2014_complete_cc_fluidity$living_alone <- as.factor(
  ifelse( d_2014_complete_cc_fluidity$living_alone == "yes", 
          "living_alone_yes",
          "living_alone_no" )
)

d_2014_complete_cc_fluidity$personal_support <- as.factor(
  ifelse( d_2014_complete_cc_fluidity$personal_support == "yes", 
          "personal_support_yes",
          "personal_support_no" ) 
)

# create survey design
survey_design_cc_fluidity <- svydesign( ids = ~ 1, 
                                        strata = ~ sampling_strata_region,
                                        weights = ~ design_weight,
                                        fpc = ~ no.of.population,
                                        data = d_2014_complete_cc_fluidity )

# the following analyses assume MCAR
```

##### 5.1.2. Caculate proportions
```{r}
# among different demographic subgroups
demographic_variables <- c( "sexual_identity_2014", "sex", "age_cat", "age_sex", "country_of_birth", "education", "occupation",
                            "income", "marital_status", "living_alone", "personal_support" )

results_list <- list()

for( variable in demographic_variables ) {
  proportions <- calculate_proportions(
    data = d_2014_complete_cc_fluidity,
    variable = variable,
    design = survey_design_cc_fluidity
  )
  
  results_list[[ variable ]] <- proportions
}

combined_results <- bind_rows( results_list )


# overall proportion in Stockholm County
prop_cc_overall <- svyciprop( formula = ~I( sexual_identity_fluidity == "changed" ),
                              design = subset( survey_design_cc_fluidity, !is.na( sexual_identity_fluidity ) ),
                              vartype = "ci",
                              method = "beta" )

prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
colnames( prop_cc_overall ) <- c( "changed_point_estimate", "changed_lower_ci", "changed_upper_ci" )
prop_cc_overall <- prop_cc_overall %>% rownames_to_column( var = "subgroup" )
prop_cc_overall[ 1, 1 ] <- "Stockholm County"
prop_cc_overall <- bind_cols( prop_cc_overall,
                              d_2014_complete_cc_fluidity[ !is.na( d_2014_complete_cc_fluidity$sexual_identity_fluidity ), ] %>% 
                                summarise( sample_size = n() ) ) %>%
  mutate( sample_size = prettyNum( sample_size, big.mark = ",", preserve.width = "none" ) )


# combine results
fluidity_cc_prop_summary_2014 <- rbind( combined_results, prop_cc_overall )
writexl::write_xlsx( fluidity_cc_prop_summary_2014, "fluidity_cc_prop_summary_2014.xlsx" )
```

### 6. Relation between Changes in Sexual Identity and Demographic Factors
#### 6.1. Complete-case analysis
##### 6.1.1. Define survey design
```{r}
##### prepare dataset #####

d_2014_cc_model_fluidity <- d_2014_complete

# exposures of interest, including sexual identity in 2014, age, sex, country of birth, education, income, marital status, living status, and personal support
levels( d_2014_cc_model_fluidity$sexual_identity_2014 )[ levels( d_2014_cc_model_fluidity$sexual_identity_2014 ) == "None of the above"] <- "Other"
d_2014_cc_model_fluidity$sexual_identity_2014_exp <- relevel( d_2014_cc_model_fluidity$sexual_identity_2014, 
                                                              ref = "Heterosexual" )

d_2014_cc_model_fluidity$age_exp <- relevel( d_2014_cc_model_fluidity$age_cat, ref = "45-59" )

d_2014_cc_model_fluidity$sex_exp <- relevel( d_2014_cc_model_fluidity$sex, ref = "Male" )

d_2014_cc_model_fluidity$country_of_birth_exp <- factor( 
  ifelse( d_2014_cc_model_fluidity$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2014_cc_model_fluidity$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
)

d_2014_cc_model_fluidity$education_exp <- relevel( d_2014_cc_model_fluidity$education, ref = ">=13 years" )

d_2014_cc_model_fluidity$income_exp <- relevel( d_2014_cc_model_fluidity$income, ref = ">4,500" )

d_2014_cc_model_fluidity$marital_status_exp <- relevel( d_2014_cc_model_fluidity$marital_status, ref = "Currently married" )

d_2014_cc_model_fluidity$living_status_exp <- relevel( d_2014_cc_model_fluidity$living_alone, ref = "no" )

d_2014_cc_model_fluidity$personal_support_exp <- relevel( d_2014_cc_model_fluidity$personal_support, ref = "yes" )


# confounding variables, including sexual identity in 2014, age, sex, country of birth, education, income, marital status, 
# living status, personal support, and place of residence (i.e., sampling strata)
d_2014_cc_model_fluidity$sexual_identity_2014_conf <- d_2014_cc_model_fluidity$sexual_identity_2014

d_2014_cc_model_fluidity$age_conf <- d_2014_cc_model_fluidity$age # age

d_2014_cc_model_fluidity$sex_conf <- d_2014_cc_model_fluidity$sex # sex

d_2014_cc_model_fluidity$country_of_birth_conf <- d_2014_cc_model_fluidity$country_of_birth # country of birth (grouped into five categories due to sparse data)

d_2014_cc_model_fluidity$education_conf <- as.factor( d_2014_cc_model_fluidity$utbniva2014 ) # education

d_2014_cc_model_fluidity$income_conf <- d_2014_cc_model_fluidity$dispink2014 # disposable income

d_2014_cc_model_fluidity$marital_status_conf <- d_2014_cc_model_fluidity$marital_status # marital status (grouped into three categories due to sparse data)

d_2014_cc_model_fluidity$living_status_conf <- d_2014_cc_model_fluidity$living_alone

d_2014_cc_model_fluidity$personal_support_conf <- as.factor( d_2014_cc_model_fluidity$F14U56G66 )

d_2014_cc_model_fluidity$place_of_residence_conf <- d_2014_cc_model_fluidity$sampling_strata_region # place of residence


##### create survey design #####
survey_design_cc_model_fluidity <- svydesign( ids = ~ 1,
                                              strata = ~ sampling_strata_region,
                                              weights = ~ design_weight,
                                              fpc = ~ no.of.population,
                                              data = d_2014_cc_model_fluidity )

# the following analyses assume MCAR
```

##### 6.1.2. Define model formula
```{r}
##### exposure of interest: sexual identity in 2014 #####

fml_sexual_identity_crude <- sexual_identity_fluidity ~ sexual_identity_2014_exp
fml_sexual_identity_model_1 <- sexual_identity_fluidity ~ sexual_identity_2014_exp + age_conf + sex_conf + country_of_birth_conf
fml_sexual_identity_model_2 <- sexual_identity_fluidity ~ sexual_identity_2014_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf

# list of formulas
fml_list_sexual_identity <- list(
  fml_sexual_identity_crude = fml_sexual_identity_crude,
  fml_sexual_identity_model_1 = fml_sexual_identity_model_1,
  fml_sexual_identity_model_2 = fml_sexual_identity_model_2
)


##### exposure of interest: age #####

fml_age_crude <- sexual_identity_fluidity ~ age_exp
fml_age_model_1 <- sexual_identity_fluidity ~ age_exp + sex_conf + country_of_birth_conf
fml_age_model_2 <- sexual_identity_fluidity ~ age_exp + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_age <- list(
  fml_age_crude = fml_age_crude,
  fml_age_model_1 = fml_age_model_1,
  fml_age_model_2 = fml_age_model_2
)


##### exposure of interest: age by sex #####

fml_age_by_sex_crude <- sexual_identity_fluidity ~ age_exp*sex_exp
fml_age_by_sex_model_1 <- sexual_identity_fluidity ~ age_exp*sex_exp + country_of_birth_conf
fml_age_by_sex_model_2 <- sexual_identity_fluidity ~ age_exp*sex_exp + country_of_birth_conf + education_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_age_by_sex <- list(
  fml_age_by_sex_crude = fml_age_by_sex_crude,
  fml_age_by_sex_model_1 = fml_age_by_sex_model_1,
  fml_age_by_sex_model_2 = fml_age_by_sex_model_2
)


##### exposure of interest: sex #####

fml_sex_crude <- sexual_identity_fluidity ~ sex_exp
fml_sex_model_1 <- sexual_identity_fluidity ~ sex_exp + age_conf + country_of_birth_conf
fml_sex_model_2 <- sexual_identity_fluidity ~ sex_exp + age_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_sex <- list(
  fml_sex_crude = fml_sex_crude,
  fml_sex_model_1 = fml_sex_model_1,
  fml_sex_model_2 = fml_sex_model_2
)


##### exposure of interest: country of birth #####

fml_country_of_birth_crude <- sexual_identity_fluidity ~ country_of_birth_exp
fml_country_of_birth_model_1 <- sexual_identity_fluidity ~ country_of_birth_exp + age_conf + sex_conf
fml_country_of_birth_model_2 <- sexual_identity_fluidity ~ country_of_birth_exp + age_conf + sex_conf + education_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_country_of_birth <- list(
  fml_country_of_birth_crude = fml_country_of_birth_crude,
  fml_country_of_birth_model_1 = fml_country_of_birth_model_1,
  fml_country_of_birth_model_2 = fml_country_of_birth_model_2
)


##### exposure of interest: education #####

fml_education_crude <- sexual_identity_fluidity ~ education_exp
fml_education_model_1 <- sexual_identity_fluidity ~ education_exp + age_conf + sex_conf + country_of_birth_conf
fml_education_model_2 <- sexual_identity_fluidity ~ education_exp + age_conf + sex_conf + country_of_birth_conf + income_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_education <- list(
  fml_education_crude = fml_education_crude,
  fml_education_model_1 = fml_education_model_1,
  fml_education_model_2 = fml_education_model_2
)


##### exposure of interest: income #####

fml_income_crude <- sexual_identity_fluidity ~ income_exp
fml_income_model_1 <- sexual_identity_fluidity ~ income_exp + age_conf + sex_conf + country_of_birth_conf
fml_income_model_2 <- sexual_identity_fluidity ~ income_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + marital_status_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_income <- list(
  fml_income_crude = fml_income_crude,
  fml_income_model_1 = fml_income_model_1,
  fml_income_model_2 = fml_income_model_2
)


##### exposure of interest: marital status #####

fml_marital_status_crude <- sexual_identity_fluidity ~ marital_status_exp
fml_marital_status_model_1 <- sexual_identity_fluidity ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_marital_status_model_2 <- sexual_identity_fluidity ~ marital_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + living_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_marital_status <- list(
  fml_marital_status_crude = fml_marital_status_crude,
  fml_marital_status_model_1 = fml_marital_status_model_1,
  fml_marital_status_model_2 = fml_marital_status_model_2
)


##### exposure of interest: living status #####

fml_living_status_crude <- sexual_identity_fluidity ~ living_status_exp
fml_living_status_model_1 <- sexual_identity_fluidity ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf
fml_living_status_model_2 <- sexual_identity_fluidity ~ living_status_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + personal_support_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_living_status <- list(
  fml_living_status_crude = fml_living_status_crude,
  fml_living_status_model_1 = fml_living_status_model_1,
  fml_living_status_model_2 = fml_living_status_model_2
)


##### exposure of interest: personal support #####

fml_personal_support_crude <- sexual_identity_fluidity ~ personal_support_exp
fml_personal_support_model_1 <- sexual_identity_fluidity ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf
fml_personal_support_model_2 <- sexual_identity_fluidity ~ personal_support_exp + age_conf + sex_conf + country_of_birth_conf + education_conf + income_conf + marital_status_conf + living_status_conf + place_of_residence_conf + sexual_identity_2014_conf

# list of formulas
fml_list_personal_support <- list(
  fml_personal_support_crude = fml_personal_support_crude,
  fml_personal_support_model_1 = fml_personal_support_model_1,
  fml_personal_support_model_2 = fml_personal_support_model_2
)

exposures <- c( "sexual_identity", "age", "age_by_sex", "sex", "country_of_birth", "education", "income", "marital_status", "living_status", "personal_support" )
```

##### 6.1.3. Crude and adjusted analyses
```{r}
# fit Poisson regression model for each exposure
models_fluidity_cc <- list()

for ( exposure in exposures ) {
  models_fluidity_cc[[ exposure ]] <- list()
  
  fml_list_name <- paste( "fml_list", exposure, sep = "_" )
  
  for ( name in names( get( fml_list_name ) ) ) {
    models_fluidity_cc[[ exposure ]][[ name ]] <- fit_model_crude( get( fml_list_name )[[ name ]],
                                                                   survey_design_cc_model_fluidity )
  }
}

# refit the model for age by sex, using female as the reference group
# to extract results for age among females
d_2014_cc_model_fluidity$sex_exp <- relevel( d_2014_cc_model_fluidity$sex, ref = "Female" )

survey_design_cc_model_fluidity_refit <- svydesign( ids = ~ 1,
                                                    strata = ~ sampling_strata_region,
                                                    weights = ~ design_weight,
                                                    fpc = ~ no.of.population,
                                                    data = d_2014_cc_model_fluidity )

refit_model_fluidity_cc_age_by_sex <- list()

for ( name in names( fml_list_age_by_sex ) ) {
  refit_model_fluidity_cc_age_by_sex[[ name ]] <- fit_model_crude( fml_list_age_by_sex[[ name ]],
                                                                   survey_design_cc_model_fluidity_refit )
}
```

##### 6.1.4. Extract results
```{r}
##### exposure of interest: sexual identity in 2014 #####

exposures_sexual_identity <- c( "sexual_identity_2014_expHomosexual", "sexual_identity_2014_expBisexual", "sexual_identity_2014_expOther" )

# extract coefficient and 95% CI
fluidity_cc_sexual_identity_coef <- list()

for ( name in names( fml_list_sexual_identity ) ) {
  
  fluidity_cc_sexual_identity_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "sexual_identity", 
    outcome = name, 
    variables = exposures_sexual_identity
  )
}

# extract risk ratio and 95% CI
fluidity_cc_sexual_identity_rr <- extract_rr_fluidity( fluidity_cc_sexual_identity_coef )


##### exposure of interest: age #####

exposures_age <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60"  )

# extract coefficient and 95% CI
fluidity_cc_age_coef <- list()

for ( name in names( fml_list_age ) ) {
  
  fluidity_cc_age_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "age", 
    outcome = name, 
    variables = exposures_age
  )
}

# extract risk ratio and 95% CI
fluidity_cc_age_rr <- extract_rr_fluidity( fluidity_cc_age_coef )


##### exposure of interest: age by sex #####

exposures_age_male <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expFemale", "age_exp30-44:sex_expFemale", "age_exp>=60:sex_expFemale" )

# extract coefficient and 95% CI among males
fluidity_cc_age_by_sex_coef_male <- list()

for ( name in names( fml_list_age_by_sex ) ) {
  
  fluidity_cc_age_by_sex_coef_male[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "age_by_sex", 
    outcome = name, 
    variables = exposures_age_male
  )
}

# extract risk ratio and 95% CI among males
fluidity_cc_age_by_sex_rr_male <- extract_rr_fluidity( fluidity_cc_age_by_sex_coef_male ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Female", Exposure ), 
                             paste0( Exposure, "_Male" ), Exposure ) )


exposures_age_female <- c( "age_exp16-29", "age_exp30-44", "age_exp>=60", "age_exp16-29:sex_expMale", "age_exp30-44:sex_expMale", "age_exp>=60:sex_expMale" )

# extract coefficient and 95% CI among females
fluidity_cc_age_by_sex_coef_female <- list()

for( model_name in names( refit_model_fluidity_cc_age_by_sex ) ) {
  
  model <- refit_model_fluidity_cc_age_by_sex[[ model_name ]]
  
  results <- cbind( coef( model )[ exposures_age_female ], 
                    confint( model, ddf = degf( model$survey.design ) )[ exposures_age_female, , drop = FALSE ] )
  
  fluidity_cc_age_by_sex_coef_female[[ model_name ]] <- results
}

# extract risk ratio and 95% CI among females
fluidity_cc_age_by_sex_rr_female <- extract_rr_fluidity( fluidity_cc_age_by_sex_coef_female ) %>%
  mutate( Exposure = ifelse( grepl( "age_exp", Exposure ) & !grepl( "Male", Exposure ), 
                             paste0( Exposure, "_Female" ), Exposure ) )

fluidity_cc_age_by_sex_rr <- rbind( fluidity_cc_age_by_sex_rr_male[ c( 1:3 ), ], 
                                    fluidity_cc_age_by_sex_rr_female[ c( 1:3 ), ] )


##### exposure of interest: sex #####

exposures_sex <- c( "sex_expFemale" )

# extract coefficient and 95% CI
fluidity_cc_sex_coef <- list()

for ( name in names( fml_list_sex ) ) {
  
  fluidity_cc_sex_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "sex", 
    outcome = name, 
    variables = exposures_sex
  )
}

# extract risk ratio and 95% CI
fluidity_cc_sex_rr <- extract_rr_fluidity( fluidity_cc_sex_coef )


##### exposure of interest: country of birth #####

exposures_country_of_birth <- c( "country_of_birth_expEurope", "country_of_birth_expOutside Europe" )

# extract coefficient and 95% CI
fluidity_cc_country_of_birth_coef <- list()

for ( name in names( fml_list_country_of_birth ) ) {
  
  fluidity_cc_country_of_birth_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "country_of_birth", 
    outcome = name, 
    variables = exposures_country_of_birth
  )
}

# extract risk ratio and 95% CI
fluidity_cc_country_of_birth_rr <- extract_rr_fluidity( fluidity_cc_country_of_birth_coef )


##### exposure of interest: education #####

exposures_education <- c( "education_exp<=9 years", "education_exp10-12 years" )

# extract coefficient and 95% CI
fluidity_cc_education_coef <- list()

for ( name in names( fml_list_education ) ) {
  
  fluidity_cc_education_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "education", 
    outcome = name, 
    variables = exposures_education
  )
}

# extract risk ratio and 95% CI
fluidity_cc_education_rr <- extract_rr_fluidity( fluidity_cc_education_coef )


##### exposure of interest: income #####

exposures_income <- c( "income_exp<=2,500", "income_exp(2,500, 3,500]", "income_exp(3,500, 4,500]" )

# extract coefficient and 95% CI
fluidity_cc_income_coef <- list()

for ( name in names( fml_list_income ) ) {
  
  fluidity_cc_income_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "income", 
    outcome = name, 
    variables = exposures_income
  )
}

# extract risk ratio and 95% CI
fluidity_cc_income_rr <- extract_rr_fluidity( fluidity_cc_income_coef )


##### exposure of interest: marital status #####

exposures_marital_status <- c( "marital_status_expNever married", "marital_status_expOther" )

# extract coefficient and 95% CI
fluidity_cc_marital_status_coef <- list()

for ( name in names( fml_list_marital_status ) ) {
  
  fluidity_cc_marital_status_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "marital_status", 
    outcome = name, 
    variables = exposures_marital_status
  )
}

# extract risk ratio and 95% CI
fluidity_cc_marital_status_rr <- extract_rr_fluidity( fluidity_cc_marital_status_coef )


##### exposure of interest: living status #####

exposures_living_status <- c( "living_status_expyes" )

# extract coefficient and 95% CI
fluidity_cc_living_status_coef <- list()

for ( name in names( fml_list_living_status ) ) {
  
  fluidity_cc_living_status_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "living_status", 
    outcome = name, 
    variables = exposures_living_status
  )
}

# extract risk ratio and 95% CI
fluidity_cc_living_status_rr <- extract_rr_fluidity( fluidity_cc_living_status_coef )


##### exposure of interest: personal support #####

exposures_personal_support <- c( "personal_support_expno" )

# extract coefficient and 95% CI
fluidity_cc_personal_support_coef <- list()

for ( name in names( fml_list_personal_support ) ) {
  
  fluidity_cc_personal_support_coef[[ name ]] <- extract_results_coef_crude(
    all_models_list = models_fluidity_cc, 
    exposure = "personal_support", 
    outcome = name, 
    variables = exposures_personal_support
  )
}

# extract risk ratio and 95% CI
fluidity_cc_personal_support_rr <- extract_rr_fluidity( fluidity_cc_personal_support_coef )


##### combine results #####

fluidity_cc_rr <- rbind( fluidity_cc_sexual_identity_rr,
                         fluidity_cc_age_rr,
                         fluidity_cc_age_by_sex_rr,
                         fluidity_cc_sex_rr,
                         fluidity_cc_country_of_birth_rr,
                         fluidity_cc_education_rr,
                         fluidity_cc_income_rr,
                         fluidity_cc_marital_status_rr,
                         fluidity_cc_living_status_rr,
                         fluidity_cc_personal_support_rr
)

writexl::write_xlsx( fluidity_cc_rr, "fluidity_cc_rr_2014.xlsx" )
```