---
title: "Self-reported sexual identity in Stockholm County in 2021"
author: Guoqiang Zhang
email: guoqiang.zhang@ki.se
output: html_notebook
editor_options: 
  chunk_output_type: console
---

### 1. Load Packages
```{r}
library(haven)
library(data.table)
library(naniar)
library(tidyverse)
library(jomo)
library(mitml)
library(mitools)
library(ggplot2)
library(ggbreak)
library(mice)
library(ggrepel)
library(ggpubr)
library(ggmosaic)
library(tidyr)
library(dplyr)
library(finalfit)
library(survey)
library(svyVGAM)
```

### 2. Import and Visualise Data
```{r}
# d_2021 <- read_sas( "G:/CES/SRHR/SPHC LGBTQ health data/sphc21.sas7bdat" )

# sampling strata
n_miss( d_2021$stratum )
d_2021$sampling_strata <- as.factor( d_2021$stratum )
length( unique( d_2021$sampling_strata ) ) # 38 strata

d_2021 <- d_2021 %>%
  mutate( sampling_strata_region = recode( sampling_strata, 
                                           `114` = "Upplands Väsby",
                                           `115` = "Vallentuna",
                                           `117` = "Österåker",
                                           `120` = "Värmdö",
                                           `123` = "Järfälla",
                                           `125` = "Ekerö",
                                           `126` = "Huddinge",
                                           `127` = "Botkyrka",
                                           `128` = "Salem",
                                           `136` = "Haninge",
                                           `138` = "Tyresö",
                                           `139` = "Upplands-Bro",
                                           `140` = "Nykvarn",
                                           `160` = "Täby",
                                           `162` = "Danderyd",
                                           `163` = "Sollentuna",
                                           `181` = "Södertälje",
                                           `182` = "Nacka",
                                           `183` = "Sundbyberg",
                                           `184` = "Solna",
                                           `186` = "Lidingö",
                                           `187` = "Vaxholm",
                                           `188` = "Norrtälje",
                                           `191` = "Sigtuna",
                                           `192` = "Nynäshamn",
                                           `180103` = "Spånga-Tensta",
                                           `180104` = "Hässelby-Vällingby",
                                           `180106` = "Bromma",
                                           `180108` = "Kungsholmen",
                                           `180109` = "Norrmalm",
                                           `180110` = "Östermalm",
                                           `180115` = "Skarpnäck",
                                           `180118` = "Farsta",
                                           `180124` = "Skärholmen",
                                           `180125` = "Rinkeby-Kista",
                                           `180127` = "Södermalm",
                                           `180128` = "Enskede, Årsta-Vantör",
                                           `180129` = "Hägersten-Älvsjö"
                                           ) )

# sexual identity
table( d_2021$F21F45_Q57, useNA = "always" )
d_2021$sexual_identity <- factor( ifelse( d_2021$F21F45_Q57 == 1, "Heterosexual", 
                                          ifelse( d_2021$F21F45_Q57 == 2, "Homosexual",
                                                  ifelse( d_2021$F21F45_Q57 == 3, "Bisexual", "None of the above" ) ) ),
                                  levels = c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" ) )
table( d_2021$sexual_identity, useNA = "always" )

# sex
table( d_2021$kon, useNA = "always" )
d_2021$sex <- factor( ifelse( d_2021$kon == 1, "Male", "Female" ), 
                      levels = c( "Male", "Female" ) )
table( d_2021$sex, useNA = "always" )

# age
summary( d_2021$F21alder )
d_2021$age <- d_2021$F21alder
d_2021$age_cat <- factor( ifelse( d_2021$age <= 29, "16-29", 
                                  ifelse( d_2021$age >=30 & d_2021$age <= 44, "30-44",
                                          ifelse( d_2021$age >= 45 & d_2021$age <= 59, "45-59", ">=60" ) ) ),
                          levels = c( "16-29", "30-44", "45-59", ">=60" ) )
table( d_2021$age_cat, useNA = "always" )

# interaction term between age and sex
d_2021$age_sex <- interaction( d_2021$age_cat, d_2021$sex )

# country of birth
table( d_2021$fodelseland, useNA = "always" )
d_2021$country_of_birth <- factor( ifelse( d_2021$fodelseland == "Afrika", "Africa",
                                           ifelse( d_2021$fodelseland == "Asien", "Asia",
                                                   ifelse( d_2021$fodelseland == "Europa", "Europe",
                                                           ifelse( d_2021$fodelseland == "Sverige", "Sweden", "Americas" ) ) ) ),
                                   levels = c( "Africa", "Americas", "Asia", "Europe", "Sweden" ) )
table( d_2021$country_of_birth, useNA = "always" )

# education
table( d_2021$utbniva2021, useNA = "always" )
d_2021$education <- factor( ifelse( d_2021$utbniva2021 <= 2, "<=9 years",
                                    ifelse( d_2021$utbniva2021 <= 4, "10-12 years", ">=13 years" ) ),
                            levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
table( d_2021$education, useNA = "always" )

# disposable income
summary( d_2021$dispink2021, useNA = "always" )
d_2021$dispink2021[ d_2021$dispink2021 < 0 ] <- NA
d_2021$income <- factor( ifelse( d_2021$dispink2021 <= 2500, "<=2,500",
                                 ifelse( d_2021$dispink2021 > 2500 & d_2021$dispink2021 <= 3500, "(2,500, 3,500]",
                                         ifelse( d_2021$dispink2021 > 3500 & d_2021$dispink2021 <= 4500, "(3,500, 4,500]", ">4,500" ) ) ),
                         levels = c( "<=2,500", "(2,500, 3,500]", "(3,500, 4,500]", ">4,500" ) )
table( d_2021$income, useNA = "always" )

# marital status
table( d_2021$civil2021, useNA = "always" )
d_2021$marital_status <- factor( ifelse( d_2021$civil2021 == "G" | d_2021$civil2021 == "RP", "Currently married",
                                         ifelse( d_2021$civil2021 == "OG", "Never married", "Other" ) ), 
                                 levels = c( "Never married", "Currently married", "Other" ) )
table( d_2021$marital_status, useNA = "always" )


##### demographic characteristics #####

# among respondents (n = 23,066)
# make characteristics table by sexual identity
explanatory =  c( "sex", "age_cat", "country_of_birth", "education", "income", "marital_status" )
dependent = "sexual_identity"

d_2021_table <- d_2021 %>% 
  summary_factorlist( dependent,
                      explanatory, 
                      na_include = TRUE,
                      na_include_dependent = TRUE, 
                      total_col = TRUE,
                      add_col_totals = TRUE )

# Fisher's test
x1 <- table( d_2021$sex, d_2021$sexual_identity )
x1
format( round( fisher.test( x1[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x1[, c( 1, 4 ) ] )$p.value, 3 ), nsmall = 3 )

x2 <- table( d_2021$age_cat, d_2021$sexual_identity )
x2
format( round( fisher.test( x2[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x2[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x3 <- table( d_2021$country_of_birth, d_2021$sexual_identity )
x3
format( round( fisher.test( x3[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x3[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x4 <- table( d_2021$education, d_2021$sexual_identity )
x4
format( round( fisher.test( x4[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 3 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x4[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x5 <- table( d_2021$income, d_2021$sexual_identity )
x5
format( round( fisher.test( x5[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x5[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )

x6 <- table( d_2021$marital_status, d_2021$sexual_identity )
x6
format( round( fisher.test( x6[, c( 1:2 ) ] )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 3 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )
format( round( fisher.test( x6[, c( 1, 4 ) ], simulate.p.value = TRUE )$p.value, 3 ), nsmall = 3 )


##### design weights #####

summary( d_2021$F21dvikt )
d_2021$design_weight <- d_2021$F21dvikt


##### non-response #####

# unit non-response
d_2021$design_weight_unit_nonresponse <- d_2021$F21dbvikt # weights calculated assuming Missing Completely At Random (MCAR) within each stratum
summary( d_2021$design_weight_unit_nonresponse )
sum( d_2021$design_weight_unit_nonresponse ) # No. of source population = 1,827,424

unitresponse_prob <- d_2021 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( unitresponse_prob = unique( design_weight ) / unique( design_weight_unit_nonresponse ),
             no.of.population = sum( design_weight_unit_nonresponse ),
             sample_size = unique( no.of.population )/unique( design_weight ) ) # calculate overall unit response rate, and no. of population and sample size within each stratum

d_2021 <- d_2021 %>% 
  left_join( unitresponse_prob, by = "sampling_strata_region" )

# item non-response
itemresponse_prob <- d_2021 %>% 
  group_by( sampling_strata_region ) %>% 
  summarise( itemresponse_prob = sum( !is.na( sexual_identity ) ) / n() ) # calculate item response rate

d_2021 <- d_2021 %>% 
  left_join( itemresponse_prob, by = "sampling_strata_region" ) %>% 
  mutate( itemresponse_prob = ifelse( is.na( sexual_identity ), 0, itemresponse_prob ) )


##### summary of stratified sampling #####

sampling_frame_2021 <- as.data.frame( d_2021 %>% 
                                   group_by( sampling_strata_region ) %>% 
                                   reframe( no.of.population = unique( no.of.population ), 
                                            sample_size = unique( no.of.population/design_weight ),
                                            unitresponse = n(),
                                            itemresponse = sum( itemresponse_prob != 0 ) ) )

sampling_frame_2021$unitresponse_rate <- sampling_frame_2021$unitresponse/sampling_frame_2021$sample_size
sampling_frame_2021$itemresponse_rate <- sampling_frame_2021$itemresponse/sampling_frame_2021$unitresponse
sampling_frame_2021$overallresponse_rate <- sampling_frame_2021$itemresponse/sampling_frame_2021$sample_size

sampling_frame_2021$unitresponse_label <- paste0( sampling_frame_2021$unitresponse, " (", 
                                             sprintf( "%.1f", sampling_frame_2021$unitresponse_rate*100 ), "%)" )
sampling_frame_2021$overallresponse_label <- paste0( sampling_frame_2021$itemresponse, " (", 
                                                sprintf( "%.1f", sampling_frame_2021$overallresponse_rate*100 ), "%)" )

round( weighted.mean( sampling_frame_2021$unitresponse_rate, sampling_frame_2021$no.of.population ), 3 ) # overall unit response rate
round( weighted.mean( sampling_frame_2021$itemresponse_rate, sampling_frame_2021$no.of.population ), 3 ) # overall item response rate
round( weighted.mean( sampling_frame_2021$overallresponse_rate, sampling_frame_2021$no.of.population ), 3 ) # overall response rate

writexl::write_xlsx( sampling_frame_2021, "sampling_frame_2021.xlsx" )


##### calibrated weights #####

d_2021$calibrated_weight <- d_2021$F21kalvikt

# visualize calibrated weights across sampling strata
ggplot( d_2021 %>% 
          group_by( sampling_strata_region ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( sampling_strata_region, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 230 ), breaks = c( 0, 50, 100, 150, 200 ), expand = c( 0, 0 ) ) +
  labs( y = NULL, x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ) )


##### replicating non-respondent rows for sampling design #####

# because d_2021 includes data only for respondents (unit response), we need to duplicate rows for non-respondents
# so that the final dataset represents the sampling process
rows_to_add <- d_2021 %>%
  group_by( sampling_strata_region ) %>%
  summarise( to_add = unique( sample_size ) - n(),
             no.of.population = unique( no.of.population ),
             sample_size = unique( sample_size ),
             design_weight = unique( design_weight ) )

sum( rows_to_add$to_add ) # 24,819 non-respondents

rows_to_add$to_add <- round( rows_to_add$to_add ) # to resolve floating-point precision issues

replicated_rows <- rows_to_add[ rep( row.names( rows_to_add ), rows_to_add$to_add ), c( 1, 3:5 ) ]

d_2021_complete <- bind_rows( d_2021, replicated_rows ) # 47,885 individuals in the original sample
```

### 3. Estimation of Proportions of Sexual Identities
#### 3.1. Complete-case analysis
##### 3.1.1. Define survey design
```{r}
# prepare dataset
d_2021_complete_cc <- d_2021_complete

d_2021_complete_cc$country_of_birth <- factor( 
  ifelse( d_2021_complete_cc$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2021_complete_cc$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

# create survey design
survey_design_cc <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ design_weight,
                               fpc = ~ no.of.population,
                               data = d_2021_complete_cc )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

# the following analyses assume MCAR
```

##### 3.1.2. By sex
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                        by = ~ sex,
                        design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( sex ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_sex
}

prop_cc_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_sex <- left_join( prop_cc_sex,
                          d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                             !is.na( d_2021_complete_cc$sex ), ] %>% 
                            group_by( subgroup = sex ) %>% 
                            summarise( sample_size_2021 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.3. By age group
###### 3.1.3.1. Calculate proportion by pre-specified age cut-off
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                        by = ~ age_cat,
                        design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( age_cat ) ),
                        FUN = svyciprop,
                        vartype = "ci",
                        method = "beta" )
  
  colnames( prop_cc_age ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_age
}

prop_cc_age <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age <- left_join( prop_cc_age,
                          d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                             !is.na( d_2021_complete_cc$age_cat ), ] %>% 
                            group_by( subgroup = age_cat ) %>% 
                            summarise( sample_size_2021 = n() ),
                          by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

###### 3.1.3.2. Calculate proportion ratio by varying age cut-offs
```{r}
d_2021_iteration_age <- d_2021_complete

min_age <- min( d_2021_iteration_age$age, na.rm = TRUE )

categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )

results_df <- data.frame()

for ( cut_off in ( min_age + 1 ):90 ) {
  d_2021_iteration_age$age_iteration <- ifelse( d_2021_iteration_age$age <= cut_off, "young", "old" )
  
  survey_design_iteration_age <- svydesign( ids = ~ 1, 
                                            strata = ~ sampling_strata_region,
                                            weights = ~ design_weight,
                                            fpc = ~ no.of.population,
                                            data = d_2021_iteration_age )
  
  list_of_df <- list()
  
  for ( cat in categories ) {
    prop_cc_age_iteration <- svyby(
      formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
      by = ~ age_iteration,
      design = subset( survey_design_iteration_age, !is.na( sexual_identity ) & !is.na( age ) ),
      FUN = svyciprop,
      method = "beta" )
    
    colnames( prop_cc_age_iteration ) <- c( "subgroup", 
                                            paste0( cat, "_point_estimate_2021" ), 
                                            paste0( cat, "_se_2021" ) )
    
    list_of_df[[cat]] <- prop_cc_age_iteration
  }
  
  prop_cc_age_iteration_merged <- Reduce( function( df1, df2 ) { 
    merge( df1, df2, by = "subgroup" ) 
    }, 
    list_of_df
    )
  
  prop_cc_age_iteration_merged$cut_off <- cut_off
  
  results_df <- rbind( results_df, prop_cc_age_iteration_merged )
  }

results_wide <- results_df %>%
  select( -ends_with( "_se_2021" ) ) %>%
  pivot_wider( names_from = subgroup, 
               values_from = c( Heterosexual_point_estimate_2021, 
                                Homosexual_point_estimate_2021, 
                                Bisexual_point_estimate_2021, 
                                `None of the above_point_estimate_2021` ) 
               )

colnames( results_wide ) <- gsub( "_point_estimate_2021", "", colnames( results_wide ) )

results_wide$Heterosexual_pr_2021 <- results_wide$Heterosexual_young/results_wide$Heterosexual_old
results_wide$Homosexual_pr_2021 <- results_wide$Homosexual_young/results_wide$Homosexual_old
results_wide$Bisexual_pr_2021 <- results_wide$Bisexual_young/results_wide$Bisexual_old
results_wide$`None of the above_pr_2021` <- results_wide$`None of the above_young`/results_wide$`None of the above_old`

results_wide$Heterosexual_pr_2021[ is.infinite( results_wide$Heterosexual_pr_2021 ) ] <- NA
results_wide$Homosexual_pr_2021[ is.infinite( results_wide$Homosexual_pr_2021 ) ] <- NA
results_wide$Bisexual_pr_2021[ is.infinite( results_wide$Bisexual_pr_2021 ) ] <- NA
results_wide$`None of the above_pr_2021`[ is.infinite( results_wide$`None of the above_pr_2021` ) ] <- NA

writexl::write_xlsx( results_wide, "prop_cc_age_iteration_2021.xlsx" )
```

##### 3.1.4. By sex*age group
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_age_sex <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                            by = ~ age_sex,
                            design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( age_sex ) ),
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_age_sex ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_age_sex
}

prop_cc_age_sex <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_age_sex <- left_join( prop_cc_age_sex,
                              d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                                 !is.na( d_2021_complete_cc$age_sex ), ] %>% 
                                group_by( subgroup = age_sex ) %>% 
                                summarise( sample_size_2021 = n() ),
                              by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.5. By education
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_education <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                              by = ~ education,
                              design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( education ) ),
                              FUN = svyciprop,
                              vartype = "ci",
                              method = "beta" )
  
  colnames( prop_cc_education ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_education
}

prop_cc_education <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_education <- left_join( prop_cc_education,
                                d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                                   !is.na( d_2021_complete_cc$education ), ] %>% 
                                  group_by( subgroup = education ) %>% 
                                  summarise( sample_size_2021 = n() ),
                                by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.6. By income
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_income <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                           by = ~ income,
                           design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( income ) ),
                           FUN = svyciprop,
                           vartype = "ci",
                           method = "beta" )
  
  colnames( prop_cc_income ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_income
}

prop_cc_income <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_income <- left_join( prop_cc_income,
                             d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                                   !is.na( d_2021_complete_cc$income ), ] %>% 
                               group_by( subgroup = income ) %>% 
                               summarise( sample_size_2021 = n() ),
                             by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.7. By country of birth
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_country_of_birth <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                     by = ~ country_of_birth,
                                     design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( country_of_birth ) ),
                                     FUN = svyciprop,
                                     vartype = "ci",
                                     method = "beta" )
  
  colnames( prop_cc_country_of_birth ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_country_of_birth
}

prop_cc_country_of_birth <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_country_of_birth <- left_join( prop_cc_country_of_birth,
                                       d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                                   !is.na( d_2021_complete_cc$country_of_birth ), ] %>% 
                                         group_by( subgroup = country_of_birth ) %>% 
                                         summarise( sample_size_2021 = n() ),
                                       by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.8. By marital status
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_marital_status <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                   by = ~ marital_status,
                                   design = subset( survey_design_cc, !is.na( sexual_identity ) & !is.na( marital_status ) ),
                                   FUN = svyciprop,
                                   vartype = "ci",
                                   method = "beta" )
  
  colnames( prop_cc_marital_status ) <- c( "subgroup", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_marital_status
}

prop_cc_marital_status <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "subgroup" )
}, 
list_of_df )

prop_cc_marital_status <- left_join( prop_cc_marital_status,
                                     d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ) &
                                                   !is.na( d_2021_complete_cc$marital_status ), ] %>% 
                                       group_by( subgroup = marital_status ) %>% 
                                       summarise( sample_size_2021 = n() ),
                                     by = "subgroup" ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.9. Overall proportions of sexual identities in Stockholm County
```{r}
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                design = subset( survey_design_cc, !is.na( sexual_identity ) ),
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  
  list_of_df[[cat]] <- prop_cc_overall
}

prop_cc_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
}, 
list_of_df ) %>% 
  as.data.frame() %>%
  rownames_to_column( var = "subgroup" )

prop_cc_overall[ 1, 1 ] <- "Stockholm County"

prop_cc_overall <- bind_cols( prop_cc_overall,
                              d_2021_complete_cc[ !is.na( d_2021_complete_cc$sexual_identity ), ] %>% 
                                summarise( sample_size_2021 = n() ) ) %>%
  mutate( sample_size_2021 = prettyNum( sample_size_2021, big.mark = ",", preserve.width = "none" ) )
```

##### 3.1.10. Merge datasets
```{r}
prop_cc_summary_2021 <- rbind( prop_cc_sex, 
                               prop_cc_age,
                               prop_cc_age_sex,
                               prop_cc_education, 
                               prop_cc_income, 
                               prop_cc_country_of_birth, 
                               prop_cc_marital_status,
                               prop_cc_overall 
                               )

writexl::write_xlsx( prop_cc_summary_2021, "prop_cc_summary_2021.xlsx" )
```

#### 3.2. Multiple imputation and inverse probability weighting
##### 3.2.1. Multiple imputation
###### 3.2.1.1. Obtain incomplete dataset
```{r}
d_2021_ic <- as.data.frame( d_2021 %>% 
                              select( "sampling_strata", "sampling_strata_region", "no.of.population", "calibrated_weight", "sexual_identity", "age", "sex", "fodelseland", "utbniva2021", "dispink2021", "marital_status" ) ) %>%
  rename(
    country_of_birth = fodelseland, 
    education = utbniva2021, 
    income = dispink2021 
    )

summary( d_2021_ic )
d_2021_ic <- within( d_2021_ic, country_of_birth <- factor( country_of_birth ) )
d_2021_ic <- within( d_2021_ic, education <- factor( education ) )

sapply( d_2021_ic, class ) # all continuous variables are numeric, and all categorical variables are factor
```

###### 3.2.1.2. Visualize missing pattern and select auxiliary variables
```{r}
# identify missing variables
vis_miss( d_2021_ic )
n_miss( d_2021_ic )
md.pattern( d_2021_ic )
miss_var_summary( d_2021_ic ) # 2.2% missing in sexual_identity, 2.1% in education, and 0.2% in income

# select auxiliary variables for sexual identity
# check whether potential auxiliary variables are correlated with sexual identity
names( d_2021_ic )
plot( d_2021_ic$sampling_strata_region, d_2021_ic$sexual_identity )
plot( d_2021_ic$sexual_identity, d_2021_ic$age )
plot( d_2021_ic$sex, d_2021_ic$sexual_identity )
plot( d_2021_ic$country_of_birth, d_2021_ic$sexual_identity )
plot( d_2021_ic$education, d_2021_ic$sexual_identity )
plot( d_2021_ic$sexual_identity, d_2021_ic$income )
plot( d_2021_ic$marital_status, d_2021_ic$sexual_identity )

# check whether potential auxiliary variables are related to sexual identity being missing
{
  explanatory = c( "sampling_strata_region", "age", "sex", "country_of_birth", "education", "income", "marital_status" )
  dependent = "sexual_identity"
  d_2021_ic %>% missing_pairs( dependent, explanatory, position = "fill", showYAxisPlotLabels = TRUE )
  }

# finally, include all the variables as auxiliary variables for sexual identity, including sampling strata, age, sex, country of birth, education, income, and marital status
```

###### 3.2.1.3. Two-level multivariate normal imputation with latent normal variable approach
```{r}
# use multiple imputation to account for item non-response
# assume Missing At Random (MAR)

# create calibrated weight strata
d_2021_ic$calibrated_weight_strata <- as.factor( cut( d_2021_ic$calibrated_weight,
                                                      breaks = quantile( d_2021_ic$calibrated_weight, probs = seq( 0, 1, length.out = 39 ) ),
                                                      labels = 1:38,
                                                      include.lowest = TRUE,
                                                      right = TRUE ) )

# visualize calibrated weight strata
ggplot( d_2021_ic %>% 
          group_by( calibrated_weight_strata ) %>% 
          summarise( mean_weight = mean( calibrated_weight ), sd_weight = sd( calibrated_weight ) ),
        aes( y = reorder( calibrated_weight_strata, -mean_weight ), x = mean_weight ) ) +
  geom_line( aes( group = 1 ) ) +
  geom_point() +
  geom_errorbarh( aes( xmin = mean_weight - sd_weight, xmax = mean_weight + sd_weight ), height = 0.4, alpha = 0.5 ) +
  scale_x_continuous( limits = c( 0, 280 ), 
                      breaks = c( 0, 50, 100, 150, 200, 250 ), 
                      expand = c( 0, 0 ) ) +
  labs( y = "Calibrated Weight Strata", x = "Mean and Standard Deviation of Calibrated Weights" ) +
  theme_classic() +
  theme( axis.text.y = element_text( family = "Arial", size = 11 ),
         axis.title.y = element_text( family = "Arial", size = 11 ),
         axis.text.x = element_text( family = "Arial", size = 11 ),
         axis.title.x = element_text( family = "Arial", size = 11 )
         )

summary( d_2021_ic )
sapply( d_2021_ic, class ) # all continuous variables are numeric, and all categorical variables are factor


# add random effects in intercepts and predictors
fml_imp <- sexual_identity + education + income ~ 1 + age + sex + age*sex + country_of_birth + marital_status + sampling_strata_region + ( 1 + age + sex + country_of_birth + marital_status + sampling_strata_region | calibrated_weight_strata )

# perform a "dry run"
ini <- jomoImpute( data = d_2021_ic,
                   formula = fml, 
                   random.L1 = "full", # random covariance matrix of residuals
                   n.burn = 500,
                   n.iter = 2,
                   m = 2,
                   seed = 12345 # set the seed so that results can be reproduced
                   )

summary( ini ) # summarize model and display convergence statistics
plot( ini ) # display convergence and autocorrelation plots

# generate imputation
imp <- jomoImpute( data = d_2021_ic,
                   formula = fml, 
                   random.L1 = "full",
                   n.burn = 2000,
                   n.iter = 1000,
                   m = 50,
                   seed = 12345
                   )

save.image( file = "working_environment_2021.RData" )
```

###### 3.2.1.4. Validate imputations
```{r}
# validate imputation
summary( imp ) # summarize model and display convergence statistics
plot( imp ) # display convergence plots and autocorrelation plot

# extract list of imputed datasets
implist <- mitmlComplete( imp, "all" )
```

##### 3.2.2. Inverse probability weighting
```{r}
# use inverse probability weighting to account for unit non-response

# transform the imputed datasets
implist <- within( implist, {
  
  # age
  age_cat <- factor( ifelse( age <= 29, "16-29", 
                             ifelse( age >=30 & age <= 44, "30-44",
                                     ifelse( age >= 45 & age <= 66, "45-66", ">=67" ) ) ),
                     levels = c( "16-29", "30-44", "45-66", ">=67" ) )

  # country of birth
  country_of_birth_cat <- factor( ifelse( country_of_birth == "Sverige", "Sweden",
                                      ifelse( country_of_birth == "Europa", "Europe", "Outside Europe" ) ),
                              levels = c( "Sweden", "Europe", "Outside Europe" ) )
  
  # education
  education_cat <- factor( ifelse( as.numeric( as.character( education ) ) <= 2, "<=9 years",
                               ifelse( as.numeric( as.character( education ) ) <= 4, "10-12 years", ">=13 years" ) ),
                       levels = c( "<=9 years", "10-12 years", ">=13 years" ) )
  
  # disposable income
  income_cat <- factor( ifelse( income < 1500, "<1,500",
                            ifelse( income >= 1500 & income < 3000, "[1,500, 3,000)",
                                    ifelse( income >= 3000 & income < 4500, "[3,000, 4,500)", ">=4,500" ) ) ),
                    levels = c( "<=1,500", "[1,500, 3,000)", "[3,000, 4,500)", ">=4,500" ) )
  
  # marital status
  marital_status_cat <- factor( ifelse( marital_status == "G" | marital_status == "RP", "Currently married", "Other" ), 
                            levels = c( "Currently married", "Other" ) )
  
  } )

survey_design_imp <- svydesign( ids = ~ 1, 
                               strata = ~ sampling_strata_region,
                               weights = ~ calibrated_weight,
                               fpc = ~ no.of.population,
                               data = imputationList( implist ) )

# calculate proportion of each sexual identity across sampling strata
categories <- c( "Heterosexual", "Homosexual", "Bisexual", "None of the above" )
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_stratum <- svyby( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                            by = ~ sampling_strata_region, # equivalent to calculating the proportion separately for each stratum 
                            design = survey_design_cc,
                            FUN = svyciprop,
                            vartype = "ci",
                            method = "beta" )
  
  colnames( prop_cc_stratum ) <- c( "sampling_strata_region", paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  list_of_df[[cat]] <- prop_cc_stratum
}

prop_cc_summary <- Reduce( function( df1, df2 ) { 
  merge( df1, df2, by = "sampling_strata_region" ) 
  }, 
  list_of_df )

# calculate overall proportions of each sexual identity
list_of_df <- list()

for ( cat in categories ) {
  prop_cc_overall <- svyciprop( formula = as.formula( paste0( "~ I( sexual_identity == '", cat, "' )" ) ),
                                design = survey_design_cc,
                                vartype = "ci",
                                method = "beta" )
  
  prop_cc_overall <- data.frame( prop_cc_overall[ 1 ], confint( prop_cc_overall )[ 1 ], confint( prop_cc_overall )[ 2 ] )
  colnames( prop_cc_overall ) <- c( paste0( cat, "_point_estimate_2021" ), paste0( cat, "_lower_ci_2021" ), paste0( cat, "_upper_ci_2021" ) )
  list_of_df[[cat]] <- prop_cc_overall
}

df_overall <- Reduce( function( df1, df2 ) {
  cbind( df1, df2 )
  }, 
  list_of_df )

df_overall$sampling_strata_region <- "Stockholm County"
prop_cc_summary_2021 <- rbind( prop_cc_summary, df_overall )
```

### 4. Relation between Sexual Identity and Demographic Factors
#### 4.1. Complete-case analysis
##### 4.1.1. Define survey design
```{r}
# prepare dataset
d_2021_complete_lbr <- d_2021_complete

d_2021_complete_lbr$country_of_birth <- factor( 
  ifelse( d_2021_complete_lbr$country_of_birth == "Sweden", "Sweden",
          ifelse( d_2021_complete_lbr$country_of_birth == "Europe", "Europe", "Outside Europe" ) ),
  levels = c( "Sweden", "Europe", "Outside Europe" )
  )

d_2021_complete_lbr$marital_status <- relevel( d_2021_complete_lbr$marital_status, ref = "Currently married" )

d_2021_complete_lbr$sexual_minority <- factor(
  ifelse( d_2021_complete_lbr$sexual_identity == "Heterosexual", "Heterosexual", "Sexual_minority" ),
  levels = c( "Heterosexual", "Sexual_minority" ) )

d_2021_complete_lbr$homosexual <- factor(
  ifelse( d_2021_complete_lbr$sexual_identity == "Homosexual", "Homosexual", "Non-homosexual" ),
  levels = c( "Non-homosexual", "Homosexual" ) )

d_2021_complete_lbr$bisexual <- factor(
  ifelse( d_2021_complete_lbr$sexual_identity == "Bisexual", "Bisexual", "Non-bisexual" ),
  levels = c( "Non-bisexual", "Bisexual" ) )

d_2021_complete_lbr$other <- factor(
  ifelse( d_2021_complete_lbr$sexual_identity == "None of the above", "Other", "Non-other" ),
  levels = c( "Non-other", "Other" ) )

d_2021_complete_lbr <- d_2021_complete_lbr %>% 
  mutate( 
    nomiss = !is.na( sexual_identity ) & !is.na( age_cat ) & !is.na( sex ) & !is.na( education ) &
      !is.na( country_of_birth ) & !is.na( income ) & !is.na( marital_status ) 
    )

# create survey design
survey_design_cc_lbr <- svydesign( ids = ~ 1, 
                                   strata = ~ sampling_strata_region,
                                   weights = ~ design_weight,
                                   fpc = ~ no.of.population,
                                   data = d_2021_complete_lbr )

# the following analyses assume MCAR
```

##### 4.1.2. Fit log-binomial regression model
```{r}
# sexual minority group vs heterosexual
model_lbr_cc_sexual_minority <- svyglm(
  sexual_minority ~ age_cat + sex + age_cat*sex + education + country_of_birth + income + marital_status + sampling_strata_region,
  design = subset( survey_design_cc_lbr, nomiss ),
  family = quasibinomial( link = "logit" )
  )

summary( model_lbr_cc_heterosexual )

model_lr_cc_homosexual_output <- round( cbind(
  summary(
    model_lbr_cc_heterosexual,
    df.resid = degf( model_lbr_cc_heterosexual$survey.design )
  )$coef,
  confint(
    model_lbr_cc_heterosexual,
    ddf = degf( model_lbr_cc_heterosexual$survey.design )
  ) ), 4 )

cbind( "AOR" = exp(   coef(model_lbr_cc_sexual_minority)),
                       exp(confint(model_lbr_cc_sexual_minority,
                           df.resid=degf(model_lbr_cc_sexual_minority$survey.design))))


# bisexual vs heterosexual
model_lr_cc_bisexual <- svyglm(
  fml_lr,
  design = subset(
    survey_design_cc_lr,
    sexual_identity == "Heterosexual" |
      sexual_identity == "Bisexual"
  ),
  family = quasibinomial( link = "logit" )
)

summary(model_lr_cc_bisexual)


# other vs heterosexual
model_lr_cc_other <- svyglm(
  fml_lr,
  design = subset(
    survey_design_cc_lr,
    sexual_identity == "Heterosexual" |
      sexual_identity == "None of the above"
  ),
  family = quasibinomial( link = "logit" )
)

summary(model_lr_cc_other)




round(
  cbind(
    summary(model_lr_cc_homosexual,
              df.resid=degf(model_lr_cc_homosexual$survey.design))$coef,
    confint(model_lr_cc_homosexual,
              ddf=degf(model_lr_cc_homosexual$survey.design))
  )
, 4)

PR <- cbind("PR" = exp(   coef(model_lr_cc_homosexual)),
                       exp(confint(model_lr_cc_homosexual,
                           df.resid=degf(model_lr_cc_homosexual$survey.design))))[-1,]
round(PR, 3)


model_lr_cc_homosexual_output <- merge( coef( model_lr_cc_homosexual ) %>% 
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ),
                                confint( model_lr_cc_homosexual ) %>%
                                  as.data.frame() %>%
                                  rownames_to_column( var = "category" ), 
                                by = "category" ) %>%
  select( "category", "Coef", "2.5 %", "97.5 %", "p" ) %>%
  mutate(
    OR_2021 = exp( Coef ),
    lower_ci_2021 = exp( `2.5 %` ),
    upper_ci_2021 = exp( `97.5 %` ) ) %>%
  rename(
    category_2021 = category,
    p_2021 = p
    )

levels( survey_design_cc_lr$variables$sexual_identity )
new_cats <- c( "Homosexual", "Bisexual", "None of the above" )

for ( i in 1:3 ) {
  model_lr_cc_output$category_2021 <- gsub(
    pattern = paste0( ":", i ), 
    replacement = paste0( "_", new_cats[i] ), 
    x = model_lr_cc_output$category_2021 )
  }

model_lr_cc_output_wide <- model_lr_cc_output %>%
  separate( category_2021, into = c( "category_2021", "sexual_identity" ), 
            sep = "_(?=[^_]+$)",
            extra = "merge" ) %>%
  pivot_wider(
    names_from = sexual_identity, 
    values_from = c( Coef, `2.5 %`, `97.5 %`, p_2021, OR_2021, lower_ci_2021, upper_ci_2021 )
    )

model_lr_cc_output_wide <- model_lr_cc_output_wide %>% select( "category_2021", "Coef_Homosexual", "2.5 %_Homosexual", "97.5 %_Homosexual", "p_2021_Homosexual", "OR_2021_Homosexual", "lower_ci_2021_Homosexual", "upper_ci_2021_Homosexual", "Coef_Bisexual", "2.5 %_Bisexual", "97.5 %_Bisexual", "p_2021_Bisexual", "OR_2021_Bisexual", "lower_ci_2021_Bisexual", "upper_ci_2021_Bisexual", "Coef_None of the above", "2.5 %_None of the above", "97.5 %_None of the above", "p_2021_None of the above", "OR_2021_None of the above", "lower_ci_2021_None of the above", "upper_ci_2021_None of the above" )

writexl::write_xlsx( model_lr_cc_output_wide, "model_lr_cc_output_wide_2021.xlsx" )
```

```{r}
# fit the substantive model to each of the imputed data sets
fit.imp <- with( imp.list, lmer( english ~ ravens + sex + fluent + ( 1|school ) ) )

# pool results
testEstimates(fit.imp, var.comp = TRUE) # Many different pooling methods are supported by mitml
```